### 2023-09-12 article/article.tex
WIP

\documentclass[11pt]{article} 
\usepackage[margin=1in]{geometry} % Sets all margins to 1 inch
\usepackage{amsmath}
\usepackage{hyperref} 
\usepackage{listings}
\usepackage{xcolor}
\usepackage{multicol}

\input{rust-listings.tex}  % Include the language definition

\title{TurboGx: A High-Throughput, Non-Cryptographic Hashing Algorithm Leveraging Modern CPU Capabilities}
\author{Olivier Giniaux}
\date{}

\begin{document}

\maketitle

\begin{abstract}

In the rapidly evolving landscape of data processing and cybersecurity, hashing algorithms play a pivotal role in ensuring data integrity and security. Traditional hashing methods, while effective, often fail to fully utilize the computational capabilities of modern processors. This paper introduces the TurboGx hashing algorithm, a novel approach that harnesses the power of high instruction-level parallelism (ILP) and Single Instruction, Multiple Data (SIMD) capabilities of contemporary CPUs to achieve high-throughput non-cryptographic hashing. Through a comprehensive analysis, including benchmarks and comparisons with existing methods, we demonstrate that TurboGx significantly outperforms conventional algorithms in terms of speed and computational efficiency without compromising on security. The paper also explores the implications, limitations, and avenues for future research in this burgeoning field.

\end{abstract}

\begin{multicols}{2}
\tableofcontents
\end{multicols}

\clearpage
\section{Introduction}

\subsection{Motivations}

\colorbox{yellow}{TODO}

\begin{lstlisting}[language=Rust, style=boxed]
use std::hint::black_box;

fn sum1(x: u32) -> u32 {
    let mut sum = x;
    for i in 0..1000 {
        sum = black_box(sum + i);
    }
    sum
}
\end{lstlisting}

\section{Related Work}

Let \( h: \{0,1\}^{n_b \times s_b} \to \{0,1\}^{s_h} \) be a cryptographic hash function where:

\begin{itemize}
    \item Input \( M \) is a binary message composed of \( n_b \) blocks of size \( s_b \), such as \( M = M_1 \parallel M_2 \parallel \ldots \parallel M_{n_b} \).
    \item Output is a binary hash of size \( s_h \).
\end{itemize}

\subsection{Merkle–Damgård Construction}

In the \textbf{Merkle–Damgård} construction, given:
\begin{itemize}
    \item The compression function \( f: \{0,1\}^{s_b} \times \{0,1\}^{s_b} \to \{0,1\}^{s_b} \)
    \item The pipe function \( g: \{0,1\}^{s_b} \to \{0,1\}^{s_h} \)
    \item A zero-filled vector \( 0^{s_b} \) of length \( s_b \)
\end{itemize}
The hash function \( h \) can be expressed as:
\begin{align*}
    h(M) &= g\left( f(\ldots f(f(0^{s_b}, M_1), M_2) \ldots, M_{n_b}) \right)
\end{align*}

\subsection{Wide-Pipe Construction} \label{widepipe}

The \textbf{Merkle–Damgård} construction has certain limitations, such as susceptibility to length extension and multicollision attacks. To address these issues, a variant known as the \textbf{wide-pipe} construction was introduced. This construction employs a larger internal state, so that:
\begin{align*}
    s_b \gg s_h
\end{align*}
By taking in a larger internal chaining value, the algorithm strengthens the integrity of the hash function, making it more challenging to reverse-engineer or compromise.

\subsection{Alternatives}

\href{https://www.researchgate.net/publication/322094216_Merkle-Damgard_Construction_Method_and_Alternatives_A_Review}{Alternatives}.

\section{High ILP Construction} \label{highilp}

Most modern general-purpose CPUs employ a superscalar architecture which enables instruction level parallelism (ILP). 
Minimizing dependencies in an algorithm allows a superscalar processor to execute more instructions concurrently, thus maximizing its inherent parallelism and overall performance.
The key limitation for ILP in the Merkle–Damgård construction is the inherent sequential dependency: each block's hash depends on the result of hashing the previous block.

In order to improve ILP, a construction can processes the message by groups of \( k_b \) blocks. This way, each group is hashed independently and intermediate hashes are compressed altogether thereafter.

\subsection{Intermediate Hashes}

Let's define \( n_g = \lfloor {n_b}/{k_b} \rfloor \) as the number of whole groups of \( k_b \) message blocks. \\
For each group we compute an intermediate hash, \( H_i \), as follows:

\begin{align*}
H_{1} &= f(\ldots f(f(0^{s_b}, M_1), M_2)\ldots, M_{k_b}), \\
H_{2} &= f(\ldots f(f(0^{s_b}, M_{k_g+1}), M_{k_g+2})\ldots, M_{2k_b}), \\
&\vdots \\
H_{n_g} &= f(\ldots f(f(0^{s_b}, M_{n_g+1}), M_{n_g+2})\ldots, M_{n_g+k_b})
\end{align*}

\subsection{Final Hash}

The final hash \( H \) is calculated using \( f \) to compress the intermediate hashes and the remaining message blocks (if any), which is then passed through \( g \):

\begin{equation*}
h(M) = g\left( f( \ldots f(f(\ldots f(f(0^s, H_1), H_2) \ldots, H_{n_g}), M_{4{n_g}+1}) \ldots, M_{n_b} ) \right).
\end{equation*}

\section{TurboGx Hashing Algorithm}

The \textbf{TurboGx} hashing algorithm employs an high ILP construction as described in section \ref{highilp}. In practice, this construction not only enables instruction level paralellism but also enables loop unrolling, disminishing the looping overhead, thus maximizing computational efficiency and overall performance.

\subsection{Pipe Width}
As for the wide-pipe construction (as seen in section \ref{widepipe}) with \( s_b \) set to the executing CPU SIMD register size.
TODO

\subsection{Compression}

TODO

\subsection{Hashing}

TODO

\subsection{Folding}

TODO

\subsection{Implementation Details}

SIMD
ILP
Vectorized
Parallelized
Optimized
Throughput
Hashing

HIGH ILP CONSTRUCTION

\subsubsection{Padding}

\subsubsection{Low-Overhead Looping}

\subsubsection{Loop Unrolling}

\subsubsection{CPU Alignement}

\textbf{Merkle–Damgård} and derivatives can actually handle message of an arbitrary size \( s_m \) by padding the message upfront with the padding function \( p: \{0,1\}^{s_m} \to \{0,1\}^{n_b \times s_b} \) where \( n_b = \lceil s_m/s_b \rceil \).

In practice, implementing \( p \) in computer code implies memory copies. Instead, TODO

\section{Benchmarks}
\subsection{Setup}
\subsection{Evaluation Metrics}
\subsection{Comparison with Existing Methods}

\section{Discussion}
\subsection{Implications}
\subsection{Limitations}
\subsection{Future Work}

\section{Conclusion}

\end{document}

### 2023-09-12 article/rust-listings.tex
WIP

\RequirePackage{color}
\RequirePackage{listings}

\lstdefinelanguage{Rust}{%
  sensitive%
, morecomment=[l]{//}%
, morecomment=[s]{/*}{*/}%
, moredelim=[s][{\itshape\color[rgb]{0,0,0.75}}]{\#[}{]}%
, morestring=[b]{"}%
, alsodigit={}%
, alsoother={}%
, alsoletter={!}%
%
%
% [1] reserve keywords
% [2] traits
% [3] primitive types
% [4] type and value constructors
% [5] identifier
%
, morekeywords={break, continue, else, for, if, in, loop, match, return, while}  % control flow keywords
, morekeywords={as, const, let, move, mut, ref, static}  % in the context of variables
, morekeywords={dyn, enum, fn, impl, Self, self, struct, trait, type, union, use, where}  % in the context of declarations
, morekeywords={crate, extern, mod, pub, super}  % in the context of modularisation
, morekeywords={unsafe}  % markers
, morekeywords={abstract, alignof, become, box, do, final, macro, offsetof, override, priv, proc, pure, sizeof, typeof, unsized, virtual, yield}  % reserved identifiers
%
% grep 'pub trait [A-Za-z][A-Za-z0-9]*' -r . | sed 's/^.*pub trait \([A-Za-z][A-Za-z0-9]*\).*/\1/g' | sort -u | tr '\n' ',' | sed 's/^\(.*\),$/{\1}\n/g' | sed 's/,/, /g'
, morekeywords=[2]{Add, AddAssign, Any, AsciiExt, AsInner, AsInnerMut, AsMut, AsRawFd, AsRawHandle, AsRawSocket, AsRef, Binary, BitAnd, BitAndAssign, Bitor, BitOr, BitOrAssign, BitXor, BitXorAssign, Borrow, BorrowMut, Boxed, BoxPlace, BufRead, BuildHasher, CastInto, CharExt, Clone, CoerceUnsized, CommandExt, Copy, Debug, DecodableFloat, Default, Deref, DerefMut, DirBuilderExt, DirEntryExt, Display, Div, DivAssign, DoubleEndedIterator, DoubleEndedSearcher, Drop, EnvKey, Eq, Error, ExactSizeIterator, ExitStatusExt, Extend, FileExt, FileTypeExt, Float, Fn, FnBox, FnMut, FnOnce, Freeze, From, FromInner, FromIterator, FromRawFd, FromRawHandle, FromRawSocket, FromStr, FullOps, FusedIterator, Generator, Hash, Hasher, Index, IndexMut, InPlace, Int, Into, IntoCow, IntoInner, IntoIterator, IntoRawFd, IntoRawHandle, IntoRawSocket, IsMinusOne, IsZero, Iterator, JoinHandleExt, LargeInt, LowerExp, LowerHex, MetadataExt, Mul, MulAssign, Neg, Not, Octal, OpenOptionsExt, Ord, OsStrExt, OsStringExt, Packet, PartialEq, PartialOrd, Pattern, PermissionsExt, Place, Placer, Pointer, Product, Put, RangeArgument, RawFloat, Read, Rem, RemAssign, Seek, Shl, ShlAssign, Shr, ShrAssign, Sized, SliceConcatExt, SliceExt, SliceIndex, Stats, Step, StrExt, Sub, SubAssign, Sum, Sync, TDynBenchFn, Terminal, Termination, ToOwned, ToSocketAddrs, ToString, Try, TryFrom, TryInto, UnicodeStr, Unsize, UpperExp, UpperHex, WideInt, Write}
, morekeywords=[2]{Send}  % additional traits
%
, morekeywords=[3]{bool, char, f32, f64, i8, i16, i32, i64, isize, str, u8, u16, u32, u64, unit, usize, i128, u128}  % primitive types
%
, morekeywords=[4]{Err, false, None, Ok, Some, true}  % prelude value constructors
% grep 'pub \(type\|struct\|enum\) [A-Za-z][A-Za-z0-9]*' -r . | sed 's/^.*pub \(type\|struct\|enum\) \([A-Za-z][A-Za-z0-9]*\).*/\2/g' | sort -u | tr '\n' ',' | sed 's/^\(.*\),$/{\1}\n/g' | sed 's/,/, /g'    
, morekeywords=[3]{AccessError, Adddf3, AddI128, AddoI128, AddoU128, ADDRESS, ADDRESS64, addrinfo, ADDRINFOA, AddrParseError, Addsf3, AddU128, advice, aiocb, Alignment, AllocErr, AnonPipe, Answer, Arc, Args, ArgsInnerDebug, ArgsOs, Argument, Arguments, ArgumentV1, Ashldi3, Ashlti3, Ashrdi3, Ashrti3, AssertParamIsClone, AssertParamIsCopy, AssertParamIsEq, AssertUnwindSafe, AtomicBool, AtomicPtr, Attr, auxtype, auxv, BackPlace, BacktraceContext, Barrier, BarrierWaitResult, Bencher, BenchMode, BenchSamples, BinaryHeap, BinaryHeapPlace, blkcnt, blkcnt64, blksize, BOOL, boolean, BOOLEAN, BoolTrie, BorrowError, BorrowMutError, Bound, Box, bpf, BTreeMap, BTreeSet, Bucket, BucketState, Buf, BufReader, BufWriter, Builder, BuildHasherDefault, BY, BYTE, Bytes, CannotReallocInPlace, cc, Cell, Chain, CHAR, CharIndices, CharPredicateSearcher, Chars, CharSearcher, CharsError, CharSliceSearcher, CharTryFromError, Child, ChildPipes, ChildStderr, ChildStdin, ChildStdio, ChildStdout, Chunks, ChunksMut, ciovec, clock, clockid, Cloned, cmsgcred, cmsghdr, CodePoint, Color, ColorConfig, Command, CommandEnv, Component, Components, CONDITION, condvar, Condvar, CONSOLE, CONTEXT, Count, Cow, cpu, CRITICAL, CStr, CString, CStringArray, Cursor, Cycle, CycleIter, daddr, DebugList, DebugMap, DebugSet, DebugStruct, DebugTuple, Decimal, Decoded, DecodeUtf16, DecodeUtf16Error, DecodeUtf8, DefaultEnvKey, DefaultHasher, dev, device, Difference, Digit32, DIR, DirBuilder, dircookie, dirent, dirent64, DirEntry, Discriminant, DISPATCHER, Display, Divdf3, Divdi3, Divmoddi4, Divmodsi4, Divsf3, Divsi3, Divti3, dl, Dl, Dlmalloc, Dns, DnsAnswer, DnsQuery, dqblk, Drain, DrainFilter, Dtor, Duration, DwarfReader, DWORD, DWORDLONG, DynamicLibrary, Edge, EHAction, EHContext, Elf32, Elf64, Empty, EmptyBucket, EncodeUtf16, EncodeWide, Entry, EntryPlace, Enumerate, Env, epoll, errno, Error, ErrorKind, EscapeDebug, EscapeDefault, EscapeUnicode, event, Event, eventrwflags, eventtype, ExactChunks, ExactChunksMut, EXCEPTION, Excess, ExchangeHeapSingleton, exit, exitcode, ExitStatus, Failure, fd, fdflags, fdsflags, fdstat, ff, fflags, File, FILE, FileAttr, filedelta, FileDesc, FilePermissions, filesize, filestat, FILETIME, filetype, FileType, Filter, FilterMap, Fixdfdi, Fixdfsi, Fixdfti, Fixsfdi, Fixsfsi, Fixsfti, Fixunsdfdi, Fixunsdfsi, Fixunsdfti, Fixunssfdi, Fixunssfsi, Fixunssfti, Flag, FlatMap, Floatdidf, FLOATING, Floatsidf, Floatsisf, Floattidf, Floattisf, Floatundidf, Floatunsidf, Floatunsisf, Floatuntidf, Floatuntisf, flock, ForceResult, FormatSpec, Formatted, Formatter, Fp, FpCategory, fpos, fpos64, fpreg, fpregset, FPUControlWord, Frame, FromBytesWithNulError, FromUtf16Error, FromUtf8Error, FrontPlace, fsblkcnt, fsfilcnt, fsflags, fsid, fstore, fsword, FullBucket, FullBucketMut, FullDecoded, Fuse, GapThenFull, GeneratorState, gid, glob, glob64, GlobalDlmalloc, greg, group, GROUP, Guard, GUID, Handle, HANDLE, Handler, HashMap, HashSet, Heap, HINSTANCE, HMODULE, hostent, HRESULT, id, idtype, if, ifaddrs, IMAGEHLP, Immut, in, in6, Incoming, Infallible, Initializer, ino, ino64, inode, input, InsertResult, Inspect, Instant, int16, int32, int64, int8, integer, IntermediateBox, Internal, Intersection, intmax, IntoInnerError, IntoIter, IntoStringError, intptr, InvalidSequence, iovec, ip, IpAddr, ipc, Ipv4Addr, ipv6, Ipv6Addr, Ipv6MulticastScope, Iter, IterMut, itimerspec, itimerval, jail, JoinHandle, JoinPathsError, KDHELP64, kevent, kevent64, key, Key, Keys, KV, l4, LARGE, lastlog, launchpad, Layout, Lazy, lconv, Leaf, LeafOrInternal, Lines, LinesAny, LineWriter, linger, linkcount, LinkedList, load, locale, LocalKey, LocalKeyState, Location, lock, LockResult, loff, LONG, lookup, lookupflags, LookupHost, LPBOOL, LPBY, LPBYTE, LPCSTR, LPCVOID, LPCWSTR, LPDWORD, LPFILETIME, LPHANDLE, LPOVERLAPPED, LPPROCESS, LPPROGRESS, LPSECURITY, LPSTARTUPINFO, LPSTR, LPVOID, LPWCH, LPWIN32, LPWSADATA, LPWSAPROTOCOL, LPWSTR, Lshrdi3, Lshrti3, lwpid, M128A, mach, major, Map, mcontext, Metadata, Metric, MetricMap, mflags, minor, mmsghdr, Moddi3, mode, Modsi3, Modti3, MonitorMsg, MOUNT, mprot, mq, mqd, msflags, msghdr, msginfo, msglen, msgqnum, msqid, Muldf3, Mulodi4, Mulosi4, Muloti4, Mulsf3, Multi3, Mut, Mutex, MutexGuard, MyCollection, n16, NamePadding, NativeLibBoilerplate, nfds, nl, nlink, NodeRef, NoneError, NonNull, NonZero, nthreads, NulError, OccupiedEntry, off, off64, oflags, Once, OnceState, OpenOptions, Option, Options, OptRes, Ordering, OsStr, OsString, Output, OVERLAPPED, Owned, Packet, PanicInfo, Param, ParseBoolError, ParseCharError, ParseError, ParseFloatError, ParseIntError, ParseResult, Part, passwd, Path, PathBuf, PCONDITION, PCONSOLE, Peekable, PeekMut, Permissions, PhantomData, pid, Pipes, PlaceBack, PlaceFront, PLARGE, PoisonError, pollfd, PopResult, port, Position, Powidf2, Powisf2, Prefix, PrefixComponent, PrintFormat, proc, Process, PROCESS, processentry, protoent, PSRWLOCK, pthread, ptr, ptrdiff, PVECTORED, Queue, radvisory, RandomState, Range, RangeFrom, RangeFull, RangeInclusive, RangeMut, RangeTo, RangeToInclusive, RawBucket, RawFd, RawHandle, RawPthread, RawSocket, RawTable, RawVec, Rc, ReadDir, Receiver, recv, RecvError, RecvTimeoutError, ReentrantMutex, ReentrantMutexGuard, Ref, RefCell, RefMut, REPARSE, Repeat, Result, Rev, Reverse, riflags, rights, rlim, rlim64, rlimit, rlimit64, roflags, Root, RSplit, RSplitMut, RSplitN, RSplitNMut, RUNTIME, rusage, RwLock, RWLock, RwLockReadGuard, RwLockWriteGuard, sa, SafeHash, Scan, sched, scope, sdflags, SearchResult, SearchStep, SECURITY, SeekFrom, segment, Select, SelectionResult, sem, sembuf, send, Sender, SendError, servent, sf, Shared, shmatt, shmid, ShortReader, ShouldPanic, Shutdown, siflags, sigaction, SigAction, sigevent, sighandler, siginfo, Sign, signal, signalfd, SignalToken, sigset, sigval, Sink, SipHasher, SipHasher13, SipHasher24, size, SIZE, Skip, SkipWhile, Slice, SmallBoolTrie, sockaddr, SOCKADDR, sockcred, Socket, SOCKET, SocketAddr, SocketAddrV4, SocketAddrV6, socklen, speed, Splice, Split, SplitMut, SplitN, SplitNMut, SplitPaths, SplitWhitespace, spwd, SRWLOCK, ssize, stack, STACKFRAME64, StartResult, STARTUPINFO, stat, Stat, stat64, statfs, statfs64, StaticKey, statvfs, StatVfs, statvfs64, Stderr, StderrLock, StderrTerminal, Stdin, StdinLock, Stdio, StdioPipes, Stdout, StdoutLock, StdoutTerminal, StepBy, String, StripPrefixError, StrSearcher, subclockflags, Subdf3, SubI128, SuboI128, SuboU128, subrwflags, subscription, Subsf3, SubU128, Summary, suseconds, SYMBOL, SYMBOLIC, SymmetricDifference, SyncSender, sysinfo, System, SystemTime, SystemTimeError, Take, TakeWhile, tcb, tcflag, TcpListener, TcpStream, TempDir, TermInfo, TerminfoTerminal, termios, termios2, TestDesc, TestDescAndFn, TestEvent, TestFn, TestName, TestOpts, TestResult, Thread, threadattr, threadentry, ThreadId, tid, time, time64, timespec, TimeSpec, timestamp, timeval, timeval32, timezone, tm, tms, ToLowercase, ToUppercase, TraitObject, TryFromIntError, TryFromSliceError, TryIter, TryLockError, TryLockResult, TryRecvError, TrySendError, TypeId, U64x2, ucontext, ucred, Udivdi3, Udivmoddi4, Udivmodsi4, Udivmodti4, Udivsi3, Udivti3, UdpSocket, uid, UINT, uint16, uint32, uint64, uint8, uintmax, uintptr, ulflags, ULONG, ULONGLONG, Umoddi3, Umodsi3, Umodti3, UnicodeVersion, Union, Unique, UnixDatagram, UnixListener, UnixStream, Unpacked, UnsafeCell, UNWIND, UpgradeResult, useconds, user, userdata, USHORT, Utf16Encoder, Utf8Error, Utf8Lossy, Utf8LossyChunk, Utf8LossyChunksIter, utimbuf, utmp, utmpx, utsname, uuid, VacantEntry, Values, ValuesMut, VarError, Variables, Vars, VarsOs, Vec, VecDeque, vm, Void, WaitTimeoutResult, WaitToken, wchar, WCHAR, Weak, whence, WIN32, WinConsole, Windows, WindowsEnvKey, winsize, WORD, Wrapping, wrlen, WSADATA, WSAPROTOCOL, WSAPROTOCOLCHAIN, Wtf8, Wtf8Buf, Wtf8CodePoints, xsw, xucred, Zip, zx}
%
, morekeywords=[5]{assert!, assert_eq!, assert_ne!, cfg!, column!, compile_error!, concat!, concat_idents!, debug_assert!, debug_assert_eq!, debug_assert_ne!, env!, eprint!, eprintln!, file!, format!, format_args!, include!, include_bytes!, include_str!, line!, module_path!, option_env!, panic!, print!, println!, select!, stringify!, thread_local!, try!, unimplemented!, unreachable!, vec!, write!, writeln!}  % prelude macros
}%

\lstdefinestyle{colouredRust}%
{ basicstyle=\ttfamily%
, identifierstyle=%
, commentstyle=\color[gray]{0.4}%
, stringstyle=\color[rgb]{0, 0, 0.5}%
, keywordstyle=\bfseries% reserved keywords
, keywordstyle=[2]\color[rgb]{0.75, 0, 0}% traits
, keywordstyle=[3]\color[rgb]{0, 0.5, 0}% primitive types
, keywordstyle=[4]\color[rgb]{0, 0.5, 0}% type and value constructors
, keywordstyle=[5]\color[rgb]{0, 0, 0.75}% macros
, columns=spaceflexible%
, keepspaces=true%
, showspaces=false%
, showtabs=false%
, showstringspaces=true%
}%

\lstdefinestyle{boxed}{
  style=colouredRust%
, numbers=left%
, firstnumber=auto%
, numberblanklines=true%
, frame=trbL%
, numberstyle=\tiny%
, frame=leftline%
, numbersep=7pt%
, framesep=5pt%
, framerule=10pt%
, xleftmargin=15pt%
, backgroundcolor=\color[gray]{0.97}%
, rulecolor=\color[gray]{0.90}%
}

### 2023-09-12 benches/benchmark.rs

@@ -1,0 +1,47 @@
+use criterion::{black_box, criterion_group, criterion_main, Criterion};
+
+const iterations: u32 = 100000;
+
+fn sum_naive() -> u32 {
+    let mut sum = 0;
+    for i in 0..iterations {
+        sum = black_box(sum + 1);
+    }
+    sum
+}
+
+fn sum_unrolled() -> u32 {
+    let mut sum = 0;
+    for i in 0..iterations/5 {
+        sum = black_box(sum + 1);
+        sum = black_box(sum + 1);
+        sum = black_box(sum + 1);
+        sum = black_box(sum + 1);
+        sum = black_box(sum + 1);
+    }
+    sum
+}
+
+fn sum_unrolled_high_ilp() -> u32 {
+    let mut sum = 0;
+    for i in 0..iterations/5 {
+        let mut tempSum: u32 = 0;
+        tempSum = black_box(tempSum + 1);
+        tempSum = black_box(tempSum + 1);
+        tempSum = black_box(tempSum + 1);
+        tempSum = black_box(tempSum + 1);
+        tempSum = black_box(tempSum + 1);
+
+        sum = black_box(sum + tempSum);
+    }
+    sum
+}
+
+fn criterion_benchmark(c: &mut Criterion) {
+    c.bench_function("naive", |b| b.iter(|| black_box(sum_naive())));
+    c.bench_function("unrolling", |b| b.iter(|| black_box(sum_unrolled())));
+    c.bench_function("unrolling + high ILP", |b| b.iter(|| black_box(sum_unrolled_high_ilp())));
+}
+
+criterion_group!(benches, criterion_benchmark);
+criterion_main!(benches);

### 2023-09-12 src/main.rs

@@ -1,0 +1,37 @@
+use std::time::Duration;
+use std::time::Instant;
+use std::hint::black_box;
+
+fn main() {
+    println!("{}", sum1(1));
+    println!("{}", sum2(1));
+}
+
+#[inline(never)]
+fn sum1(x: u32) -> u32 {
+    let mut sum = x;
+    for i in 0..1000 {
+        sum = black_box(sum + i);
+        sum = black_box(sum + i);
+        sum = black_box(sum + i);
+        sum = black_box(sum + i);
+        sum = black_box(sum + i);
+    }
+    sum
+}
+
+#[inline(never)]
+fn sum2(x: u32) -> u32 {
+    let mut sum = x;
+    for i in 0..1000 {
+        let mut tempSum: u32 = 0;
+        tempSum += x;
+        tempSum += x;
+        tempSum += x;
+        tempSum += x;
+        tempSum += x;
+
+        sum += tempSum;
+    }
+    sum
+}

### 2023-09-12 benches/benchmark.rs
Why is there no ILP

@@ -1,4 +1,8 @@
+use std::arch::aarch64::int8x16_t;
+
 use criterion::{black_box, criterion_group, criterion_main, Criterion};
+
+use gxhash::gxhash;
 
 const iterations: u32 = 100000;
 
@@ -37,11 +41,30 @@ fn sum_unrolled_high_ilp() -> u32 {
     sum
 }
 
-fn criterion_benchmark(c: &mut Criterion) {
+fn ilp_benchmark(c: &mut Criterion) {
     c.bench_function("naive", |b| b.iter(|| black_box(sum_naive())));
     c.bench_function("unrolling", |b| b.iter(|| black_box(sum_unrolled())));
     c.bench_function("unrolling + high ILP", |b| b.iter(|| black_box(sum_unrolled_high_ilp())));
 }
 
-criterion_group!(benches, criterion_benchmark);
+use rand::Rng;
+
+fn gxhash_benchmark(c: &mut Criterion) {
+    let mut rng = rand::thread_rng();
+    let mut random_bytes = [0i8; 16384]; // Create an array of 16 bytes, initialized to 0
+    rng.fill(&mut random_bytes[..]); // Fill the array with random bytes
+
+    let (prefix, aligned, suffix) = unsafe { random_bytes.align_to_mut::<int8x16_t>() };
+    
+    // Get the raw pointer and length for the new slice of i8
+    let ptr = aligned.as_ptr() as *const i8;
+    let len = aligned.len() * std::mem::size_of::<int8x16_t>();
+
+    // Create the new slice of i8
+    let i8_slice: &[i8] = unsafe { std::slice::from_raw_parts(ptr, len) };
+    c.bench_function("gxhash", |b| b.iter(|| black_box(unsafe { gxhash(&i8_slice) })));
+}
+
+criterion_group!(benches, gxhash_benchmark);
+//criterion_group!(benches, ilp_benchmark, gxhash_benchmark);
 criterion_main!(benches);

### 2023-09-12 src/gxhash.rs

@@ -1,0 +1,78 @@
+// Import ARM NEON intrinsics
+#[cfg(target_arch = "aarch64")]
+use core::arch::aarch64::*;
+
+use std::{mem, intrinsics::{prefetch_read_data, likely}};
+
+pub unsafe fn gxhash(input: &[i8]) -> u32 {
+
+    const VECTOR_SIZE_SHIFT: usize = 4;
+    const UNROLL_FACTOR_SHIFT: usize = 3;
+
+    const VECTOR_SIZE: usize = 1 << VECTOR_SIZE_SHIFT;
+    const UNROLL_FACTOR: usize = 1 << UNROLL_FACTOR_SHIFT;
+
+    let len = input.len();
+
+    let unrollable_blocks_count: usize = (len >> (VECTOR_SIZE_SHIFT + UNROLL_FACTOR_SHIFT)) << UNROLL_FACTOR_SHIFT; 
+    let remaining_blocks_count: usize = (len >> VECTOR_SIZE_SHIFT) - unrollable_blocks_count;
+    let remaining_bytes = len & (VECTOR_SIZE - 1);
+
+    let mut p = input.as_ptr();
+    let mut v = p as *const int8x16_t;
+    let end_address = v.add(unrollable_blocks_count) as usize;
+
+    let mut hash_vector: int8x16_t = vdupq_n_s8(0);
+
+    prefetch_read_data(p, 2);
+
+    while likely((v as usize) < end_address) {
+
+        let mut block_hash_vector: int8x16_t = vdupq_n_s8(0);
+        block_hash_vector = compress(block_hash_vector, *v);
+        block_hash_vector = compress(block_hash_vector, *v.offset(1));
+        block_hash_vector = compress(block_hash_vector, *v.offset(2));
+        block_hash_vector = compress(block_hash_vector, *v.offset(3));
+        block_hash_vector = compress(block_hash_vector, *v.offset(4));
+        block_hash_vector = compress(block_hash_vector, *v.offset(5));
+        block_hash_vector = compress(block_hash_vector, *v.offset(6));
+        block_hash_vector = compress(block_hash_vector, *v.offset(7));
+        
+        hash_vector = compress(hash_vector, block_hash_vector);
+
+        // hash_vector = compress(hash_vector, *v);
+        // hash_vector = compress(hash_vector, *v.offset(1));
+        // hash_vector = compress(hash_vector, *v.offset(2));
[…]

### 2023-09-12 src/lib.rs

@@ -1,0 +1,52 @@
+#![feature(core_intrinsics)]
+
+//use std::intrinsics::likely;
+use std::time::Duration;
+use std::time::Instant;
+use std::hint::black_box;
+use rand::Rng;
+
+mod gxhash;
+
+pub use gxhash::gxhash;
+
+// fn main() {
+//     println!("{}", sum1(1));
+//     println!("{}", sum2(1));
+
+//     let mut rng = rand::thread_rng();
+//     let mut random_bytes = [0i8; 16384]; // Create an array of 16 bytes, initialized to 0
+//     rng.fill(&mut random_bytes[..]); // Fill the array with random bytes
+
+//     unsafe { println!("{}", gxhash(&random_bytes)) };
+// }
+
+// #[inline(never)]
+// fn sum1(x: u32) -> u32 {
+//     let mut sum = x;
+//     for i in 0..1000 {
+//         sum = black_box(sum + i);
+//         sum = black_box(sum + i);
+//         sum = black_box(sum + i);
+//         sum = black_box(sum + i);
+//         sum = black_box(sum + i);
+//     }
+//     sum
+// }
+
+// #[inline(never)]
+// fn sum2(x: u32) -> u32 {
+//     let mut sum = x;
+//     for i in 0..1000 {
+//         let mut tempSum: u32 = 0;
+//         tempSum += x;
+//         tempSum += x;
+//         tempSum += x;
+//         tempSum += x;
+//         tempSum += x;
+
+//         sum += tempSum;
+//     }
+//     sum
+// }
+

### 2023-09-12 src/main.rs

@@ -1,37 +1,26 @@
-use std::time::Duration;
-use std::time::Instant;
-use std::hint::black_box;
+use std::arch::aarch64::int8x16_t;
+
+use rand::Rng;
+
+use gxhash::gxhash;
 
 fn main() {
-    println!("{}", sum1(1));
-    println!("{}", sum2(1));
-}
 
-#[inline(never)]
-fn sum1(x: u32) -> u32 {
-    let mut sum = x;
-    for i in 0..1000 {
-        sum = black_box(sum + i);
-        sum = black_box(sum + i);
-        sum = black_box(sum + i);
-        sum = black_box(sum + i);
-        sum = black_box(sum + i);
-    }
-    sum
-}
+    let mut rng = rand::thread_rng();
+    let mut random_bytes = [0i8; 16384]; // Create an array of 16 bytes, initialized to 0
+    rng.fill(&mut random_bytes[..]); // Fill the array with random bytes
 
-#[inline(never)]
-fn sum2(x: u32) -> u32 {
-    let mut sum = x;
-    for i in 0..1000 {
-        let mut tempSum: u32 = 0;
-        tempSum += x;
-        tempSum += x;
-        tempSum += x;
-        tempSum += x;
-        tempSum += x;
+    let (prefix, aligned, suffix) = unsafe { random_bytes.align_to_mut::<int8x16_t>() };
+    
+    // Get the raw pointer and length for the new slice of i8
+    let ptr = aligned.as_ptr() as *const i8;
+    let len = aligned.len() * std::mem::size_of::<int8x16_t>();
 
-        sum += tempSum;
-    }
-    sum
+    // Create the new slice of i8
+    let i8_slice: &[i8] = unsafe { std::slice::from_raw_parts(ptr, len) };
+
+    println!("bytes: {}", prefix.len());
+    println!("bytes: {}", i8_slice.len());
+
+    unsafe { println!("{}", gxhash(&i8_slice)) };
 }

### 2023-09-13 src/gxhash.rs
Meh speed

@@ -3,6 +3,7 @@
 use core::arch::aarch64::*;
 
 use std::{mem, intrinsics::{prefetch_read_data, likely}};
+use std::hint::black_box;
 
 pub unsafe fn gxhash(input: &[i8]) -> u32 {
 
@@ -40,15 +41,6 @@ pub unsafe fn gxhash(input: &[i8]) -> u32 {
         
         hash_vector = compress(hash_vector, block_hash_vector);
 
-        // hash_vector = compress(hash_vector, *v);
-        // hash_vector = compress(hash_vector, *v.offset(1));
-        // hash_vector = compress(hash_vector, *v.offset(2));
-        // hash_vector = compress(hash_vector, *v.offset(3));
-        // hash_vector = compress(hash_vector, *v.offset(4));
-        // hash_vector = compress(hash_vector, *v.offset(5));
-        // hash_vector = compress(hash_vector, *v.offset(6));
-        // hash_vector = compress(hash_vector, *v.offset(7));
-
         v = v.add(UNROLL_FACTOR);
     }
 
@@ -74,5 +66,5 @@ pub unsafe fn gxhash(input: &[i8]) -> u32 {
 
 #[inline]
 unsafe fn compress(a: int8x16_t, b: int8x16_t) -> int8x16_t {
-    vaddq_s8(a, b)
+    vaddq_s8(vmulq_s8(a, b), b)
 }

### 2023-09-16 benches/throughput.rs
Benchmark both aligned an unaligned data

@@ -1,44 +1,51 @@
 use std::{mem::size_of, time::Duration};
 
-use criterion::{criterion_group, criterion_main, Criterion, Throughput};
+use criterion::{black_box, criterion_group, criterion_main, Criterion, Throughput};
 
 use gxhash::gxhash;
 
 use rand::Rng;
 
+use std::alloc::{alloc, dealloc, Layout};
+use std::slice;
+
 fn gxhash_benchmark(c: &mut Criterion) {
     let mut rng = rand::thread_rng();
-
     let mut len = 1;
-
     let mut group = c.benchmark_group("gxhash");
+
+    // Allocate 32-bytes-aligned
+    let layout = Layout::from_size_align(100000, 16).unwrap();
+    let ptr = unsafe { alloc(layout) };
+    let slice: &mut [u8] = unsafe { slice::from_raw_parts_mut(ptr, 100000) };
+
+    // Fill with random bytes
+    rng.fill(slice);
+
     for i in 1..9 {
         len *= 4;
-        let mut random_bytes: Vec<u8> = vec![0; len];
-        rng.fill(&mut random_bytes[..]);
 
-        let ptr = random_bytes.as_ptr() as *const u8;
-        let len = ptr as usize % size_of::<gxhash::state>() == 0;
-        
-        println!("aligned: {}", len);
+        group.throughput(Throughput::Bytes(len as u64));
 
-        // let (prefix, aligned, suffix) = unsafe { random_bytes.align_to_mut::<gxhash::state>() };
-        // let ptr = aligned.as_ptr() as *const u8;
-        // let len = aligned.len() * std::mem::size_of::<gxhash::state>();
-        // let i8_slice: &[u8] = unsafe { std::slice::from_raw_parts(ptr, len) };
+        let aligned_slice = &slice[0..len];
+        group.bench_with_input(format!("{} bytes (aligned)", len), aligned_slice, |bencher, input| {
+            bencher.iter(|| black_box(gxhash(input)))
+        });
 
-        group.throughput(Throughput::Bytes(random_bytes.len() as u64));
-        group.bench_with_input(format!("{} bytes", random_bytes.len()), &random_bytes, |bencher, input| {
-            bencher.iter(|| gxhash(input))
+        let unaligned_slice = &slice[1..len];
+        group.bench_with_input(format!("{} bytes (unaligned)", len), unaligned_slice, |bencher, input| {
+            bencher.iter(|| black_box(gxhash(input)))
         });
     }
+
[…]

### 2023-09-16 src/gxhash.rs

@@ -146,8 +146,8 @@ pub fn gxhash(input: &[u8]) -> u32 {
         }
 
         while (v as usize) < end_address {
-            hash_vector = compress(hash_vector, _mm256_loadu_si256(v));
-            v = v.offset(1);
+            load_unaligned!(v, v0);
+            hash_vector = compress(hash_vector, v0);
         }
 
         if likely(remaining_bytes > 0) {

### 2023-09-16 benches/ilp_sum.rs
Some cleanup

@@ -25,14 +25,14 @@ fn sum_unrolled() -> u32 {
 fn sum_unrolled_tempsum() -> u32 {
     let mut sum = 0;
     for i in 0..ITERATIONS/5 {
-        let mut tempSum: u32 = 0;
-        tempSum = black_box(tempSum + 1);
-        tempSum = black_box(tempSum + 1);
-        tempSum = black_box(tempSum + 1);
-        tempSum = black_box(tempSum + 1);
-        tempSum = black_box(tempSum + 1);
+        let mut temp_sum: u32 = 0;
+        temp_sum = black_box(temp_sum + 1);
+        temp_sum = black_box(temp_sum + 1);
+        temp_sum = black_box(temp_sum + 1);
+        temp_sum = black_box(temp_sum + 1);
+        temp_sum = black_box(temp_sum + 1);
 
-        sum = black_box(sum + tempSum);
+        sum = black_box(sum + temp_sum);
     }
     sum
 }

### 2023-09-16 benches/throughput.rs

@@ -1,13 +1,10 @@
-use std::{mem::size_of, time::Duration};
-
-use criterion::{black_box, criterion_group, criterion_main, Criterion, Throughput};
-
-use gxhash::gxhash;
-
-use rand::Rng;
-
+use std::time::Duration;
 use std::alloc::{alloc, dealloc, Layout};
 use std::slice;
+
+use criterion::{black_box, criterion_group, criterion_main, Criterion, Throughput};
+use gxhash::gxhash;
+use rand::Rng;
 
 fn gxhash_benchmark(c: &mut Criterion) {
     let mut rng = rand::thread_rng();
@@ -15,7 +12,7 @@ fn gxhash_benchmark(c: &mut Criterion) {
     let mut group = c.benchmark_group("gxhash");
 
     // Allocate 32-bytes-aligned
-    let layout = Layout::from_size_align(100000, 16).unwrap();
+    let layout = Layout::from_size_align(100000, 32).unwrap();
     let ptr = unsafe { alloc(layout) };
     let slice: &mut [u8] = unsafe { slice::from_raw_parts_mut(ptr, 100000) };
 
@@ -44,8 +41,8 @@ fn gxhash_benchmark(c: &mut Criterion) {
 criterion_group! {
     name = benches;
     config = Criterion::default()
-        .sample_size(100)
-        .measurement_time(Duration::from_secs(5));  // Set your custom sample size here
+        .sample_size(1000)
+        .measurement_time(Duration::from_secs(10));
     targets = gxhash_benchmark,
 }
 criterion_main!(benches);

### 2023-09-16 src/gxhash.rs

@@ -54,6 +54,21 @@ mod platform_defs {
     }
 
     #[inline]
+    pub unsafe fn load_unaligned(p: *const state) -> state {
+        _mm256_loadu_si256(p)
+    }
+
+    #[inline]
+    pub unsafe fn get_partial(p: *const state, len: isize) -> state {
+        const MASK: [u8; 64] = [
+            0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF,
+            0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00 ];
+
+        let mask = _mm256_loadu_epi8((MASK.as_ptr() as *const i8).offset(32 - len));
+        _mm256_and_si256(_mm256_loadu_si256(p), mask)
+    }
+
+    #[inline]
     pub unsafe fn compress(a: state, b: state) -> state {
         let sum: state = _mm256_add_epi8(a, b);
         _mm256_alignr_epi8(sum, sum, 1) 
@@ -71,26 +86,17 @@ mod platform_defs {
     pub unsafe fn fold(hash: state) -> u32 {
         let p = &hash as *const state as *const u32;
         *p + *p.offset(1) + *p.offset(2) + *p.offset(3) + *p.offset(4) + *p.offset(5) + *p.offset(6)+ *p.offset(7)
-
-        // let mut result: [u32; 8] = [0; 8];
-        // _mm256_storeu_si256(result.as_mut_ptr() as *mut state, hash);
-        // result[7]
-
-        // let sum128 = _mm_add_epi32( 
-        //     _mm256_castsi256_si128(hash),
-        //     _mm256_extracti128_si256(hash, 1)); // silly GCC uses a longer AXV512VL instruction if AVX512 is enabled :/
[…]

### 2023-09-16 src/gxhash.rs
Fix build ARM64

@@ -13,7 +13,22 @@ mod platform_defs {
     
     #[inline]
     pub unsafe fn prefetch(p: *const state) {
-        __pld(p as *const i8);
+        //__pld(p as *const i8);
+    }
+
+    #[inline]
+    pub unsafe fn load_unaligned(p: *const state) -> state {
+        vld1q_s8(p as *const i8)
+    }
+
+    #[inline]
+    pub unsafe fn get_partial(p: *const state, len: isize) -> state {
+        const MASK: [u8; 32] = [
+            0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF,
+            0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00 ];
+
+        let mask = vld1q_s8((MASK.as_ptr() as *const i8).offset(16 - len));
+        vandq_s8(load_unaligned(p), mask)
     }
 
     #[inline]

### 2023-09-16 benches/ilp_sum.rs
Improve ILP benchmark

@@ -1,63 +1,86 @@
+
 use criterion::{black_box, criterion_group, criterion_main, Criterion};
 
-const ITERATIONS: u32 = 100000;
-
-fn sum_naive() -> u32 {
-    let mut sum = 0;
-    for i in 0..ITERATIONS {
-        sum = black_box(sum + 1);
-    }
-    sum
+#[inline]
+fn dohash(hash: usize, value: usize) -> usize {
+    hash * value + value
 }
 
-fn sum_unrolled() -> u32 {
-    let mut sum = 0;
-    for i in 0..ITERATIONS/5 {
-        sum = black_box(sum + 1);
-        sum = black_box(sum + 1);
-        sum = black_box(sum + 1);
-        sum = black_box(sum + 1);
-        sum = black_box(sum + 1);
+fn simple_loop(input: &[usize]) -> usize {
+    let mut hash = 0;
+    let mut i: usize = 0;
+    while i < input.len() {
+        hash = dohash(hash, input[i]);
+
+        i = i + 1;
     }
-    sum
+    hash
 }
 
-fn sum_unrolled_tempsum() -> u32 {
-    let mut sum = 0;
-    for i in 0..ITERATIONS/5 {
-        let mut temp_sum: u32 = 0;
-        temp_sum = black_box(temp_sum + 1);
-        temp_sum = black_box(temp_sum + 1);
-        temp_sum = black_box(temp_sum + 1);
-        temp_sum = black_box(temp_sum + 1);
-        temp_sum = black_box(temp_sum + 1);
+fn unrolled_loop(input: &[usize]) -> usize {
+    let mut hash: usize = 0;
+    let mut i: usize = 0;
+    while i < input.len() {
+        hash = dohash(hash, input[i]);
+        hash = dohash(hash, input[i + 1]);
+        hash = dohash(hash, input[i + 2]);
+        hash = dohash(hash, input[i + 3]);
+        hash = dohash(hash, input[i + 4]);
 
-        sum = black_box(sum + temp_sum);
+        i = i + 5;
     }
-    sum
+    hash
 }
 
-fn sum_unrolled_5_lanes() -> u32 {
-    let mut sum1 = 0;
-    let mut sum2 = 0;
-    let mut sum3 = 0;
-    let mut sum4 = 0;
-    let mut sum5 = 0;
-    for i in 0..ITERATIONS/5 {
-        sum1 = black_box(sum1 + 1);
-        sum2 = black_box(sum2 + 1);
[…]

### 2023-09-16 benches/ilp.rs
Renaming

@@ -32,7 +32,7 @@ fn unrolled_loop(input: &[usize]) -> usize {
     hash
 }
 
-fn unrolled_loop_temp_per_iteration(input: &[usize]) -> usize {
+fn unrolled_temp_loop(input: &[usize]) -> usize {
     let mut hash: usize = 0;
     let mut i: usize = 0;
     while i < input.len() {

### 2023-09-16 benches/ilp.rs
Update formula for laned processing in latex

@@ -79,7 +79,7 @@ fn ilp_benchmark(c: &mut Criterion) {
     }
     c.bench_function("simple_loop", |b| b.iter(|| black_box(simple_loop(&input))));
     c.bench_function("unrolled_loop", |b| b.iter(|| black_box(unrolled_loop(&input))));
-    c.bench_function("unrolled_loop_temp_per_iteration", |b| b.iter(|| black_box(unrolled_loop_temp_per_iteration(&input))));
+    c.bench_function("unrolled_temp_loop", |b| b.iter(|| black_box(unrolled_temp_loop(&input))));
     c.bench_function("unrolled_laned_loop", |b| b.iter(|| black_box(unrolled_laned_loop(&input))));
 }
 

### 2023-09-16 benches/throughput.rs

@@ -19,7 +19,7 @@ fn gxhash_benchmark(c: &mut Criterion) {
     // Fill with random bytes
     rng.fill(slice);
 
-    for i in 1..9 {
+    for _ in 1..9 {
         len *= 4;
 
         group.throughput(Throughput::Bytes(len as u64));

### 2023-09-18 article/article.tex
Update formula for laned processing in latex
More writing

@@
 \documentclass[11pt]{article} 
-\usepackage[margin=1in]{geometry} % Sets all margins to 1 inch
+\usepackage[margin=0.8in]{geometry} % Sets all margins to 1 inch
 \usepackage{amsmath}
@@
 
-\title{TurboGx: A High-Throughput, Non-Cryptographic Hashing Algorithm Leveraging Modern CPU Capabilities}
+\title{GxHash: A High-Throughput, Non-Cryptographic Hashing Algorithm Leveraging Modern CPU Capabilities}
 \author{Olivier Giniaux}
@@
 Traditional hashing methods, while effective, often fail to fully utilize the computational capabilities of modern processors.
-This paper introduces the TurboGx hashing algorithm, a novel approach that harnesses the power of high instruction-level parallelism (ILP) and Single Instruction, Multiple Data (SIMD) capabilities of contemporary CPUs to achieve high-throughput non-cryptographic hashing.
-Through a comprehensive analysis, including benchmarks and comparisons with existing methods, we demonstrate that TurboGx significantly outperforms conventional algorithms in terms of speed and computational efficiency without compromising on security.
+This paper introduces the GxHash hashing algorithm, a novel approach that harnesses the power of high instruction-level parallelism (ILP) and Single Instruction, Multiple Data (SIMD) capabilities of contemporary CPUs to achieve high-throughput non-cryptographic hashing.
+Through a comprehensive analysis, including benchmarks and comparisons with existing methods, we demonstrate that GxHash significantly outperforms conventional algorithms in terms of speed and computational efficiency without compromising on security.
 The paper also explores the implications, limitations, and avenues for future research in this burgeoning field.
@@
 
+\subsection{ILP Techniques}
+
+While compilers and CPUs employ various techniques to optimize Instruction-Level Parallelism (ILP), their capabilities are often constrained by the inherent data dependencies in the code.
+It's for this reason that algorithmic design can be pivotal.
+By structuring algorithms to minimize dependency chains from the outset, we create opportunities for higher ILP that even the most advanced compiler optimizations and CPU features cannot achieve alone.
+Therefore, algorithmic design that is mindful of ILP can be a game-changer for performance optimization.
+\\\\
+\textbf{Example}\\
+Let's take a FNV-like hashing function.
+The "naive" way to process an array of elements would look like the \texttt{baseline} method, as shown in Rust snippet (Figure~\ref{fig:ilp_rust_example}).
+As we can see, every loop iteration requires the value of \texttt{h}, which has been computed the iteration before.
+Here we have a dependency chain, preventing the compiler from doing any optimization.
+
+To make ILP possible, for the function \texttt{temp} we unroll the loop and hash a few inputs altogether, independently from \texttt{h}, and mix it once thereafter with \texttt{h}.
+We still have a dependency chain on \texttt{h}, but for less iterations.
+The temporary hashes are independent and thus eligible for ILP.
+
+Another track taken for the function \texttt{laned} is to unroll the loop and hash on separate lanes, and then mix the lanes together upon exiting the loop.
+Each lane has its own dependency chain, but on less iterations.
+\\\\
+\textbf{Benchmark}\\
+Here are the timing on both an x86 and an ARM CPU.
+It also includes timing for the function \texttt{unrolled}, to show that performance increase comes indeed from ILP and not the loop unrolling itself.
+We can see that \texttt{temp} and \texttt{laned} performed equally, leveraging ILP for an almost x3 performance increase over the \texttt{baseline}.
+\\
+\begin{figure}[h]
+    \centering  % This command centers the table 
+    \begin{tabular}{|c|c|c|c|c|}
+        \hline
+        CPU & \texttt{baseline} & \texttt{unrolled} & \texttt{temp} & \texttt{laned} \\
+        \hline
+        AMD Ryzen 5 5625U (x86 64-bit) & 92.787 µs & 93.047 µs & 37.516 µs & 37.434 µs \\
+        Apple M1 Pro (ARM 64-bit) & ? & ? & ? & ? \\
+        \hline
+    \end{tabular}
+    \caption{Benchmark timings for ILP example}
+    \label{tab:your_table_label}
+\end{figure}
+
+\begin{figure}[h]
+    \begin{multicols}{2}
+        \begin{lstlisting}[language=Rust, style=boxed]
+const PRIME: u64 = 0x00000100000001b3;
+const OFFSET: u64 = 0xcbf29ce484222325;
+
+#[inline]
+fn hash(hash: u64, value: u64) -> u64 {
+    (hash ^ value) * PRIME
+}
+
+fn baseline(input: &[u64]) -> u64 {
+    let mut h = OFFSET;
+    let mut i: usize = 0;
+    while i < input.len() {
+        h = hash(h, input[i]);
+
+        i = i + 1;
+    }
+    h
+}
+
+fn unrolled(input: &[u64]) -> u64 {
+    let mut h: u64 = OFFSET;
+    let mut i: usize = 0;
+    while i < input.len() {
+        h = hash(h, input[i]);
+        h = hash(h, input[i + 1]);
+        h = hash(h, input[i + 2]);
+        h = hash(h, input[i + 3]);
+        h = hash(h, input[i + 4]);
+
+        i = i + 5;
+    }
+    h
+}
+        \end{lstlisting}
+        \columnbreak
+        \begin{lstlisting}[language=Rust, style=boxed]
+fn temp(input: &[u64]) -> u64 {
+    let mut h: u64 = OFFSET;
+    let mut i: usize = 0;
+    while i < input.len() {
+        let mut tmp: u64 = input[i];
+        tmp = hash(tmp, input[i + 1]);
+        tmp = hash(tmp, input[i + 2]);
+        tmp = hash(tmp, input[i + 3]);
+        tmp = hash(tmp, input[i + 4]);
+
+        h = hash(h, tmp);
+
+        i = i + 5;
+    }
+    h
+}
+
+fn laned(input: &[u64]) -> u64 {
+    let mut h1: u64 = OFFSET;
+    let mut h2: u64 = OFFSET;
+    let mut h3: u64 = OFFSET;
+    let mut h4: u64 = OFFSET;
+    let mut h5: u64 = OFFSET; 
+    let mut i: usize = 0;
+    while i < input.len() {
+        h1 = hash(h1, input[i]);
+        h2 = hash(h2, input[i + 1]);
+        h3 = hash(h3, input[i + 2]);
+        h4 = hash(h4, input[i + 3]);
+        h5 = hash(h5, input[i + 4]);
+
+        i = i + 5;
+    }
+    hash(hash(hash(hash(h1, h2), h3), h4), h5)
+}
+        \end{lstlisting}
+    \end{multicols}
+    \caption{FNV-like hash functions in Rust}
+    \label{fig:ilp_rust_example}
+\end{figure}
+
+\subsection{Laned Construction}
+
 In order to improve ILP, a construction can processes the message by groups of \( k_b \) blocks.
@@
 
-\subsection{Intermediate Hashes}
+\subsubsection{Intermediate Hashes}
 
@@
 \begin{align*}
-H_{1} &= f(\ldots f(f(0^{s_b}, M_1), M_2)\ldots, M_{k_b}), \\
-H_{2} &= f(\ldots f(f(0^{s_b}, M_{k_g+1}), M_{k_g+2})\ldots, M_{2k_b}), \\
+H_{1} &= f(\ldots f(f(f(0^{s_b}, M_{0k_b + 1}), M_{1k_b + 1}), M_{2k_b + 1})\ldots, M_{n_g + 1}) \\
+H_{2} &= f(\ldots f(f(f(0^{s_b}, M_{0k_b + 2}), M_{1k_b + 2}), M_{2k_b + 2})\ldots, M_{n_g + 2}) \\
 &\vdots \\
-H_{n_g} &= f(\ldots f(f(0^{s_b}, M_{n_g+1}), M_{n_g+2})\ldots, M_{n_g+k_b})
+H_{k_b} &= f(\ldots f(f(f(0^{s_b}, M_{0k_b + k_b}), M_{1k_b + k_b}), M_{2k_b + k_b})\ldots, M_{n_g + k_b}) \\
 \end{align*}
 
-\subsection{Final Hash}
+\subsubsection{Final Hash}
 
@@
 \begin{equation*}
-h(M) = g\left( f( \ldots f(f(\ldots f(f(0^s, H_1), H_2) \ldots, H_{n_g}), M_{4{n_g}+1}) \ldots, M_{n_b} ) \right).
+h(M) = g\left( f( \ldots f(f(\ldots f(f(0^{s_b}, H_1), H_2) \ldots, H_{k_b}), M_{{k_b}{n_g}+1}) \ldots, M_{n_b} ) \right).
 \end{equation*}
 
-\section{TurboGx Hashing Algorithm}
+\section{GxHash Algorithm}
 
-The \textbf{TurboGx} hashing algorithm employs an high ILP construction as described in section \ref{highilp}.
+The \textbf{GxHash} hashing algorithm employs an high ILP construction as described in section \ref{highilp}.
 In practice, this construction not only enables instruction level paralellism but also enables loop unrolling, disminishing the looping overhead, thus maximizing computational efficiency and overall performance.

### 2023-09-18 article/rust-listings.tex
More writing

@@
 \lstdefinestyle{colouredRust}%
-{ basicstyle=\ttfamily%
+{ basicstyle=\fontsize{9}{9}\ttfamily\selectfont,%
 , identifierstyle=%

### 2023-09-18 benches/ilp.rs

@@ -1,86 +1,87 @@
-
 use criterion::{black_box, criterion_group, criterion_main, Criterion};
 
+const PRIME: u64 = 0x00000100000001b3;
+const OFFSET: u64 = 0xcbf29ce484222325;
+
 #[inline]
-fn dohash(hash: usize, value: usize) -> usize {
-    hash * value + value
+fn hash(hash: u64, value: u64) -> u64 {
+    (hash ^ value) * PRIME
 }
 
-fn simple_loop(input: &[usize]) -> usize {
-    let mut hash = 0;
+fn baseline(input: &[u64]) -> u64 {
+    let mut h = OFFSET;
     let mut i: usize = 0;
     while i < input.len() {
-        hash = dohash(hash, input[i]);
+        h = hash(h, input[i]);
 
         i = i + 1;
     }
-    hash
+    h
 }
 
-fn unrolled_loop(input: &[usize]) -> usize {
-    let mut hash: usize = 0;
+fn unrolled(input: &[u64]) -> u64 {
+    let mut h: u64 = OFFSET;
     let mut i: usize = 0;
     while i < input.len() {
-        hash = dohash(hash, input[i]);
-        hash = dohash(hash, input[i + 1]);
-        hash = dohash(hash, input[i + 2]);
-        hash = dohash(hash, input[i + 3]);
-        hash = dohash(hash, input[i + 4]);
+        h = hash(h, input[i]);
+        h = hash(h, input[i + 1]);
+        h = hash(h, input[i + 2]);
+        h = hash(h, input[i + 3]);
+        h = hash(h, input[i + 4]);
 
         i = i + 5;
     }
-    hash
+    h
 }
 
-fn unrolled_temp_loop(input: &[usize]) -> usize {
-    let mut hash: usize = 0;
+fn temp(input: &[u64]) -> u64 {
+    let mut h: u64 = OFFSET;
     let mut i: usize = 0;
     while i < input.len() {
-        let mut temp_hash: usize = 0;
-        temp_hash = dohash(temp_hash, input[i]);
-        temp_hash = dohash(temp_hash, input[i + 1]);
-        temp_hash = dohash(temp_hash, input[i + 2]);
-        temp_hash = dohash(temp_hash, input[i + 3]);
-        temp_hash = dohash(temp_hash, input[i + 4]);
+        let mut tmp: u64 = input[i];
+        tmp = hash(tmp, input[i + 1]);
[…]

### 2023-09-19 article/article.tex
Update article.tex

@@
 
-Most modern general-purpose CPUs employ a superscalar architecture which enables instruction level parallelism (ILP). 
+Most modern general-purpose CPUs employ a superscalar architecture which enables Instruction-Level Parallelism (ILP). 
 Minimizing dependencies in an algorithm allows a superscalar processor to execute more instructions concurrently, thus maximizing its inherent parallelism and overall performance.
@@
 
-\subsection{ILP Techniques}
+\subsection{ILP Awareness}
 
-While compilers and CPUs employ various techniques to optimize Instruction-Level Parallelism (ILP), their capabilities are often constrained by the inherent data dependencies in the code.
+While compilers and CPUs employ various techniques to optimize ILP, their capabilities are often constrained by the inherent data dependencies in the code.
 It's for this reason that algorithmic design can be pivotal.
@@
 It also includes timing for the function \texttt{unrolled}, to show that performance increase comes indeed from ILP and not the loop unrolling itself.
-We can see that \texttt{temp} and \texttt{laned} performed equally, leveraging ILP for an almost x3 performance increase over the \texttt{baseline}.
+We can see that \texttt{temp} and \texttt{laned} performed equally, leveraging ILP for a significant performance increase over the \texttt{baseline}.
 \\
@@
         AMD Ryzen 5 5625U (x86 64-bit) & 92.787 µs & 93.047 µs & 37.516 µs & 37.434 µs \\
-        Apple M1 Pro (ARM 64-bit) & ? & ? & ? & ? \\
+        Apple M1 Pro (ARM 64-bit) & 125.23 µs & 124.42 µs & 28.507 µs & 30.716 µs \\
         \hline
@@
 \end{figure}
+\\
+While the \texttt{temp} and \texttt{laned} functions won't yield exactly the same hashes as the \texttt{baseline}, they serve the same purpose, while being much faster.
+The following section will delve more in depth onto the definition of such an high ILP construction, for performance critical scenarios.
 

### 2023-09-19 benches/throughput.rs
Use power for bench len

@@ -8,7 +8,6 @@ use rand::Rng;
 
 fn gxhash_benchmark(c: &mut Criterion) {
     let mut rng = rand::thread_rng();
-    let mut len = 1;
     let mut group = c.benchmark_group("gxhash");
 
     // Allocate 32-bytes-aligned
@@ -19,8 +18,8 @@ fn gxhash_benchmark(c: &mut Criterion) {
     // Fill with random bytes
     rng.fill(slice);
 
-    for _ in 1..9 {
-        len *= 4;
+    for i in 1..9 {
+        let len = usize::pow(4, i);
 
         group.throughput(Throughput::Bytes(len as u64));
 

### 2023-09-19 src/gxhash.rs

@@ -157,7 +157,7 @@ pub fn gxhash(input: &[u8]) -> u32 {
             }
         
             hash_vector = compress(compress(compress(compress(compress(compress(compress(s0, s1), s2), s3), s4), s5), s6), s7);
-            
+
             let remaining_blocks_count: isize = (len / VECTOR_SIZE) - unrollable_blocks_count;
             end_address = v.offset(remaining_blocks_count) as usize;
         }

### 2023-09-19 article/article.tex
Update article.tex

@@
-\documentclass[11pt]{article} 
-\usepackage[margin=0.8in]{geometry} % Sets all margins to 1 inch
+\documentclass[10pt]{article} 
+\usepackage[margin=0.8in]{geometry}
 \usepackage{amsmath}
@@
 
-\input{rust-listings.tex}  % Include the language definition
+\input{rust-listings.tex}
 
@@
 Traditional hashing methods, while effective, often fail to fully utilize the computational capabilities of modern processors.
-This paper introduces the GxHash hashing algorithm, a novel approach that harnesses the power of high instruction-level parallelism (ILP) and Single Instruction, Multiple Data (SIMD) capabilities of contemporary CPUs to achieve high-throughput non-cryptographic hashing.
-Through a comprehensive analysis, including benchmarks and comparisons with existing methods, we demonstrate that GxHash significantly outperforms conventional algorithms in terms of speed and computational efficiency without compromising on security.
-The paper also explores the implications, limitations, and avenues for future research in this burgeoning field.
+This paper introduces the GxHash hashing algorithm, a novel approach that harnesses the power of high instruction-level parallelism (ILP) and Single
+Instruction, Multiple Data (SIMD) capabilities of contemporary CPUs to achieve high-throughput non-cryptographic hashing. Through a comprehensive
+analysis, including benchmarks and comparisons with existing methods, we demonstrate that GxHash significantly outperforms conventional algorithms
+in terms of speed and computational efficiency without compromising on security. The paper also explores the implications, limitations, and avenues
+for future research in this burgeoning field.
 
@@
 \begin{itemize}
-    \item Input \( M \) is a binary message composed of \( n_b \) blocks of size \( s_b \), such as \( M = M_1 \parallel M_2 \parallel \ldots \parallel M_{n_b} \).
+    \item Input \( M \) is a binary message composed of \( n_b \) blocks of size \( s_b \),
+    such as \( M = M_1 \parallel M_2 \parallel \ldots \parallel M_{n_b} \).
     \item Output is a binary hash of size \( s_h \).
@@
 
-\subsection{Merkle–Damgård Construction}
+\subsection{The Merkle–Damgård Construction}
 
@@
 
-\subsection{Wide-Pipe Construction} \label{widepipe}
+\subsection{The Wide-Pipe Construction} \label{widepipe}
 
@@
 \end{align*}
-By taking in a larger internal chaining value, the algorithm strengthens the integrity of the hash function, making it more challenging to reverse-engineer or compromise.
+By taking in a larger internal chaining value, the algorithm strengthens the integrity of the hash function,
+making it more challenging to reverse-engineer or compromise.
 
@@
 Most modern general-purpose CPUs employ a superscalar architecture which enables Instruction-Level Parallelism (ILP). 
-Minimizing dependencies in an algorithm allows a superscalar processor to execute more instructions concurrently, thus maximizing its inherent parallelism and overall performance.
-The key limitation for ILP in the Merkle–Damgård construction is the inherent sequential dependency: each block's hash depends on the result of hashing the previous block.
+Minimizing dependencies in an algorithm allows a superscalar processor to execute more instructions concurrently,
+thus maximizing its inherent parallelism and overall performance.
+The key limitation for ILP in the Merkle–Damgård construction is the inherent sequential dependency:
+each block's hash depends on the result of hashing the previous block.
 
@@
 
-While compilers and CPUs employ various techniques to optimize ILP, their capabilities are often constrained by the inherent data dependencies in the code.
-It's for this reason that algorithmic design can be pivotal.
-By structuring algorithms to minimize dependency chains from the outset, we create opportunities for higher ILP that even the most advanced compiler optimizations and CPU features cannot achieve alone.
-Therefore, algorithmic design that is mindful of ILP can be a game-changer for performance optimization.
-\\\\
-\textbf{Example}\\
-Let's take a FNV-like hashing function.
-The "naive" way to process an array of elements would look like the \texttt{baseline} method, as shown in Rust snippet (Figure~\ref{fig:ilp_rust_example}).
-As we can see, every loop iteration requires the value of \texttt{h}, which has been computed the iteration before.
-Here we have a dependency chain, preventing the compiler from doing any optimization.
+While compilers and CPUs employ various techniques to optimize ILP, their capabilities are often constrained by the inherent data dependencies
+in the code. It's for this reason that algorithmic design can be pivotal. By structuring algorithms to minimize dependency chains from the outset,
+we create opportunities for higher ILP that even the most advanced compiler optimizations and CPU features cannot achieve alone. Therefore,
+algorithmic design that is mindful of ILP can be a game-changer for performance optimization.
 
-To make ILP possible, for the function \texttt{temp} we unroll the loop and hash a few inputs altogether, independently from \texttt{h}, and mix it once thereafter with \texttt{h}.
-We still have a dependency chain on \texttt{h}, but for less iterations.
+\subsubsection{Example}
+Let's take a FNV-like hashing function. The "naive" way to process an array of elements would look like the \texttt{baseline} method,
+as shown in Rust snippet (Figure~\ref{fig:ilp_rust_example}). As we can see, every loop iteration requires the value of \texttt{h},
+which has been computed the iteration before. Here we have a dependency chain, preventing the compiler from doing any optimization.
+
+To make ILP possible, for the function \texttt{temp} we unroll the loop and hash a few inputs altogether, independently from \texttt{h},
+and mix it once thereafter with \texttt{h}. We still have a dependency chain on \texttt{h}, but for less iterations.
 The temporary hashes are independent and thus eligible for ILP.
 
-Another track taken for the function \texttt{laned} is to unroll the loop and hash on separate lanes, and then mix the lanes together upon exiting the loop.
-Each lane has its own dependency chain, but on less iterations.
-\\\\
-\textbf{Benchmark}\\
-Here are the timing on both an x86 and an ARM CPU.
-It also includes timing for the function \texttt{unrolled}, to show that performance increase comes indeed from ILP and not the loop unrolling itself.
-We can see that \texttt{temp} and \texttt{laned} performed equally, leveraging ILP for a significant performance increase over the \texttt{baseline}.
-\\
-\begin{figure}[h]
-    \centering  % This command centers the table 
-    \begin{tabular}{|c|c|c|c|c|}
-        \hline
-        CPU & \texttt{baseline} & \texttt{unrolled} & \texttt{temp} & \texttt{laned} \\
-        \hline
-        AMD Ryzen 5 5625U (x86 64-bit) & 92.787 µs & 93.047 µs & 37.516 µs & 37.434 µs \\
-        Apple M1 Pro (ARM 64-bit) & 125.23 µs & 124.42 µs & 28.507 µs & 30.716 µs \\
-        \hline
-    \end{tabular}
-    \caption{Benchmark timings for ILP example}
-    \label{tab:your_table_label}
-\end{figure}
-\\
-While the \texttt{temp} and \texttt{laned} functions won't yield exactly the same hashes as the \texttt{baseline}, they serve the same purpose, while being much faster.
-The following section will delve more in depth onto the definition of such an high ILP construction, for performance critical scenarios.
+Another track taken for the function \texttt{laned} is to unroll the loop and hash on separate lanes,
+and then mix the lanes together upon exiting the loop. Each lane has its own dependency chain, but on less iterations.
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \begin{multicols}{2}
@@
 
-\subsection{Laned Construction}
+\clearpage
+\subsubsection{Benchmark}
+Here are the timing on both an x86 and an ARM CPU. It also includes timing for the function \texttt{unrolled},
+to show that performance increase comes indeed from ILP and not the loop unrolling itself.
+We can see that \texttt{temp} and \texttt{laned} performed equally, leveraging ILP for a significant performance increase over the \texttt{baseline}.
+\\
+\begin{figure}[ht]
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+CPU & \texttt{baseline} & \texttt{unrolled} & \texttt{temp} & \texttt{laned} \\
+\hline
+AMD Ryzen 5 5625U (x86 64-bit) & 92.787 µs & 93.047 µs & 37.516 µs & 37.434 µs \\
+Apple M1 Pro (ARM 64-bit) & 125.23 µs & 124.42 µs & 28.507 µs & 30.716 µs \\
+\hline
+\end{tabular}
+\caption{Benchmark timings for ILP example}
+\label{tab:your_table_label}
+\end{figure}
+\\
+While the \texttt{temp} and \texttt{laned} functions won't yield exactly the same hashes as the \texttt{baseline},
+they serve the same purpose, while being much faster.
+Both approaches have they pro and cons. As the \texttt{laned} explicitely declares \( n \) variables for our lanes,
+this approach is simpler in regards to compiler analysis and is thus more likely to benefit from ILP,
+regardless of the compiler or programming language used.
+The following section will delve more in depth onto the definition of a \textbf{Laned Construction}.
 
-In order to improve ILP, a construction can processes the message by groups of \( k_b \) blocks.
-This way, each group is hashed independently and intermediate hashes are compressed altogether thereafter.
+\clearpage
+\subsection{The Laned Construction}
+
+The \textbf{Laned Construction} introduces \( k_b \) lanes, and processes the message by groups of \( k_b \) blocks,
+so that for a given group each of the \( k_b \) block and be processed on its own lane.
+This way, we have \( k_b \) independent dependency chains. The lane hashes can then be compressed altogether thereafter upon exiting the loop.
 
@@
 Let's define \( n_g = \lfloor {n_b}/{k_b} \rfloor \) as the number of whole groups of \( k_b \) message blocks. \\
-For each group we compute an intermediate hash, \( H_i \), as follows:
+For each lane we compute an intermediate hash, \( H_i \), as follows:
 
@@
 
-The final hash \( H \) is calculated using \( f \) to compress the intermediate hashes and the remaining message blocks (if any), which is then passed through \( g \):
+The final hash \( H \) is calculated using \( f \) to compress the intermediate hashes and the remaining message blocks (if any),
+which is then passed through \( g \):
 
@@
 
-\section{GxHash Algorithm}
+\section{The GxHash Algorithm}
 
-The \textbf{GxHash} hashing algorithm employs an high ILP construction as described in section \ref{highilp}.
-In practice, this construction not only enables instruction level paralellism but also enables loop unrolling, disminishing the looping overhead, thus maximizing computational efficiency and overall performance.
+The \textbf{GxHash} hashing algorithm employs an high ILP construction as described in section \ref{highilp}. In practice,
+this construction not only enables instruction level paralellism but also enables loop unrolling, disminishing the looping overhead,
+thus maximizing computational efficiency and overall performance.
 
@@
 
-\textbf{Merkle–Damgård} and derivatives can actually handle message of an arbitrary size \( s_m \) by padding the message upfront with the padding function \( p: \{0,1\}^{s_m} \to \{0,1\}^{n_b \times s_b} \) where \( n_b = \lceil s_m/s_b \rceil \).
+\textbf{Merkle–Damgård} and derivatives can actually handle message of an arbitrary size \( s_m \) by padding the message upfront with the padding
+function \( p: \{0,1\}^{s_m} \to \{0,1\}^{n_b \times s_b} \) where \( n_b = \lceil s_m/s_b \rceil \).
 

### 2023-09-19 article/article.tex
Add some references

@@
 \usepackage{multicol}
+\usepackage{graphicx}
 
@@
 
-\colorbox{yellow}{TODO}
-
-\begin{lstlisting}[language=Rust, style=boxed]
-use std::hint::black_box;
-
-fn sum1(x: u32) -> u32 {
-    let mut sum = x;
-    for i in 0..1000 {
-        sum = black_box(sum + i);
-    }
-    sum
-}
-\end{lstlisting}
+As a software engineer at Equativ, a company specializing in high-performance AdServing backends that handle billions of auctions daily,
+I face unique challenges in maximizing throughput while minimizing latency. In this high-stakes environment, every millisecond counts,
+and the performance of underlying data structures becomes critically important. We heavily rely on in-memory caches and other hash-based data structures,
+making the efficiency of hashing algorithms a non-trivial concern in our system's overall performance.\\\\
+While diving into the theory of hashing out of both necessity and intellectual curiosity, I discovered that existing hashing algorithms,
+including those built on well-known constructions like Merkle–Damgård, are not optimized to exploit the full capabilities of modern general-purpose CPUs.
+These CPUs offer advanced features such as Single Instruction, Multiple Data (SIMD) and Instruction-Level Parallelism (ILP), which remain largely untapped
+by current hashing methods.\\\\
+The challenge of creating a faster, more efficient hashing algorithm became not just a professional necessity but also a personal quest.
+It was both challenging and exhilarating to delve into hashing theory and experiment with new approaches. The result is what I believe to be the fastest
+non-cryptographic hashing algorithm developed to date.\\\\
+The primary motivation behind this research is to bridge the existing performance gap by designing a hashing algorithm that fully leverages SIMD and ILP
+capabilities. The aim is to achieve an order-of-magnitude improvement in hashing speed, thereby revolutionizing the efficiency of various applications,
+from databases to real-time analytics and beyond.\\\\
+In summary, this work is driven by both the practical needs of my professional environment and a personal passion for pushing the boundaries of what is
+technically possible in the realm of hashing algorithms.
 
@@
 
+The field of hashing algorithms has been a subject of extensive research and development, tracing its roots back to foundational architectures like
+the \textbf{Merkle–Damgård} Construction\cite{merkle}\cite{damgard}, introduced in 1989. Over the years, this area has seen a plethora of innovations, each attempting to address various
+aspects of hashing—be it collision resistance, distribution uniformity, or computational efficiency. While cryptographic hashing has often been the focal
+point of research, non-cryptographic hashing algorithms have also garnered attention for their utility in data structures like hashmaps and caches.
+
+In this section, we will explore some of the seminal works and recent advancements in the realm of hashing algorithms to contextualize
+our research.
+
+\subsection{The Merkle–Damgård Construction}
+
+The Merkle–Damgård construction serves as the foundational architecture for many existing hash functions.
+It operates by breaking down an input into fixed-size blocks, which are then processed sequentially through a compression
+function. The output of each block feeds into the next, culminating in a final, fixed-size hash.\\\\
+
 Let \( h: \{0,1\}^{n_b \times s_b} \to \{0,1\}^{s_h} \) be a cryptographic hash function where: 
-
 \begin{itemize}
@@
 
-\subsection{The Merkle–Damgård Construction}
-
-In the \textbf{Merkle–Damgård} construction, given:
+The Merkle–Damgård construction can be formalized like so. Given:
 \begin{itemize}
@@
 \end{align*}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=1\textwidth]{linear-construction.png}
+\caption{Merkle–Damgård Construction Overview}
+\label{fig:linear-construction}
+\end{figure}
 
@@
 
-\href{https://www.researchgate.net/publication/322094216_Merkle-Damgard_Construction_Method_and_Alternatives_A_Review}{Alternatives}.
+\cite{merkle_damgard_alternatives_review}
 
+\clearpage
 \section{High ILP Construction} \label{highilp}
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=1\textwidth]{laned-construction.png}
+\caption{Laned Construction Overview}
+\label{fig:linear-construction}
+\end{figure}
+
 \section{The GxHash Algorithm}
@@
 
+\bibliography{references}
+\bibliographystyle{plain}
+
 \end{document}

### 2023-09-20 article/article.tex
More latex

@@
 
+\subsection{Scope Limitation}
+
+This paper primarily investigates methods for enhancing the throughput of non-cryptographic hashing algorithms,
+which are commonly used in a variety of time-sensitive applications, including but not limited to hashmap lookups.
+In such contexts, hash computation is often expected to be extremely fast, typically requiring execution times ranging
+from nanoseconds to microseconds. Given these considerations, the paper intentionally excludes Thread-Level Parallelism
+(TLP) as a viable strategy for performance optimization.\\\\
+Firstly, it's worth mentioning that TLP is orthogonal to the methods being explored in this paper.
+TLP focuses on optimizing coarser-grained operations by distributing tasks across multiple threads,
+which doesn't directly align with the fine-grained performance improvements we aim to achieve.\\\\
+Secondly, introducing TLP would necessitate the incorporation of task scheduling, synchronization, and context switching.
+These overheads, while perhaps manageable in applications that can afford greater latencies, become less justifiable when
+aiming for high-throughput, low-latency operations that are typical in non-cryptographic hashing scenarios.\\\\
+In summary, while TLP might be a suitable performance optimization strategy in other computational contexts, we chose to
+leave it aside in this paper.
+
+\subsubsection{Portability}
+
+\clearpage
 \section{Related Work}
@@
 
-\subsection{The Merkle–Damgård Construction}
+\subsection{The Merkle--Damgård Construction}
 
@@
 function. The output of each block feeds into the next, culminating in a final, fixed-size hash.\\\\
-
-Let \( h: \{0,1\}^{n_b \times s_b} \to \{0,1\}^{s_h} \) be a cryptographic hash function where: 
+To formalize it, let us denote a hash function \( h: \{0,1\}^{n_b \times s_b} \to \{0,1\}^{s_h} \), where:
 \begin{itemize}
-    \item Input \( M \) is a binary message composed of \( n_b \) blocks of size \( s_b \),
-    such as \( M = M_1 \parallel M_2 \parallel \ldots \parallel M_{n_b} \).
-    \item Output is a binary hash of size \( s_h \).
+    \item \( M \) represents an input message that is divided into \( n_b \) blocks, each of \( s_b \) bits. In formal notation, \( M = M_1 \parallel M_2 \parallel \cdots \parallel M_{n_b} \).
+    \item The output is a hash value with a fixed bit-length \( s_h \).
+\end{itemize}
+Before proceeding to the formal definition, we need to establish the key functional components that constitute the Merkle--Damgård architecture:
+\begin{itemize}
+    \item A compression function \( f: \{0,1\}^{s_b} \times \{0,1\}^{s_b} \to \{0,1\}^{s_b} \),
+    \item A finalization function \( g: \{0,1\}^{s_b} \to \{0,1\}^{s_h} \),
+    \item An initialization vector \( 0^{s_b} \), comprised of \( s_b \) zero bits,
 \end{itemize}
 
-The Merkle–Damgård construction can be formalized like so. Given:
-\begin{itemize}
-    \item The compression function \( f: \{0,1\}^{s_b} \times \{0,1\}^{s_b} \to \{0,1\}^{s_b} \)
-    \item The pipe function \( g: \{0,1\}^{s_b} \to \{0,1\}^{s_h} \)
-    \item A zero-filled vector \( 0^{s_b} \) of length \( s_b \)
-\end{itemize}
-The hash function \( h \) can be expressed as:
+With these components, the hash function \( h \) may be articulated as follows:
 \begin{align*}
-    h(M) &= g\left( f(\ldots f(f(0^{s_b}, M_1), M_2) \ldots, M_{n_b}) \right)
+    h(M) &= g\left( f(\cdots f(f(0^{s_b}, M_1), M_2) \cdots, M_{n_b}) \right)
 \end{align*}
@@
 
-\subsection{The Wide-Pipe Construction} \label{widepipe}
+\subsection{The Wide-Pipe Construction Variant} \label{widepipe}
 
-The \textbf{Merkle–Damgård} construction has certain limitations, such as susceptibility to length extension and multicollision attacks.
-To address these issues, a variant known as the \textbf{wide-pipe} construction was introduced.
-This construction employs a larger internal state, so that:
+The \textbf{Wide-Pipe} construction serves as a variant of the traditional Merkle–Damgård architecture and aims to improve the hash
+function's cryptographic resilience.\\\\
+The standard Merkle–Damgård construction has been found vulnerable to certain types of cryptographic attacks, including length extension
+and multicollision attacks. The Wide-Pipe variant mitigates these vulnerabilities by modifying the hash function's internal state.
+In this construction, the size of the internal state (\(s_b\)) is deliberately made much larger than the size of the hash output
+(\(s_h\)), as expressed by the inequality:
 \begin{align*}
@@
 \end{align*}
-By taking in a larger internal chaining value, the algorithm strengthens the integrity of the hash function,
-making it more challenging to reverse-engineer or compromise.
 
-\subsection{Alternatives}
+This design choice serves to complicate potential attack vectors by introducing a greater level of computational complexity.
+As a result, the hash function gains increased resistance against certain types of attacks that exploit the limitations of the
+Merkle–Damgård construction.\\\\
+While performance remains our primary focus, the algorithm we examine in this paper incorporates the Wide-Pipe idea. By doing so,
+it offers a dual advantage: performance efficacy, which is central to this study, along with a good cryptographic resilience,
+which is an indeniable advantage even in the realm of non-cryptographic hash functions.
 
-\cite{merkle_damgard_alternatives_review}
+\subsection{Other Variants}
+
+While the classical Merkle–Damgård construction provides a reliable framework for cryptographic hash functions,
+there are a wide number of variants\cite{merkle_damgard_alternatives_review}. In this section, we discuss around some
+of the most popular variants around opportunities for performance enhancement.
+
+\subsubsection{Sponge Construction}
+
+The Sponge construction,  proceeds in two phases: absorption and squeezing.
+During the absorption phase, blocks of input data are XORed into a portion of the internal state,
+followed by a cryptographic permutation of the entire state. Importantly, each absorption step is inherently sequential,
+as it relies on the state resulting from the cryptographic permutation of the previous step. Consequently,
+the algorithm does cannot benefit from instruction-level parallelism during the absorption phase.
+The squeezing phase, which follows the absorption of all input blocks, generates the output hash from the internal state.
+The opportunity for parallelization with the Sponge construction is thus constrained by its sequential nature during the absorbing phase.
+
+\subsubsection{HAIFA Construction}
+
+The HAsh Iterative FrAmework (HAIFA) not only mitigates vulnerabilities but also incorporates features like support for a configurable number of rounds and real-time incremental hashing.
+However, like the standard Merkle–Damgård and Sponge constructions, the HAsh Iterative FrAmework (HAIFA) is also inherently sequential in its processing of message blocks.
+Each iteration of the compression function in HAIFA depends on the outcome of the previous iteration.
+This dependency chain means that the construction does not naturally lend itself to instruction-level parallelism (ILP),
+although other types of optimizations may still be possible depending on the specific implementation and hardware architecture.
+
+\subsubsection{Tree Hashing}
+
+Tree hashing breaks the input message into smaller fragments and processes them independently in a tree-like structure.
+While tree-based hashing constructions offer a degree of parallelism, it is essential to recognize their inherent limitations.
+The extent of parallelization diminishes progressively as we move upward through the tree, owing to the dependencies between higher-level nodes.
+Here's a breakdown:
+
+\begin{itemize}
+\item \textbf{Leaf Level:} At this level, all blocks are independent, allowing the hashing operations to occur in parallel.
+If \( n \) is the number of leaves, then \( \frac{n}{2} \) parallel operations can occur for an even \( n \), or \( \frac{n-1}{2} + 1 \) for an odd \( n \).
+\item \textbf{Second Level and Above:} The second level requires the hash results from the first level.
+Each node at the second level depends on two nodes from the level below, effectively halving the potential parallelism.
+This pattern of diminishing parallelization continues in subsequent levels.
+\item \textbf{Final Level:} At the top of the tree, we are left with a single hash that relies on the two hashes beneath it. This operation is inherently sequential.
+\end{itemize}
+
+Although the tree-based hashing approach has a theoretical advantage in parallelization, practical implementations often face several challenges that can impact efficiency.
+These issues can make tree hashing hardly as efficient as a sequential structure for certain applications.
+Here are the primary factors:
+
+\begin{itemize}
+\item \textbf{Synchronization Overhead:} The parallel nature of the algorithm necessitates synchronization between different processing threads or units, especially at higher tree levels where dependencies exist.
+This overhead counters the gains from parallelization.
+\item \textbf{Memory Consumption:} Tree constructions typically require more memory to store intermediate hash values, particularly when branching factors are high.
+Memory allocation and fragmentation usually impact performance.
+\item \textbf{Cache Efficiency:} Unlike sequential algorithms that can benefit from cache locality, the tree-based approach often has to handle multiple non-contiguous data blocks, potentially leading to cache misses and reduced efficiency.
+\item \textbf{Implementation Complexity:} The algorithmic and data-structure requirements for implementing tree-based hashing are more complex than those of a straightforward sequential hashing algorithm.
+The increased complexity can introduce more room for errors and maintenance challenges.
+\end{itemize}
+
+In light of these practical challenges, tree-based constructions might not be the best fit given our high performance goals and the architecture of today's general purpose computers.
 
@@
 to show that performance increase comes indeed from ILP and not the loop unrolling itself.
-We can see that \texttt{temp} and \texttt{laned} performed equally, leveraging ILP for a significant performance increase over the \texttt{baseline}.
+We can see that \texttt{temp} and \texttt{laned} performed equally, leveraging ILP for a significant performance increase
+over the \texttt{baseline}.
 \\
@@
 so that for a given group each of the \( k_b \) block and be processed on its own lane.
-This way, we have \( k_b \) independent dependency chains. The lane hashes can then be compressed altogether thereafter upon exiting the loop.
+This way, we have \( k_b \) independent dependency chains. The lane hashes can then be compressed altogether thereafter upon
+exiting the loop.
 
@@
 this construction not only enables instruction level paralellism but also enables loop unrolling, disminishing the looping overhead,
-thus maximizing computational efficiency and overall performance.
+thus maximizing computational efficiency and overall performance.\\\\
+With that ILP unlocked, we still have to define f and g. In our quest for high-thoughput, it is essential for us to find computationally
+efficient definitions TODO
 
@@
 
+\textbf{Merkle–Damgård} and derivatives can actually handle message of an arbitrary size \( s_m \) by padding the message upfront with the padding
+function \( p: \{0,1\}^{s_m} \to \{0,1\}^{n_b \times s_b} \) where \( n_b = \lceil s_m/s_b \rceil \).
+
+In practice, implementing \( p \) in computer code implies memory copies. Instead, TODO
+
 \subsubsection{Low-Overhead Looping}
@@
 \subsubsection{CPU Alignement}
-
-\textbf{Merkle–Damgård} and derivatives can actually handle message of an arbitrary size \( s_m \) by padding the message upfront with the padding
-function \( p: \{0,1\}^{s_m} \to \{0,1\}^{n_b \times s_b} \) where \( n_b = \lceil s_m/s_b \rceil \).
-
-In practice, implementing \( p \) in computer code implies memory copies. Instead, TODO
 

### 2023-09-21 benches/throughput.rs
Prepare for windows benchmark

@@ -18,7 +18,7 @@ fn gxhash_benchmark(c: &mut Criterion) {
     // Fill with random bytes
     rng.fill(slice);
 
-    for i in 1..9 {
+    for i in 1..8 {
         let len = usize::pow(4, i);
 
         group.throughput(Throughput::Bytes(len as u64));
@@ -28,10 +28,10 @@ fn gxhash_benchmark(c: &mut Criterion) {
             bencher.iter(|| black_box(gxhash(input)))
         });
 
-        let unaligned_slice = &slice[1..len];
-        group.bench_with_input(format!("{} bytes (unaligned)", len), unaligned_slice, |bencher, input| {
-            bencher.iter(|| black_box(gxhash(input)))
-        });
+        // let unaligned_slice = &slice[1..len];
+        // group.bench_with_input(format!("{} bytes (unaligned)", len), unaligned_slice, |bencher, input| {
+        //     bencher.iter(|| black_box(gxhash(input)))
+        // });
     }
 
     unsafe { dealloc(ptr, layout) };

### 2023-09-21 benches/ilp.rs
First commit (WIP) (#2)

@@ -1,0 +1,88 @@
+use criterion::{black_box, criterion_group, criterion_main, Criterion};
+
+const PRIME: u64 = 0x00000100000001b3;
+const OFFSET: u64 = 0xcbf29ce484222325;
+
+#[inline]
+fn hash(hash: u64, value: u64) -> u64 {
+    (hash ^ value) * PRIME
+}
+
+fn baseline(input: &[u64]) -> u64 {
+    let mut h = OFFSET;
+    let mut i: usize = 0;
+    while i < input.len() {
+        h = hash(h, input[i]);
+
+        i = i + 1;
+    }
+    h
+}
+
+fn unrolled(input: &[u64]) -> u64 {
+    let mut h: u64 = OFFSET;
+    let mut i: usize = 0;
+    while i < input.len() {
+        h = hash(h, input[i]);
+        h = hash(h, input[i + 1]);
+        h = hash(h, input[i + 2]);
+        h = hash(h, input[i + 3]);
+        h = hash(h, input[i + 4]);
+
+        i = i + 5;
+    }
+    h
+}
+
+fn temp(input: &[u64]) -> u64 {
+    let mut h: u64 = OFFSET;
+    let mut i: usize = 0;
+    while i < input.len() {
+        let mut tmp: u64 = input[i];
+        tmp = hash(tmp, input[i + 1]);
+        tmp = hash(tmp, input[i + 2]);
+        tmp = hash(tmp, input[i + 3]);
+        tmp = hash(tmp, input[i + 4]);
+
+        h = hash(h, tmp);
+
+        i = i + 5;
+    }
+    h
+}
+
+fn laned(input: &[u64]) -> u64 {
+    let mut h1: u64 = OFFSET;
+    let mut h2: u64 = OFFSET;
+    let mut h3: u64 = OFFSET;
+    let mut h4: u64 = OFFSET;
+    let mut h5: u64 = OFFSET; 
+    let mut i: usize = 0;
+    while i < input.len() {
+        h1 = hash(h1, input[i]);
+        h2 = hash(h2, input[i + 1]);
+        h3 = hash(h3, input[i + 2]);
+        h4 = hash(h4, input[i + 3]);
+        h5 = hash(h5, input[i + 4]);
+
+        i = i + 5;
+    }
+    hash(hash(hash(hash(h1, h2), h3), h4), h5)
+}
+
+use rand::Rng;
+
+fn ilp_benchmark(c: &mut Criterion) {
+    let mut rng = rand::thread_rng();
[…]

### 2023-09-21 src/main.rs

@@ -1,0 +1,12 @@
+use rand::Rng;
+
+use gxhash::gxhash;
+
+fn main() {
+
+    let mut rng = rand::thread_rng();
+    let mut random_bytes = [0u8; 16384]; // Create an array of 16 bytes, initialized to 0
+    rng.fill(&mut random_bytes[..]); // Fill the array with random bytes
+
+    println!("{}", gxhash(&random_bytes));
+}

### 2023-09-21 benches/throughput.rs
First commit (WIP) (#2)

@@ -1,0 +1,47 @@
+use std::time::Duration;
+use std::alloc::{alloc, dealloc, Layout};
+use std::slice;
+
+use criterion::{black_box, criterion_group, criterion_main, Criterion, Throughput};
+use gxhash::gxhash;
+use rand::Rng;
+
+fn gxhash_benchmark(c: &mut Criterion) {
+    let mut rng = rand::thread_rng();
+    let mut group = c.benchmark_group("gxhash");
+
+    // Allocate 32-bytes-aligned
+    let layout = Layout::from_size_align(100000, 32).unwrap();
+    let ptr = unsafe { alloc(layout) };
+    let slice: &mut [u8] = unsafe { slice::from_raw_parts_mut(ptr, 100000) };
+
+    // Fill with random bytes
+    rng.fill(slice);
+
+    for i in 1..8 {
+        let len = usize::pow(4, i);
+
+        group.throughput(Throughput::Bytes(len as u64));
+
+        let aligned_slice = &slice[0..len];
+        group.bench_with_input(format!("{} bytes (aligned)", len), aligned_slice, |bencher, input| {
+            bencher.iter(|| black_box(gxhash(input)))
+        });
+
+        // let unaligned_slice = &slice[1..len];
+        // group.bench_with_input(format!("{} bytes (unaligned)", len), unaligned_slice, |bencher, input| {
+        //     bencher.iter(|| black_box(gxhash(input)))
+        // });
+    }
+
+    unsafe { dealloc(ptr, layout) };
+}
+
+criterion_group! {
+    name = benches;
+    config = Criterion::default()
+        .sample_size(1000)
+        .measurement_time(Duration::from_secs(10));
+    targets = gxhash_benchmark,
+}
+criterion_main!(benches);

### 2023-09-21 src/gxhash.rs

@@ -1,0 +1,181 @@
+// For ARM architecture
+#[cfg(target_arch = "aarch64")]
+mod platform_defs {
+    use std::mem;
+    use core::arch::aarch64::*;
+
+    pub type state = int8x16_t;
+
+    #[inline]
+    pub unsafe fn create_empty() -> state {
+        vdupq_n_s8(0)
+    }
+    
+    #[inline]
+    pub unsafe fn prefetch(p: *const state) {
+        //__pld(p as *const i8);
+    }
+
+    #[inline]
+    pub unsafe fn load_unaligned(p: *const state) -> state {
+        vld1q_s8(p as *const i8)
+    }
+
+    #[inline]
+    pub unsafe fn get_partial(p: *const state, len: isize) -> state {
+        const MASK: [u8; 32] = [
+            0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF,
+            0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00 ];
+
+        let mask = vld1q_s8((MASK.as_ptr() as *const i8).offset(16 - len));
+        vandq_s8(load_unaligned(p), mask)
+    }
+
+    #[inline]
+    pub unsafe fn compress(a: state, b: state) -> state {
+        let sum: state = vaddq_s8(a, b);
+        vextq_s8(sum, sum, 1) 
+    }
+
+    #[inline]
+    pub unsafe fn mix(hash: state) -> state {
+        hash
+    }
+
+    #[inline]
+    pub unsafe fn fold(hash: state) -> u32 {
+        // Bit-cast the int8x16_t to uint32x4_t
+        let vec_u32: uint32x4_t = mem::transmute(hash);
+        // Get the first u32 value from the vector
+        vgetq_lane_u32(vec_u32, 3)
+    }
+}
+
+// For x86 architecture
+#[cfg(target_arch = "x86_64")]
+mod platform_defs {
+    use core::arch::x86_64::*;
+
+    pub type state = __m256i;
+
+    #[inline]
+    pub unsafe fn create_empty() -> state {
+        _mm256_setzero_si256()
+    }
+
+    #[inline]
[…]

### 2023-09-21 src/lib.rs

@@ -1,0 +1,6 @@
+#![feature(core_intrinsics)]
+#![feature(stdsimd)]
+
+mod gxhash;
+
+pub use gxhash::*;

### 2023-09-22 article/article.tex
Include citation
Add description of the GxHash algorithm

@@
 As a software engineer at Equativ, a company specializing in high-performance AdServing backends that handle billions of auctions daily,
-I face unique challenges in maximizing throughput while minimizing latency. In this high-stakes environment, every millisecond counts,
-and the performance of underlying data structures becomes critically important. We heavily rely on in-memory caches and other hash-based data structures,
-making the efficiency of hashing algorithms a non-trivial concern in our system's overall performance.\\\\
-While diving into the theory of hashing out of both necessity and intellectual curiosity, I discovered that existing hashing algorithms,
-including those built on well-known constructions like Merkle–Damgård, are not optimized to exploit the full capabilities of modern general-purpose CPUs.
-These CPUs offer advanced features such as Single Instruction, Multiple Data (SIMD) and Instruction-Level Parallelism (ILP), which remain largely untapped
-by current hashing methods.\\\\
+I face unique challenges in maximizing throughput while minimizing latency.
+In this high-stakes environment, every millisecond counts, and the performance of underlying data structures becomes critically important.
+We heavily rely on in-memory caches and other hash-based data structures, making the efficiency of hashing algorithms a non-trivial concern in our system's overall performance.\\\\
+While diving into the theory of hashing out of both necessity and intellectual curiosity, I discovered that existing hashing algorithms, including those built on well-known constructions like Merkle–Damgård, are not optimized to exploit the full capabilities of modern general-purpose CPUs.
+These CPUs offer advanced features such as Single Instruction, Multiple Data (SIMD) and Instruction-Level Parallelism (ILP), which remain largely untapped by current hashing methods.\\\\
 The challenge of creating a faster, more efficient hashing algorithm became not just a professional necessity but also a personal quest.
-It was both challenging and exhilarating to delve into hashing theory and experiment with new approaches. The result is what I believe to be the fastest
-non-cryptographic hashing algorithm developed to date.\\\\
-The primary motivation behind this research is to bridge the existing performance gap by designing a hashing algorithm that fully leverages SIMD and ILP
-capabilities. The aim is to achieve an order-of-magnitude improvement in hashing speed, thereby revolutionizing the efficiency of various applications,
-from databases to real-time analytics and beyond.\\\\
-In summary, this work is driven by both the practical needs of my professional environment and a personal passion for pushing the boundaries of what is
-technically possible in the realm of hashing algorithms.
+It was both challenging and exhilarating to delve into hashing theory and experiment with new approaches.
+The result is what I believe to be the fastest non-cryptographic hashing algorithm developed to date.\\\\
+The primary motivation behind this research is to bridge the existing performance gap by designing a hashing algorithm that fully leverages SIMD and ILP capabilities.
+The aim is to achieve an order-of-magnitude improvement in hashing speed, thereby revolutionizing the efficiency of various applications, from databases to real-time analytics and beyond.\\\\
+In summary, this work is driven by both the practical needs of my professional environment and a personal passion for pushing the boundaries of what is technically possible in the realm of hashing algorithms.
 
@@
 
-This paper primarily investigates methods for enhancing the throughput of non-cryptographic hashing algorithms,
-which are commonly used in a variety of time-sensitive applications, including but not limited to hashmap lookups.
-In such contexts, hash computation is often expected to be extremely fast, typically requiring execution times ranging
-from nanoseconds to microseconds. Given these considerations, the paper intentionally excludes Thread-Level Parallelism
+This paper primarily investigates methods for enhancing the throughput of non-cryptographic hashing algorithms, which are commonly used in a variety of time-sensitive applications, including but not limited to hashmap lookups.
+In such contexts, hash computation is often expected to be extremely fast, typically requiring execution times ranging from nanoseconds to microseconds.
+Given these considerations, the paper intentionally excludes Thread-Level Parallelism
 (TLP) as a viable strategy for performance optimization.\\\\
 Firstly, it's worth mentioning that TLP is orthogonal to the methods being explored in this paper.
-TLP focuses on optimizing coarser-grained operations by distributing tasks across multiple threads,
-which doesn't directly align with the fine-grained performance improvements we aim to achieve.\\\\
+TLP focuses on optimizing coarser-grained operations by distributing tasks across multiple threads, which doesn't directly align with the fine-grained performance improvements we aim to achieve.\\\\
 Secondly, introducing TLP would necessitate the incorporation of task scheduling, synchronization, and context switching.
-These overheads, while perhaps manageable in applications that can afford greater latencies, become less justifiable when
-aiming for high-throughput, low-latency operations that are typical in non-cryptographic hashing scenarios.\\\\
-In summary, while TLP might be a suitable performance optimization strategy in other computational contexts, we chose to
-leave it aside in this paper.
+These overheads, while perhaps manageable in applications that can afford greater latencies, become less justifiable when aiming for high-throughput, low-latency operations that are typical in non-cryptographic hashing scenarios.\\\\
+In summary, while TLP might be a suitable performance optimization strategy in other computational contexts, we chose to leave it aside in this paper.
 
@@
 
-The field of hashing algorithms has been a subject of extensive research and development, tracing its roots back to foundational architectures like
-the \textbf{Merkle–Damgård} Construction\cite{merkle}\cite{damgard}, introduced in 1989. Over the years, this area has seen a plethora of innovations, each attempting to address various
-aspects of hashing—be it collision resistance, distribution uniformity, or computational efficiency. While cryptographic hashing has often been the focal
-point of research, non-cryptographic hashing algorithms have also garnered attention for their utility in data structures like hashmaps and caches.
+The field of hashing algorithms has been a subject of extensive research and development, tracing its roots back to foundational architectures like the \textbf{Merkle–Damgård} Construction\cite{merkle}\cite{damgard}, introduced in 1989.
+Over the years, this area has seen a plethora of innovations, each attempting to address various aspects of hashing—be it collision resistance, distribution uniformity, or computational efficiency.
+While cryptographic hashing has often been the focal point of research, non-cryptographic hashing algorithms have also garnered attention for their utility in data structures like hashmaps and caches.
 
-In this section, we will explore some of the seminal works and recent advancements in the realm of hashing algorithms to contextualize
-our research.
+In this section, we will explore some of the seminal works and recent advancements in the realm of hashing algorithms to contextualize our research.
 
@@
 
-The \textbf{Wide-Pipe} construction serves as a variant of the traditional Merkle–Damgård architecture and aims to improve the hash
-function's cryptographic resilience.\\\\
-The standard Merkle–Damgård construction has been found vulnerable to certain types of cryptographic attacks, including length extension
-and multicollision attacks. The Wide-Pipe variant mitigates these vulnerabilities by modifying the hash function's internal state.
+The \textbf{Wide-Pipe} construction serves as a variant of the traditional Merkle–Damgård architecture and aims to improve the hash function's cryptographic resilience.\\\\
+The standard Merkle–Damgård construction has been found vulnerable to certain types of cryptographic attacks, including length extension and multicollision attacks.
+The Wide-Pipe variant mitigates these vulnerabilities by modifying the hash function's internal state.
 In this construction, the size of the internal state (\(s_b\)) is deliberately made much larger than the size of the hash output
@@
 This design choice serves to complicate potential attack vectors by introducing a greater level of computational complexity.
-As a result, the hash function gains increased resistance against certain types of attacks that exploit the limitations of the
-Merkle–Damgård construction.\\\\
-While performance remains our primary focus, the algorithm we examine in this paper incorporates the Wide-Pipe idea. By doing so,
-it offers a dual advantage: performance efficacy, which is central to this study, along with a good cryptographic resilience,
-which is an indeniable advantage even in the realm of non-cryptographic hash functions.
+As a result, the hash function gains increased resistance against certain types of attacks that exploit the limitations of the Merkle–Damgård construction.\\\\
+While performance remains our primary focus, the algorithm we examine in this paper incorporates the Wide-Pipe idea.
+By doing so, it offers a dual advantage: performance efficacy, which is central to this study, along with a good cryptographic resilience, which is an indeniable advantage even in the realm of non-cryptographic hash functions.
 
@@
 
-While the classical Merkle–Damgård construction provides a reliable framework for cryptographic hash functions,
-there are a wide number of variants\cite{merkle_damgard_alternatives_review}. In this section, we discuss around some
-of the most popular variants around opportunities for performance enhancement.
+While the classical Merkle–Damgård construction provides a reliable framework for cryptographic hash functions, there are a wide number of variants\cite{merkle_damgard_alternatives_review}.
+In this section, we discuss around some of the most popular variants around opportunities for performance enhancement.
 
@@
 The Sponge construction,  proceeds in two phases: absorption and squeezing.
-During the absorption phase, blocks of input data are XORed into a portion of the internal state,
-followed by a cryptographic permutation of the entire state. Importantly, each absorption step is inherently sequential,
-as it relies on the state resulting from the cryptographic permutation of the previous step. Consequently,
-the algorithm does cannot benefit from instruction-level parallelism during the absorption phase.
+During the absorption phase, blocks of input data are XORed into a portion of the internal state, followed by a cryptographic permutation of the entire state.
+Importantly, each absorption step is inherently sequential, as it relies on the state resulting from the cryptographic permutation of the previous step.
+Consequently, the algorithm does cannot benefit from instruction-level parallelism during the absorption phase.
 The squeezing phase, which follows the absorption of all input blocks, generates the output hash from the internal state.
@@
 Each iteration of the compression function in HAIFA depends on the outcome of the previous iteration.
-This dependency chain means that the construction does not naturally lend itself to instruction-level parallelism (ILP),
-although other types of optimizations may still be possible depending on the specific implementation and hardware architecture.
+This dependency chain means that the construction does not naturally lend itself to instruction-level parallelism (ILP), although other types of optimizations may still be possible depending on the specific implementation and hardware architecture.
 
@@
 Most modern general-purpose CPUs employ a superscalar architecture which enables Instruction-Level Parallelism (ILP). 
-Minimizing dependencies in an algorithm allows a superscalar processor to execute more instructions concurrently,
-thus maximizing its inherent parallelism and overall performance.
-The key limitation for ILP in the Merkle–Damgård construction is the inherent sequential dependency:
-each block's hash depends on the result of hashing the previous block.
+Minimizing dependencies in an algorithm allows a superscalar processor to execute more instructions concurrently, thus maximizing its inherent parallelism and overall performance.
+The key limitation for ILP in the Merkle–Damgård construction is the inherent sequential dependency: each block's hash depends on the result of hashing the previous block.
 
@@
 
-While compilers and CPUs employ various techniques to optimize ILP, their capabilities are often constrained by the inherent data dependencies
-in the code. It's for this reason that algorithmic design can be pivotal. By structuring algorithms to minimize dependency chains from the outset,
-we create opportunities for higher ILP that even the most advanced compiler optimizations and CPU features cannot achieve alone. Therefore,
-algorithmic design that is mindful of ILP can be a game-changer for performance optimization.
+While compilers and CPUs employ various techniques to optimize ILP, their capabilities are often constrained by the inherent data dependencies in the code.
+It's for this reason that algorithmic design can be pivotal.
+By structuring algorithms to minimize dependency chains from the outset, we create opportunities for higher ILP that even the most advanced compiler optimizations and CPU features cannot achieve alone.
+Therefore, algorithmic design that is mindful of ILP can be a game-changer for performance optimization.
 
 \subsubsection{Example}
-Let's take a FNV-like hashing function. The "naive" way to process an array of elements would look like the \texttt{baseline} method,
-as shown in Rust snippet (Figure~\ref{fig:ilp_rust_example}). As we can see, every loop iteration requires the value of \texttt{h},
-which has been computed the iteration before. Here we have a dependency chain, preventing the compiler from doing any optimization.
+Let's take a FNV-like hashing function.
+The "naive" way to process an array of elements would look like the \texttt{baseline} method, as shown in Rust snippet (Figure~\ref{fig:ilp_rust_example}).
+As we can see, every loop iteration requires the value of \texttt{h}, which has been computed the iteration before.
+Here we have a dependency chain, preventing the compiler from doing any optimization.
 
-To make ILP possible, for the function \texttt{temp} we unroll the loop and hash a few inputs altogether, independently from \texttt{h},
-and mix it once thereafter with \texttt{h}. We still have a dependency chain on \texttt{h}, but for less iterations.
+To make ILP possible, for the function \texttt{temp} we unroll the loop and hash a few inputs altogether, independently from \texttt{h}, and mix it once thereafter with \texttt{h}.
+We still have a dependency chain on \texttt{h}, but for less iterations.
 The temporary hashes are independent and thus eligible for ILP.
 
-Another track taken for the function \texttt{laned} is to unroll the loop and hash on separate lanes,
-and then mix the lanes together upon exiting the loop. Each lane has its own dependency chain, but on less iterations.
+Another track taken for the function \texttt{laned} is to unroll the loop and hash on separate lanes, and then mix the lanes together upon exiting the loop.
+Each lane has its own dependency chain, but on less iterations.
 
@@
 \subsubsection{Benchmark}
-Here are the timing on both an x86 and an ARM CPU. It also includes timing for the function \texttt{unrolled},
-to show that performance increase comes indeed from ILP and not the loop unrolling itself.
-We can see that \texttt{temp} and \texttt{laned} performed equally, leveraging ILP for a significant performance increase
-over the \texttt{baseline}.
+Here are the timing on both an x86 and an ARM CPU.
+It also includes timing for the function \texttt{unrolled}, to show that performance increase comes indeed from ILP and not the loop unrolling itself.
+We can see that \texttt{temp} and \texttt{laned} performed equally, leveraging ILP for a significant performance increase over the \texttt{baseline}.
 \\
@@
 \\
-While the \texttt{temp} and \texttt{laned} functions won't yield exactly the same hashes as the \texttt{baseline},
-they serve the same purpose, while being much faster.
-Both approaches have they pro and cons. As the \texttt{laned} explicitely declares \( n \) variables for our lanes,
-this approach is simpler in regards to compiler analysis and is thus more likely to benefit from ILP,
-regardless of the compiler or programming language used.
+While the \texttt{temp} and \texttt{laned} functions won't yield exactly the same hashes as the \texttt{baseline}, they serve the same purpose, while being much faster.
+Both approaches have they pro and cons.
+As the \texttt{laned} explicitely declares \( n \) variables for our lanes, this approach is simpler in regards to compiler analysis and is thus more likely to benefit from ILP, regardless of the compiler or programming language used.
 The following section will delve more in depth onto the definition of a \textbf{Laned Construction}.
@@
 
-The \textbf{Laned Construction} introduces \( k_b \) lanes, and processes the message by groups of \( k_b \) blocks,
-so that for a given group each of the \( k_b \) block and be processed on its own lane.
-This way, we have \( k_b \) independent dependency chains. The lane hashes can then be compressed altogether thereafter upon
-exiting the loop.
+The \textbf{Laned Construction} introduces \( k_b \) lanes, and processes the message by groups of \( k_b \) blocks, so that for a given group each of the \( k_b \) block and be processed on its own lane.
+This way, we have \( k_b \) independent dependency chains.
+The lane hashes can then be compressed altogether thereafter upon exiting the loop.
 
@@
 
+\clearpage
 \section{The GxHash Algorithm}
 
-The \textbf{GxHash} hashing algorithm employs an high ILP construction as described in section \ref{highilp}. In practice,
-this construction not only enables instruction level paralellism but also enables loop unrolling, disminishing the looping overhead,
-thus maximizing computational efficiency and overall performance.\\\\
-With that ILP unlocked, we still have to define f and g. In our quest for high-thoughput, it is essential for us to find computationally
-efficient definitions TODO
+The \textbf{GxHash} hashing algorithm is designed to maximize throughput by optimizing for Instruction-Level Parallelism (ILP) and making extensive use of Single Instruction, Multiple Data (SIMD) instructions.
+Notably, while these optimization avenues are orthogonal — focusing on parallelized and vectorized instructions respectively — they collectively harness the full potential of modern CPU architectures.\\\\
+This design philosophy introduces specific constraints for the compression and finalization functions:
+
+\begin{itemize}
+\item \textbf{Utilization of Hardware Intrinsics:} To achieve the SIMD-oriented goal, arithmetic operations are tailored to be compatible with both x86 and ARM Neon intrinsics.
+\item \textbf{Efficiency through Simplicity:} Minimizing the number of operations is crucial, as fewer operations typically translate to faster execution.
+\item \textbf{Hash Quality Assurance:} Despite these performance optimizations, the algorithm must ensure a minimum level of hash quality to maintain low collision probabilities.
+\end{itemize}
+
+In the next sections, we'll delve into the specific operations and transformations chosen for the compression and finalization functions of the \textbf{GxHash-0} (version 0) algorithm.
 
 \subsection{Pipe Width}
-As for the wide-pipe construction (as seen in section \ref{widepipe}) with \( s_b \) set to the executing CPU SIMD register size.
-TODO
+
+To optimize throughput, the pipe width \( s_b \) is set to match the native width of the CPU's SIMD registers.
+This alignment ensures that each SIMD instruction operates on the entire pipe width, maximizing data processed per instruction.
+Given that typical SIMD registers are at least 128 bits in width, the pipe width surpasses common 32-bit or 64-bit output hash sizes.
+Consequently, the GxHash design aligns with the characteristics of a wide-pipe construction, as discussed in section \ref{widepipe}.
+This makes GxHash more resistant to multicollision attacks.
 
@@
 
-TODO
+The role of the compression function is to transform a larger input (or message) into a smaller, fixed-size output.
+Due to this inherent reduction in size, the compression function cannot be bijective.
 
-\subsection{Hashing}
+To delve deeper into this, consider the definition of a bijective function.
+A function is bijective if and only if it is both injective (one-to-one) and surjective (onto).
+In simpler terms, for every unique input, there is a unique output, and every possible output has a corresponding input.
 
-TODO
+Given the nature of the compression function \( f: \{0,1\}^{s_b} \times \{0,1\}^{s_b} \to \{0,1\}^{s_b} \), where the domain is much larger than the codomain (\( s_b \times s_b > s_b \)), it becomes mathematically impossible for the function to be one-to-one.
+There will inevitably be multiple different inputs that map to the same output, as known as collisions.\\
 
-\subsection{Folding}
+With the inevitable non-bijectivity, the performance requirements and the limited set of available SIMD intrinsics, the selection for the compression has to empirical, thus implying specifying a version to account for these current choice that may be improved in future versions.\\
 
-TODO
+In practice, the \textbf{GxHash-0} uses a combination of SIMD 8-bit wrapping add and state-wide circular shift of one.
+The addition is a simple way to mix the state with the next message block bits, while providing and arithmetic carry which helps in regards to distribution (as opposed to a XOR for instance).
+Adding on a 8-bit basis also helps in regards to distribution, as opposed to adding on larger bit widths.
+This operation alone however comes with several weaknesses:
+\begin{itemize}
+\item Such a simple operation is inherently weak to different kind of attacks.
+This can however be partially addressed with a more robust bit mixing for the finalization function.
+In the context of non-cryptographic hashing, which is the scope of usage of our algorithm, we think it is an acceptable compromise.
+\item A major issue lies in the addition being associative (\(a \cdot b) \cdot c = a \cdot (b \cdot c \)).
+An associative compression function would make the hashing algorithm would be insensitive to the ordering of the input message blocks, which is something we want to avoid.
+To address this, we circularily shift the state bits by one.
+\end{itemize}
+
+While mathematically collisions are inevitable due to the inherent non-bijectivity, odds of collisions using the GxHash-0 compression remain statically low given the uniformity of distribution, altough those collisions are predictable due to the inherent simplicity of the function.
+
+\begin{figure}[ht]
+\begin{multicols}{2}
+\begin{lstlisting}[language=Rust, style=boxed]
+// For ARM 64-bit
+
+use core::arch::aarch64::*;
+
+pub fn compress(a: int8x16_t, b: int8x16_t)
+-> int8x16_t {
+    let sum: int8x16_t = vaddq_s8(a, b);
+    return vextq_s8(sum, sum, 1);
+}
+\end{lstlisting}
+\columnbreak
+\begin{lstlisting}[language=Rust, style=boxed]
+// For x86 64-bit
+
+use core::arch::x86_64::*;
+
+pub fn compress(a: __m256i, b: __m256i)
+-> __m256i {
+    let sum: state = _mm256_add_epi8(a, b);
+    return _mm256_alignr_epi8(sum, sum, 1);
+}
+\end{lstlisting}
+\end{multicols}
+\caption{GxHash-0 Compression in Rust}
+\label{fig:compression_rust_example}
+\end{figure}
+
+\subsection{Finalization}
+
+The finalization process in the GxHash-0 algorithm is crucial to ensure the transformation of its internal state into a fixed-size, uniformly distributed hash output.
+This process is delineated into two primary steps: mixing the bits and folding (reducing) to the desired hash size.
+
+\subsubsection{Mixing}
+
+This step is responsible for ensuring the even distribution of bits in the state, thereby reducing patterns or biases that might arise from the input data or the compression process.
+Given the inherent simplicity of the GxHash-0 compression, it is worth for the finalization to incorporate slightly more intricate bit mixing operations, especially given it runs only once per message hashed, as opposed to the compression that occurs once for each block.\\
+Leveraging SIMD capabilities can help in regards to performance and efficiency, which remains to us a primary consideration.
+Fortunately, both x86 and ARM architectures provide AES (Advanced Encryption Standard) intrinsics that serve as efficient tools for bit mixing.
+The use of an AES block cipher intrinsics ensures a robust diffusion of bits across the state at a cheap computational cost.\\
+On top of that, salt is added while forming the AES block cipher keys.
+This not only improves the distribution but also provide a way to use random salt values per-process, protecting from eventual precomputed or replay attacks attempts.
+
+\begin{figure}[ht]
+\begin{lstlisting}[language=Rust, style=boxed]
+// For x86 64-bit
+
+use core::arch::x86_64::*;
+
+pub fn mix(hash: state) -> state {
+    // Salt (Knuth primes recommended)
+    let salt = _mm256_set_epi64x(
+        -4860325414534694371,
+        8120763769363581797,
+        -4860325414534694371,
+        8120763769363581797);
+
+    let keys = _mm256_mul_epu32(salt, hash);
+    return _mm256_aesenc_epi128(hash, keys);
+}
+\end{lstlisting}
+\caption{GxHash-0 Mixing in Rust}
+\label{fig:mixing_rust_example}
+\end{figure}
+
+\subsubsection{Folding}
+
+Once the state's bits have been thoroughly mixed, the next step is to condense or "fold" this state into a smaller, fixed-size hash output, typically 32 or 64 bits.
+A straightforward and effective approach taken for GxHash-0 to achieve this reduction is by summing the constituent \( X \)-bit integer parts of the mixed state.
+This summation serves as a reduction function, ensuring that the output hash remains within the desired size bounds while still retaining the essence of the mixed state.
+
+While it would have been interesting to leverage SIMD once again, it turned out that, in practice, for both 128-bit and 256-bit state and for both x86 and ARM, summing the integer parts one by one is as performance if not more performant than using the various SIMD workarounds I tested.
 
 \subsection{Implementation Details}
-
-SIMD
-ILP
-Vectorized
-Parallelized
-Optimized
-Throughput
-Hashing
-
-HIGH ILP CONSTRUCTION
 
@@
 
+Language dependent. As close to the metal as possible, avoid loop overhead.
+
 \subsubsection{Loop Unrolling}
+
+Implicit with laned construction, but worth mentionning.
 
@@
 
+Load unaligned/aligned subtle difference in performance.
+Usually memory allocation are somehow aligned, but when using wide pipe (wide SIMD registers supported) it might not be the case that data is aligned.
+Overhead for aligning data.
+
 \section{Benchmarks}
-\subsection{Setup}
-\subsection{Evaluation Metrics}
-\subsection{Comparison with Existing Methods}
+
+\subsection{Quality}
+\subsection{Performance}
+
+t1ha\cite{rust-t1ha} xxhash\cite{twox-hash} HighwayHash\cite{highway-rs}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=1\textwidth]{throughput.png}
+\caption{Throughput Benchmark Results}
+\label{fig:benchmark-throughput}
+\end{figure}
 

### 2023-09-22 article/rust-listings.tex
Add description of the GxHash algorithm

--- 2023-09-12 article/rust-listings.tex
@@
 %
-, morekeywords={break, continue, else, for, if, in, loop, match, return, while}  % control flow keywords
-, morekeywords={as, const, let, move, mut, ref, static}  % in the context of variables
-, morekeywords={dyn, enum, fn, impl, Self, self, struct, trait, type, union, use, where}  % in the context of declarations
-, morekeywords={crate, extern, mod, pub, super}  % in the context of modularisation
-, morekeywords={unsafe}  % markers
-, morekeywords={abstract, alignof, become, box, do, final, macro, offsetof, override, priv, proc, pure, sizeof, typeof, unsized, virtual, yield}  % reserved identifiers
+, morekeywords=[1]{break, continue, else, for, if, in, loop, match, return, while}  % control flow keywords
+, morekeywords=[1]{as, const, let, move, mut, ref, static}  % in the context of variables
+, morekeywords=[1]{dyn, enum, fn, impl, Self, self, struct, trait, type, union, use, where}  % in the context of declarations
+, morekeywords=[1]{crate, extern, mod, pub, super}  % in the context of modularisation
+, morekeywords=[1]{unsafe}  % markers
+, morekeywords=[1]{abstract, alignof, become, box, do, final, macro, offsetof, override, priv, proc, pure, sizeof, typeof, unsized, virtual, yield}  % reserved identifiers
 %
@@
 \lstdefinestyle{colouredRust}%
-{ basicstyle=\ttfamily%
+{ basicstyle=\fontsize{9}{9}\ttfamily\selectfont,%
 , identifierstyle=%
-, commentstyle=\color[gray]{0.4}%
+, commentstyle=\color[rgb]{0, 0.7, 0}%
 , stringstyle=\color[rgb]{0, 0, 0.5}%
 , keywordstyle=\bfseries% reserved keywords
+, keywordstyle=[1]\color[rgb]{0, 0.2, 0.9}% traits
 , keywordstyle=[2]\color[rgb]{0.75, 0, 0}% traits

### 2023-09-22 src/gxhash.rs

@@ -86,7 +86,15 @@ mod platform_defs {
     #[inline]
     pub unsafe fn compress(a: state, b: state) -> state {
         let sum: state = _mm256_add_epi8(a, b);
-        _mm256_alignr_epi8(sum, sum, 1) 
+        //let sum: state = _mm256_xor_epi32(a, b);
+        _mm256_alignr_epi8(sum, sum, 1)
+
+        // Cantor Pairing Function
+        //return (0.5 * (x + y) * (x + y + 1)) + y;
+        // let a_plus_b = _mm256_add_epi32(a, b);
+        // let a_plus_b_plus_1 = _mm256_add_epi32(a_plus_b, _mm256_set1_epi32(1));
+        // let m1 = _mm256_mul_epi32(a_plus_b, a_plus_b_plus_1);
+        // _mm256_add_epi32(m1, b)
     }
 
     #[inline]
@@ -94,7 +102,6 @@ mod platform_defs {
         let salt = _mm256_set_epi64x(-4860325414534694371, 8120763769363581797, -4860325414534694371, 8120763769363581797);
         let keys = _mm256_mul_epu32(salt, hash);
         _mm256_aesenc_epi128(hash, keys)
-
     }
 
     #[inline]

### 2023-09-23 article/article.tex
Add writing on implementation details

@@
 \documentclass[10pt]{article} 
-\usepackage[margin=0.8in]{geometry}
+\usepackage[margin=0.73in]{geometry}
 \usepackage{amsmath}
@@
 Traditional hashing methods, while effective, often fail to fully utilize the computational capabilities of modern processors.
-This paper introduces the GxHash hashing algorithm, a novel approach that harnesses the power of high instruction-level parallelism (ILP) and Single
-Instruction, Multiple Data (SIMD) capabilities of contemporary CPUs to achieve high-throughput non-cryptographic hashing. Through a comprehensive
-analysis, including benchmarks and comparisons with existing methods, we demonstrate that GxHash significantly outperforms conventional algorithms
-in terms of speed and computational efficiency without compromising on security. The paper also explores the implications, limitations, and avenues
-for future research in this burgeoning field.
+This paper introduces the GxHash hashing algorithm, a novel approach that harnesses the power of high instruction-level parallelism (ILP) and Single Instruction, Multiple Data (SIMD) capabilities of contemporary CPUs to achieve high-throughput non-cryptographic hashing.
+Through a comprehensive analysis, including benchmarks and comparisons with existing methods, we demonstrate that GxHash significantly outperforms conventional algorithms in terms of speed and computational efficiency without compromising on security.
+The paper also explores the implications, limitations, and avenues for future research in this burgeoning field.
 
@@
 While performance remains our primary focus, the algorithm we examine in this paper incorporates the Wide-Pipe idea.
-By doing so, it offers a dual advantage: performance efficacy, which is central to this study, along with a good cryptographic resilience, which is an indeniable advantage even in the realm of non-cryptographic hash functions.
+By doing so, it offers a dual advantage: performance efficacy, which is central to this study, along with good cryptographic resilience, which is an undeniable advantage even in the realm of non-cryptographic hash functions.
 
@@
 While the classical Merkle–Damgård construction provides a reliable framework for cryptographic hash functions, there are a wide number of variants\cite{merkle_damgard_alternatives_review}.
-In this section, we discuss around some of the most popular variants around opportunities for performance enhancement.
+In this section, we discuss some of the most popular variants around opportunities for performance enhancement.
 
@@
 Importantly, each absorption step is inherently sequential, as it relies on the state resulting from the cryptographic permutation of the previous step.
-Consequently, the algorithm does cannot benefit from instruction-level parallelism during the absorption phase.
+Consequently, the algorithm cannot benefit from instruction-level parallelism during the absorption phase.
 The squeezing phase, which follows the absorption of all input blocks, generates the output hash from the internal state.
@@
 
-In light of these practical challenges, tree-based constructions might not be the best fit given our high performance goals and the architecture of today's general purpose computers.
+In light of these practical challenges, tree-based constructions might not be the best fit given our high performance goals and the architecture of today's general-purpose computers.
 
@@
 To make ILP possible, for the function \texttt{temp} we unroll the loop and hash a few inputs altogether, independently from \texttt{h}, and mix it once thereafter with \texttt{h}.
-We still have a dependency chain on \texttt{h}, but for less iterations.
+We still have a dependency chain on \texttt{h}, but for fewer iterations.
 The temporary hashes are independent and thus eligible for ILP.
@@
 Another track taken for the function \texttt{laned} is to unroll the loop and hash on separate lanes, and then mix the lanes together upon exiting the loop.
-Each lane has its own dependency chain, but on less iterations.
+Each lane has its own dependency chain but also on fewer iterations.
 
@@
 While the \texttt{temp} and \texttt{laned} functions won't yield exactly the same hashes as the \texttt{baseline}, they serve the same purpose, while being much faster.
-Both approaches have they pro and cons.
-As the \texttt{laned} explicitely declares \( n \) variables for our lanes, this approach is simpler in regards to compiler analysis and is thus more likely to benefit from ILP, regardless of the compiler or programming language used.
-The following section will delve more in depth onto the definition of a \textbf{Laned Construction}.
+Both approaches have their pros and cons.
+As the \texttt{laned} explicitly declares \( n \) variables for our lanes, this approach is simpler in regards to compiler analysis and is thus more likely to benefit from ILP, regardless of the compiler or programming language used.
+The following section will delve more in depth into the definition of a \textbf{Laned Construction}.
 
@@
 Given the nature of the compression function \( f: \{0,1\}^{s_b} \times \{0,1\}^{s_b} \to \{0,1\}^{s_b} \), where the domain is much larger than the codomain (\( s_b \times s_b > s_b \)), it becomes mathematically impossible for the function to be one-to-one.
-There will inevitably be multiple different inputs that map to the same output, as known as collisions.\\
+There will inevitably be multiple different inputs that map to the same output, known as collisions.\\
 
-With the inevitable non-bijectivity, the performance requirements and the limited set of available SIMD intrinsics, the selection for the compression has to empirical, thus implying specifying a version to account for these current choice that may be improved in future versions.\\
+With the inevitable non-bijectivity, the performance requirements and the limited set of available SIMD intrinsics, the selection for the compression has to be empirical, thus implying specifying a version to account for these current choices that may be improved in future versions.\\
 
 In practice, the \textbf{GxHash-0} uses a combination of SIMD 8-bit wrapping add and state-wide circular shift of one.
-The addition is a simple way to mix the state with the next message block bits, while providing and arithmetic carry which helps in regards to distribution (as opposed to a XOR for instance).
+The addition is a simple way to mix the state with the next message block bits, while providing an arithmetic carry which helps in regard to distribution (as opposed to a XOR for instance).
 Adding on a 8-bit basis also helps in regards to distribution, as opposed to adding on larger bit widths.
@@
 \item A major issue lies in the addition being associative (\(a \cdot b) \cdot c = a \cdot (b \cdot c \)).
-An associative compression function would make the hashing algorithm would be insensitive to the ordering of the input message blocks, which is something we want to avoid.
-To address this, we circularily shift the state bits by one.
+An associative compression function would make the hashing algorithm insensitive to the ordering of the input message blocks, which is something we want to avoid.
+To address this, we circularly shift the state bits by one.
 \end{itemize}
 
-While mathematically collisions are inevitable due to the inherent non-bijectivity, odds of collisions using the GxHash-0 compression remain statically low given the uniformity of distribution, altough those collisions are predictable due to the inherent simplicity of the function.
+While mathematically collisions are inevitable due to the inherent non-bijectivity, odds of collisions using the GxHash-0 compression remain statically low given the uniformity of distribution, although those collisions are predictable due to the inherent simplicity of the function.
 
@@
 Given the inherent simplicity of the GxHash-0 compression, it is worth for the finalization to incorporate slightly more intricate bit mixing operations, especially given it runs only once per message hashed, as opposed to the compression that occurs once for each block.\\
-Leveraging SIMD capabilities can help in regards to performance and efficiency, which remains to us a primary consideration.
+Leveraging SIMD capabilities can help in regard to performance and efficiency, which remains for us a primary consideration.
 Fortunately, both x86 and ARM architectures provide AES (Advanced Encryption Standard) intrinsics that serve as efficient tools for bit mixing.
@@
 On top of that, salt is added while forming the AES block cipher keys.
-This not only improves the distribution but also provide a way to use random salt values per-process, protecting from eventual precomputed or replay attacks attempts.
+This not only improves the distribution but also provides a way to use random salt values per-process, protecting from eventual precomputed or replay attack attempts.
 
@@
 \begin{lstlisting}[language=Rust, style=boxed]
-// For x86 64-bit
-
 use core::arch::x86_64::*;
@@
 
-While it would have been interesting to leverage SIMD once again, it turned out that, in practice, for both 128-bit and 256-bit state and for both x86 and ARM, summing the integer parts one by one is as performance if not more performant than using the various SIMD workarounds I tested.
+While it would have been interesting to leverage SIMD once again, it turned out that, in practice, for both 128-bit and 256-bit state and for both x86 and ARM, summing the integer parts one by one is as performant if not more performant than using the various SIMD workarounds I tested.
 
@@
 
-\subsubsection{Padding}
+\subsubsection{CPU Alignement}
 
-\textbf{Merkle–Damgård} and derivatives can actually handle message of an arbitrary size \( s_m \) by padding the message upfront with the padding
-function \( p: \{0,1\}^{s_m} \to \{0,1\}^{n_b \times s_b} \) where \( n_b = \lceil s_m/s_b \rceil \).
+Data alignment in memory, commonly referred to as CPU alignment, directly impacts the efficiency of data access and processing.
+The CPU is optimized to access data from addresses that align with its natural word size.
+When data is properly aligned, the CPU can retrieve and process it in fewer cycles, resulting in increased computational efficiency.
 
-In practice, implementing \( p \) in computer code implies memory copies. Instead, TODO
+In practice, a program usually allocates memory with some degree of alignment, and so data is generally aligned.
+However, a given input message to our hash function is still not guaranteed to be aligned.
+To handle this case, we can either read our data with an offset to account for the misalignment (at the cost of a much-increased complexity) or use specific SIMD intrinsics designed to handle potentially unaligned data.
+
+Benchmarks conducted show a less than 20\% performance degradation on both our x86 and ARM hardware when using the second solution. This is the chosen solution for GxHash-0.
 
@@
 
-Language dependent. As close to the metal as possible, avoid loop overhead.
+While the looping semantics will vary from one language to another, any overhead from looping over the input message blocks is likely to directly affect the overall throughput of the algorithm, given how optimized the rest of the algorithm is meant to be.
+In some cases, compilers might do a great job at generating loop instructions with minimal overhead, but it isn't the case in the language where GxHash-0 was ported, where looping using pointer arithmetics was needed.
 
-\subsubsection{Loop Unrolling}
+Unrolling the loop is a complementary optimization that diminishes greatly any loop overhead.
+In the case of GxHash, the laned construction implies some kind of unrolling, which is sufficient for achieving the high throughput numbers we see in our benchmarks.
 
-Implicit with laned construction, but worth mentionning.
+\subsubsection{Padding}
 
-\subsubsection{CPU Alignement}
+\textbf{Merkle–Damgård} and derivatives can handle message of an arbitrary size \( s_m \) by padding the message upfront with the padding function \( p: \{0,1\}^{s_m} \to \{0,1\}^{n_b \times s_b} \) where \( n_b = \lceil s_m/s_b \rceil \).
+In the case where the last block is not whole, the padding fills it with zero-bytes until the size \( s_b \) is reached.
+The last block can then be processed like any other block by the compression function.
 
-Load unaligned/aligned subtle difference in performance.
-Usually memory allocation are somehow aligned, but when using wide pipe (wide SIMD registers supported) it might not be the case that data is aligned.
-Overhead for aligning data.
+In practice, a naive implementation for \( p \) for GxHash in computer code implies copying the remaining bytes into a zero-initialized buffer of size \( s_b \), which can then be loaded onto an SIMD registry and then handed to the compression.
+In our performance-critical context, these allocations and copies have a substantial overhead.
+
+\paragraph{Read beyond and mask.}
+To avoid this overhead, one possible trick consists of reading \( s_b \) bytes starting from the last block address, even if it implies reading beyond the memory storing the input message.
+The read bytes can then be masked with the help of a sliding mask, transforming the trailing bytes that don't belong to our message into zeros, in a single SIMD operation.
+Compared to the naive method, this solution is up to ten times faster on our test machine (Ryzen 5, x86 64-bit, AVX2).
+
+\begin{figure}[ht]
+\begin{lstlisting}[language=Rust, style=boxed]
+use core::arch::x86_64::*;
+
+unsafe fn read_padded(p: *const __m256i, len: isize) -> __m256i {
+    // The mask array is twice as long as the SIMD registry size (32*2 here), so that
+    // each 32-byte slice accounts for a different number of trailing bytes to mask out
+    const MASK: [u8; 64] = [
+        0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF,
+        0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF,
+        0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00,
+        0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00 ];
+    // Loading the mask slice
+    let mask = _mm256_loadu_epi8((MASK.as_ptr() as *const i8).offset(32 - len));
+    // Read beyond and mask
+    return _mm256_and_si256(_mm256_loadu_si256(p), mask);
+}
+\end{lstlisting}
+\caption{GxHash-0 Padding in Rust}
+\label{fig:read_beyond_example}
+\end{figure}
+
+\paragraph{Safety considerations.}
+Reading beyond a given pointer can lead to accessing memory that is either not mapped to the program's address space or is protected.
+When the program tries to read such memory, the operating system detects the violation and typically terminates the program, resulting in a crash.
+This mechanism protects processes from interfering with each other and from accessing system-critical memory regions.
+While this is very unlikely to occur in most scenarios, the fact that it can theoretically occur is a problem.
+
+In modern computers, memory is divided into fixed-size chunks called pages.
+Once a page is given to a program, it can freely access any part of that page without causing system-level errors like segmentation faults.
+We can take this to our advantage by checking if our unsafe operation is entirely contained in a single block.
+If so, it means we can use the optimized method safely.
+Otherwise, we can fallback to the naive method.
+
+In practice, this is quite trivial to implement since memory is divided into pages in such a way that addresses within a single page will share the same higher bits and only vary in the lower bits that represent offsets within that page.
+The snippet in figure~\ref{fig:check_page_example} does this considering a minimal page size of 4096.
+Statistically speaking, the odds of having 32 bytes on the same page are above 99\%.
+This safety check being very cheap to compute, we keep most of the performance advantages of our method while addressing the safety issue.
+
+\begin{figure}[ht]
+\begin{lstlisting}[language=Rust, style=boxed]
+unsafe fn is_same_page(ptr: *const __m256i) -> bool {
+    // Usual minimal page size on modern computers
+    const PAGE_SIZE = 4096;
+    // Get the actual pointer address integer value
+    let address = ptr as usize;
+    // Mask to keep only the last 12 bits (2^12 = 4096)
+    let offset_within_page = address & 0xFFF;
+    // Check if the 32nd byte from the current offset exceeds the page boundary
+    offset_within_page <= (PAGE_SIZE - 31)
+}
+\end{lstlisting}
+\caption{Read-Beyond Safety Check in Rust}
+\label{fig:check_page_example}
+\end{figure}
 

### 2023-09-23 src/gxhash.rs
Add writing on implementation details

@@ -79,22 +79,37 @@ mod platform_defs {
             0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF,
             0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00 ];
 
-        let mask = _mm256_loadu_epi8((MASK.as_ptr() as *const i8).offset(32 - len));
-        _mm256_and_si256(_mm256_loadu_si256(p), mask)
+        // Safety check
+        if (check_same_page(p)) {
+            let mask = _mm256_loadu_epi8((MASK.as_ptr() as *const i8).offset(32 - len));
+            return _mm256_and_si256(_mm256_loadu_si256(p), mask);
+        }
+        return get_partial_safe(p as *const u8, len as usize);
+    }
+
+    #[inline]
+    unsafe fn check_same_page(ptr: *const state) -> bool {
+        let address = ptr as usize;
+        // Mask to keep only the last 12 bits (3 bytes)
+        let offset_within_page = address & 0xFFF;
+        // Check if the 32nd byte from the current offset exceeds the page boundary
+        offset_within_page <= (4096 - 31)
+    }
+
+    #[inline]
+    unsafe fn get_partial_safe(data: *const u8, len: usize) -> state {
+        // Temporary buffer filled with zeros
+        let mut buffer: [u8; 32] = [0; 32];
+        // Copy data into the buffer
+        std::ptr::copy(data, buffer.as_mut_ptr(), len);
+        // Load the buffer into a __m256i vector
+        _mm256_loadu_si256(buffer.as_ptr() as *const state)
     }
 
     #[inline]
     pub unsafe fn compress(a: state, b: state) -> state {
         let sum: state = _mm256_add_epi8(a, b);
[…]

### 2023-09-28 src/main.rs
Small loop in main for flamegraph analysis

@@ -1,3 +1,5 @@
+use std::hint::black_box;
+
 use rand::Rng;
 
 use gxhash::gxhash;
@@ -8,5 +10,7 @@ fn main() {
     let mut random_bytes = [0u8; 16384]; // Create an array of 16 bytes, initialized to 0
     rng.fill(&mut random_bytes[..]); // Fill the array with random bytes
 
-    println!("{}", gxhash(&random_bytes));
+    for i in 0..100000 {
+        black_box(gxhash(&random_bytes));
+    }
 }

### 2023-09-28 src/gxhash.rs
Complete ARM neon AES

@@ -6,6 +6,15 @@ mod platform_defs {
 
     pub type state = int8x16_t;
 
+    #[repr(C)]
+    union ReinterpretUnion {
+        int64: int64x2_t,
+        int32: int32x4_t,
+        uint32: uint32x4_t,
+        int8: int8x16_t,
+        uint8: uint8x16_t,
+    }
+
     #[inline]
     pub unsafe fn create_empty() -> state {
         vdupq_n_s8(0)
@@ -27,7 +36,7 @@ mod platform_defs {
             0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF,
             0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00 ];
 
-        let mask = vld1q_s8((MASK.as_ptr() as *const i8).offset(size_of::<state>() - len));
+        let mask = vld1q_s8((MASK.as_ptr() as *const i8).offset(size_of::<state>() as isize - len));
         vandq_s8(load_unaligned(p), mask)
     }
 
@@ -39,13 +48,20 @@ mod platform_defs {
 
     #[inline]
     pub unsafe fn mix(hash: state) -> state {
-        hash
+        let salt = vcombine_s64(vcreate_s64(4860325414534694371), vcreate_s64(8120763769363581797));
+        let keys = vmulq_s32(
+            ReinterpretUnion { int64: salt }.int32,
+            ReinterpretUnion { int8: hash }.int32);
+        let a = vaeseq_u8(ReinterpretUnion { int8: hash }.uint8, vdupq_n_u8(0));
+        let b = vaesmcq_u8(a);
+        let c = veorq_u8(b, ReinterpretUnion{ int32: keys }.uint8);
+        ReinterpretUnion{ uint8: c }.int8
     }
 
     #[inline]
     pub unsafe fn fold(hash: state) -> u32 {
         // Bit-cast the int8x16_t to uint32x4_t
-        let vec_u32: uint32x4_t = mem::transmute(hash);
+        let vec_u32: uint32x4_t = ReinterpretUnion { int8: hash }.uint32;
         // Get the first u32 value from the vector
         vgetq_lane_u32(vec_u32, 3)
     }
@@ -248,7 +264,7 @@ mod tests {
[…]

### 2023-09-28 src/main.rs
No blackbox for flamegraph

@@ -1,5 +1,3 @@
-use std::hint::black_box;
-
 use rand::Rng;
 
 use gxhash::gxhash;
@@ -10,7 +8,11 @@ fn main() {
     let mut random_bytes = [0u8; 16384]; // Create an array of 16 bytes, initialized to 0
     rng.fill(&mut random_bytes[..]); // Fill the array with random bytes
 
-    for i in 0..100000 {
-        black_box(gxhash(&random_bytes));
+    let mut sum: u32 = 0;
+
+    for _ in 0..100_000_000 {
+        sum = sum.wrapping_add(gxhash(&random_bytes));
     }
+
+    println!("{}", sum);
 }

### 2023-09-29 article/article.tex
Update readme

@@
 \subsection{Quality}
+
+\subsubsection{Benchmark Quality Criteria}
+The primary quality criteria for non-cryptographic hash functions include:
+
+\begin{itemize}
+    \item \textbf{Uniform Distribution:} A high-quality hash function distributes its output values as uniformly as possible across the output space.
+This ensures that, when used in applications like hash tables, the data is spread evenly, reducing clustering and the frequency of collisions.
+    \item \textbf{Minimal Collisions:} While no hash function can be entirely collision-free due to the pigeonhole principle, a good non-cryptographic hash should minimize collisions for typical input sets, ensuring that different inputs usually produce distinct outputs.
+    \item \textbf{Avalanche Effect:} A subtle change in the input should result in a considerably different output, ensuring sensitivity to input variations.
+This also contributes to lessen the risk of clustered hashes in applications like hash tables.
+    \item \textbf{Performance:} The performance of a non cryptographic hash function is usually reflected by the performance of the application using it.
+For instance, a fast non-cryptographic hash function generally implies a fast hash table.
+This specific criteria will be tackled in the next section which is dedicated to it.
+\end{itemize}
+
+While we can compute quality metrics, the result will greatly vary depending on the actual inputs used for our hash function. Pragmatically, we choose a few patterns for our input data:
+\begin{itemize}
+    \item Randomly generated inputs to observe how the hash function behaves with truly unpredictable data
+    \item Sequential inputs to observe how the function handles closely related values. Typically, close values would highlight weaknesses in distribution.
+    \item English words inputs to observe how the function behaves in a "real world scenario"
+\end{itemize}
+
+\subsubsection{Quality Criteria Results}
+For reference, we include a few well-known algorithms on top of GxHash-0.
+
 \subsection{Performance}

### 2023-09-29 src/gxhash.rs

@@ -157,7 +157,8 @@ pub use platform_defs::*;
 #[cfg(test)]
 pub static mut COUNTERS : Vec<usize> = vec![];
 
-#[inline]
+//#[inline]
+#[inline(never)]
 pub fn gxhash(input: &[u8]) -> u32 {
     unsafe {
         const VECTOR_SIZE: isize = std::mem::size_of::<state>() as isize;
@@ -265,8 +266,7 @@ mod tests {
 
             // cargo test -- --nocapture
             println!("{:?}", &COUNTERS);
-            assert!(COUNTERS.as_slice() == expected.as_slice());
-            
+            assert_eq!(COUNTERS.as_slice(), expected.as_slice());
         }
     }
 

### 2023-09-29 src/gxhash.rs
Xor folding and constant AES salt

@@ -97,7 +97,7 @@ mod platform_defs {
             0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00 ];
 
         // Safety check
-        if check_same_page(p) {
+        if check_same_page(p) { // false {//
             let mask = _mm256_loadu_epi8((MASK.as_ptr() as *const i8).offset(32 - len));
             _mm256_and_si256(_mm256_loadu_si256(p), mask)
         } else {
@@ -133,20 +133,20 @@ mod platform_defs {
     #[inline]
     pub unsafe fn mix(hash: state) -> state {
         let salt = _mm256_set_epi64x(-4860325414534694371, 8120763769363581797, -4860325414534694371, 8120763769363581797);
-        let keys = _mm256_mul_epu32(salt, hash);
-        _mm256_aesenc_epi128(hash, keys)
+        //let keys = _mm256_mul_epu32(salt, hash);
+        _mm256_aesenc_epi128(hash, salt)
     }
 
     #[inline]
     pub unsafe fn fold(hash: state) -> u32 {
         let p = &hash as *const state as *const u32;
-        (*p).wrapping_add(*p.offset(1))
-            .wrapping_add(*p.offset(2))
-            .wrapping_add(*p.offset(3))
-            .wrapping_add(*p.offset(4))
-            .wrapping_add(*p.offset(5))
-            .wrapping_add(*p.offset(6))
-            .wrapping_add(*p.offset(7))
+        *p  ^ *p.offset(1)
+            ^ *p.offset(2)
+            ^ *p.offset(3)
+            ^ *p.offset(4)
+            ^ *p.offset(5)
+            ^ *p.offset(6)
+            ^ *p.offset(7)
     }
 }
 
@@ -157,8 +157,8 @@ pub use platform_defs::*;
 #[cfg(test)]
 pub static mut COUNTERS : Vec<usize> = vec![];
 
-//#[inline]
-#[inline(never)]
+#[inline]
+//#[inline(never)]
 pub fn gxhash(input: &[u8]) -> u32 {
     unsafe {
[…]

### 2023-10-01 article/article.tex
Update finalization

@@
 The finalization process in the GxHash-0 algorithm is crucial to ensure the transformation of its internal state into a fixed-size, uniformly distributed hash output.
-This process is delineated into two primary steps: mixing the bits and folding (reducing) to the desired hash size.
+This process is delineated into two primary steps: mixing the bits and reducing to the desired hash size.
 
-\subsubsection{Mixing}
-
-This step is responsible for ensuring the even distribution of bits in the state, thereby reducing patterns or biases that might arise from the input data or the compression process.
+This mixing step is responsible for ensuring the even distribution of bits in the state, thereby reducing patterns or biases that might arise from the input data or the compression process.
 Given the inherent simplicity of the GxHash-0 compression, it is worth for the finalization to incorporate slightly more intricate bit mixing operations, especially given it runs only once per message hashed, as opposed to the compression that occurs once for each block.\\
@@
 Fortunately, both x86 and ARM architectures provide AES (Advanced Encryption Standard) intrinsics that serve as efficient tools for bit mixing.
-The use of an AES block cipher intrinsics ensures a robust diffusion of bits across the state at a cheap computational cost.\\
-On top of that, salt is added while forming the AES block cipher keys.
-This not only improves the distribution but also provides a way to use random salt values per-process, protecting from eventual precomputed or replay attack attempts.
+The use of three AES block cipher rounds ensures a robust diffusion of bits across the state at a cheap computational cost.\\
+The AES keys can be set changed, providing a way to have unique hashes per-application and even per-process, protecting from eventual precomputed or replay attack attempts.
 
-\begin{figure}[ht]
-\begin{lstlisting}[language=Rust, style=boxed]
-use core::arch::x86_64::*;
-
-pub fn mix(hash: state) -> state {
-    // Salt (Knuth primes recommended)
-    let salt = _mm256_set_epi64x(
-        -4860325414534694371,
-        8120763769363581797,
-        -4860325414534694371,
-        8120763769363581797);
-
-    let keys = _mm256_mul_epu32(salt, hash);
-    return _mm256_aesenc_epi128(hash, keys);
-}
-\end{lstlisting}
-\caption{GxHash-0 Mixing in Rust}
-\label{fig:mixing_rust_example}
-\end{figure}
-
-\subsubsection{Folding}
-
-Once the state's bits have been thoroughly mixed, the next step is to condense or "fold" this state into a smaller, fixed-size hash output, typically 32 or 64 bits.
-A straightforward and effective approach taken for GxHash-0 to achieve this reduction is by summing the constituent \( X \)-bit integer parts of the mixed state.
-This summation serves as a reduction function, ensuring that the output hash remains within the desired size bounds while still retaining the essence of the mixed state.
-
-While it would have been interesting to leverage SIMD once again, it turned out that, in practice, for both 128-bit and 256-bit state and for both x86 and ARM, summing the integer parts one by one is as performant if not more performant than using the various SIMD workarounds I tested.
+Once the state's bits have been thoroughly mixed, the next step is to reduce this state into a smaller, fixed-size hash output, typically 32 or 64 bits.
+There are several approaches to this, one being combiniting the \( X \)-bit integer parts of the mixed state together (by xoring them together for instance).
+GxHash0 takes a simpler path by reinterpreting our state into a smaller \( X \)-bit value, assuming an uniform distribution at the mixing stage thanks to the 3 rounds of AES.
+This allow the GxHash0 algorithm to generate hashes of any size up to \( s_b \) bits with virtually no additional computational cost.
 
@@
 
-While we can compute quality metrics, the result will greatly vary depending on the actual inputs used for our hash function. Pragmatically, we choose a few patterns for our input data:
-\begin{itemize}
-    \item Randomly generated inputs to observe how the hash function behaves with truly unpredictable data
-    \item Sequential inputs to observe how the function handles closely related values. Typically, close values would highlight weaknesses in distribution.
-    \item English words inputs to observe how the function behaves in a "real world scenario"
-\end{itemize}
+\subsubsection{Quality Criteria Results}
 
-\subsubsection{Quality Criteria Results}
-For reference, we include a few well-known algorithms on top of GxHash-0.
+While we can compute quality metrics, the result will greatly vary depending on the actual inputs used for our hash function.
+Let's see how the GxHash0 algorithm qualifies against a few well known non-cryptographic algorithm in a few scenarios.
+
+\paragraph{Random Blobs}
+
+Randomly generated inputs to observe how the hash function behaves with truly unpredictable data
+
+\paragraph{Sequential Number}
+
+Sequential inputs to observe how the function handles closely related values. Typically, close values would highlight weaknesses in distribution.
+
+\paragraph{English Words}
+English words inputs to observe how the function behaves in a "real world scenario"
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=1\textwidth]{quality-sequential.png}
+\caption{Merkle–Damgård Construction Overview}
+\label{fig:linear-construction}
+\end{figure}
 

### 2023-10-01 src/gxhash.rs
Update finalization

@@ -47,7 +47,7 @@ mod platform_defs {
     }
 
     #[inline]
-    pub unsafe fn mix(hash: state) -> state {
+    pub unsafe fn finalize(hash: state) -> u32 {
         let salt = vcombine_s64(vcreate_s64(4860325414534694371), vcreate_s64(8120763769363581797));
         let keys = vmulq_s32(
             ReinterpretUnion { int64: salt }.int32,
@@ -55,15 +55,8 @@ mod platform_defs {
         let a = vaeseq_u8(ReinterpretUnion { int8: hash }.uint8, vdupq_n_u8(0));
         let b = vaesmcq_u8(a);
         let c = veorq_u8(b, ReinterpretUnion{ int32: keys }.uint8);
-        ReinterpretUnion{ uint8: c }.int8
-    }
-
-    #[inline]
-    pub unsafe fn fold(hash: state) -> u32 {
-        // Bit-cast the int8x16_t to uint32x4_t
-        let vec_u32: uint32x4_t = ReinterpretUnion { int8: hash }.uint32;
-        // Get the first u32 value from the vector
-        vgetq_lane_u32(vec_u32, 3)
+        let p = &ReinterpretUnion{ uint8: c }.int8 as *const state as *const u32;
+        *p
     }
 }
 
@@ -93,8 +86,10 @@ mod platform_defs {
     #[inline]
     pub unsafe fn get_partial(p: *const state, len: isize) -> state {
         const MASK: [u8; size_of::<state>() * 2] = [
-            0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF,
-            0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00 ];
[…]

### 2023-10-07 article/article.tex
More writing on quality

@@
 \usepackage{graphicx}
+\usepackage{float}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
@@
 
-\begin{figure}[ht]
+\begin{figure}[H]
 \begin{multicols}{2}
@@
 We can see that \texttt{temp} and \texttt{laned} performed equally, leveraging ILP for a significant performance increase over the \texttt{baseline}.
-\\
-\begin{figure}[ht]
+
+\begin{figure}[H]
 \centering
@@
 \end{figure}
-\\
+
 While the \texttt{temp} and \texttt{laned} functions won't yield exactly the same hashes as the \texttt{baseline}, they serve the same purpose, while being much faster.
@@
 
-\paragraph{Read beyond and mask.}
+\paragraph{Read Beyond and Mask}\leavevmode\\
 To avoid this overhead, one possible trick consists of reading \( s_b \) bytes starting from the last block address, even if it implies reading beyond the memory storing the input message.
@@
 
-\begin{figure}[ht]
+\begin{figure}[H]
 \begin{lstlisting}[language=Rust, style=boxed]
@@
 
-\paragraph{Safety considerations.}
-Reading beyond a given pointer can lead to accessing memory that is either not mapped to the program's address space or is protected.
-When the program tries to read such memory, the operating system detects the violation and typically terminates the program, resulting in a crash.
-This mechanism protects processes from interfering with each other and from accessing system-critical memory regions.
-While this is very unlikely to occur in most scenarios, the fact that it can theoretically occur is a problem.
+\paragraph{Safety Considerations}\leavevmode\\
+Reading beyond a specified pointer might access memory not mapped to the program's address space or that's protected.
+If the program tries to read this memory, the OS detects the violation, typically causing a crash.
+This mechanism ensures processes don't interfere with each other or access critical memory areas.
+Although rare, the potential for this issue exists.
 
-In modern computers, memory is divided into fixed-size chunks called pages.
-Once a page is given to a program, it can freely access any part of that page without causing system-level errors like segmentation faults.
-We can take this to our advantage by checking if our unsafe operation is entirely contained in a single block.
-If so, it means we can use the optimized method safely.
-Otherwise, we can fallback to the naive method.
+In modern computers, memory is divided into chunks called pages.
+A program can access any part of its assigned page without system-level errors like segmentation faults.
+We can check if an unsafe operation is within a single page.
+If it is, we can use the optimized method; if not, we fallback to the naive method.
 
-In practice, this is quite trivial to implement since memory is divided into pages in such a way that addresses within a single page will share the same higher bits and only vary in the lower bits that represent offsets within that page.
-The snippet in figure~\ref{fig:check_page_example} does this considering a minimal page size of 4096.
-Statistically speaking, the odds of having 32 bytes on the same page are above 99\%.
-This safety check being very cheap to compute, we keep most of the performance advantages of our method while addressing the safety issue.
+Memory pages are designed so addresses within them share higher bits and vary only in lower bits, representing offsets.
+The code in figure~\ref{fig:check_page_example} uses this principle, considering a page size of 4096.
+The likelihood of having 32 bytes on the same page exceeds 99\%.
+This safety check is cost-effective, retaining most performance benefits while ensuring safety.
 
-\begin{figure}[ht]
+\begin{figure}[H]
 \begin{lstlisting}[language=Rust, style=boxed]
@@
 
+\clearpage
 \section{Benchmarks}
@@
 
-\subsubsection{Quality Criteria Results}
+\subsubsection{Quality Results}
 
@@
 
-\paragraph{Random Blobs}
+Todo: Actual funcs used ? Like what is bits distribution vs distribution ?
 
+\clearpage
+\paragraph{Random Blobs}\leavevmode\\
 Randomly generated inputs to observe how the hash function behaves with truly unpredictable data
 
-\paragraph{Sequential Number}
+\begin{table}[H]
+\centering
+\begin{tabular}{|l|r|r|r|r|}
+\hline
+\textbf{Function for Random dataset} & \textbf{Collisions} & \textbf{Bits Distribution} & \textbf{Distribution} & \textbf{Avalanche} \\
+\hline
+Int32 GxHash0(4)            & 0,0241\% & 0,001094  & 0,000002 & 0,00412 \\
+Int32 GxHash0(64)           & 0,0103\% & 0,001081  & 0,000002 & 0,00296 \\
+Int32 GxHash0(1000)         & 0,012\%  & 0,001148  & 0,000002 & 0,00336 \\
+Int32 HighwayHash(4)        & 0,0237\% & 0,001135  & 0,000002 & 0,00001 \\
+Int32 HighwayHash(64)       & 0,0117\% & 0,001028  & 0,000002 & 0,00078 \\
+Int32 HighwayHash(1000)     & 0,0103\% & 0,00092   & 0,000002 & 0,00032 \\
+Int32 T1ha(4)               & 0,021\%  & 0,001034  & 0,000002 & 0,00002 \\
+Int32 T1ha(64)              & 0,0123\% & 0,000933  & 0,000002 & 0,00047 \\
+Int32 T1ha(1000)            & 0,0114\% & 0,001087  & 0,000002 & 0,00027 \\
+UInt32 XxHash(4)            & 0,0119\% & 0,00102   & 0,000002 & 0,00027 \\
+UInt32 XxHash(64)           & 0,013\%  & 0,000871  & 0,000002 & 0,00083 \\
+UInt32 XxHash(1000)         & 0,0131\% & 0,001214  & 0,000002 & 0,00038 \\
+UInt32 Fnv1a(4)             & 0,031\%  & 0,001008  & 0,000002 & 0,20155 \\
+UInt32 Fnv1a(64)            & 0,0094\% & 0,000748  & 0,000002 & 0,08599 \\
+UInt32 Fnv1a(1000)          & 0,0138\% & 0,000821  & 0,000002 & 0,07861 \\
+UInt32 Crc(4)               & 0,0119\% & 0,000811  & 0,000002 & 0,11689 \\
+UInt32 Crc(64)              & 0,0117\% & 0,001041  & 0,000002 & 0,02473 \\
+UInt32 Crc(1000)            & 0,0123\% & 0,001097  & 0,000002 & 0,00514 \\
+\hline
+\end{tabular}
+\caption{Your Table Caption Here}
+\label{tab:my_label}
+\end{table}
 
+Du blabla
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\textwidth]{quality-random.png}
+\caption{Distribution map for random dataset}
+\label{fig:quality-random}
+\end{figure}
+
+Encore du blabla
+
+\clearpage
+\paragraph{Sequential Number}\leavevmode\\
 Sequential inputs to observe how the function handles closely related values. Typically, close values would highlight weaknesses in distribution.
 
-\paragraph{English Words}
+\begin{table}[H]
+\centering
+\begin{tabular}{|l|r|r|r|r|}
+\hline
+\textbf{Function for Sequential dataset} & \textbf{Collisions} & \textbf{Bits Distribution} & \textbf{Distribution} & \textbf{Avalanche} \\
+\hline
+Int32 GxHash0(4)                & 0,0104\% & 0,000009  & 0,000002 & 0,00308 \\
+Int32 GxHash0(64)               & 0,0106\% & 0,000009  & 0,0000019 & 0,00225 \\
+Int32 GxHash0(1000)             & 0,0104\% & 0,000009  & 0,000002 & 0,00283 \\
+Int32 HighwayHash(4)            & 0,0117\% & 0,00112   & 0,000002 & 0,00011 \\
+Int32 HighwayHash(64)           & 0,0104\% & 0,001204  & 0,000002 & 0,00044 \\
+Int32 HighwayHash(1000)         & 0,0112\% & 0,001188  & 0,000002 & 0,00131 \\
+Int32 T1ha(4)                   & 0,012\%  & 0,000746  & 0,000002 & 0,00076 \\
+Int32 T1ha(64)                  & 0,0125\% & 0,000987  & 0,000002 & 0,00071 \\
+Int32 T1ha(1000)                & 0,0113\% & 0,000944  & 0,000002 & 0,00003 \\
+UInt32 XxHash(4)                & 0\%      & 0,000933  & 0,000002 & 0,00018 \\
+UInt32 XxHash(64)               & 0\%      & 0,000907  & 0,000002 & 0,00046 \\
+UInt32 XxHash(1000)             & 0\%      & 0,001081  & 0,000002 & 0,0007 \\
+UInt32 Fnv1a(4)                 & 0\%      & 0,00009   & 0,0000017 & 0,18255 \\
+UInt32 Fnv1a(64)                & 0\%      & 0,000064  & 0,0000022 & 0,08281 \\
+UInt32 Fnv1a(1000)              & 0\%      & 0,000042  & 0,0000018 & 0,08416 \\
+UInt32 Crc(4)                   & 0\%      & 0,000003  & 0,000002 & 0,11729 \\
+UInt32 Crc(64)                  & 0\%      & 0,000003  & 0,0000004 & 0,02542 \\
+UInt32 Crc(1000)                & 0\%      & 0,00001   & 0,0000004 & 0,0046 \\
+\hline
+\end{tabular}
+\caption{Your Table Caption Here}
+\label{tab:my_label}
+\end{table}
+
+Some blabla
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\textwidth]{quality-sequential.png}
+\caption{Distribution map for sequential dataset}
+\label{fig:quality-sequential}
+\end{figure}
+
+Some more blabla
+
+\clearpage
+\paragraph{English Words}\leavevmode\\
 English words inputs to observe how the function behaves in a "real world scenario"
 
-\begin{figure}[h]
+\begin{table}[H]
 \centering
-\includegraphics[width=1\textwidth]{quality-sequential.png}
-\caption{Merkle–Damgård Construction Overview}
-\label{fig:linear-construction}
-\end{figure}
+\begin{tabular}{|l|r|r|r|r|}
+\hline
+\textbf{Function for MarkovWords dataset} & \textbf{Collisions} & \textbf{Bits Distribution} & \textbf{Distribution} & \textbf{Avalanche} \\
+\hline
+Int32 GxHash0(64)                & 0,0136\% & 0,001082  & 0,000002 & 0,00319 \\
+Int32 GxHash0(1000)              & 0,0119\% & 0,000894  & 0,000002 & 0,0034 \\
+Int32 HighwayHash(64)            & 0,0123\% & 0,000809  & 0,000002 & 0,00048 \\
+Int32 HighwayHash(1000)          & 0,0117\% & 0,00092   & 0,000002 & 0,00078 \\
+Int32 T1ha(64)                   & 0,0111\% & 0,000803  & 0,000002 & 0,00064 \\
+Int32 T1ha(1000)                 & 0,0123\% & 0,001175  & 0,000002 & 0,00135 \\
+UInt32 XxHash(64)                & 0,0106\% & 0,000766  & 0,000002 & 0,00046 \\
+UInt32 XxHash(1000)              & 0,01\%   & 0,000892  & 0,000002 & 0,00021 \\
+UInt32 Fnv1a(64)                 & 0,0122\% & 0,000998  & 0,000002 & 0,08585 \\
+UInt32 Fnv1a(1000)               & 0,0127\% & 0,000993  & 0,000002 & 0,08143 \\
+UInt32 Crc(64)                   & 0,0124\% & 0,000965  & 0,000002 & 0,02467 \\
+UInt32 Crc(1000)                 & 0,0123\% & 0,000708  & 0,000002 & 0,00499 \\
+\hline
+\end{tabular}
+\caption{Your Table Caption Here}
+\label{tab:my_label}
+\end{table}
 
+\clearpage
 \subsection{Performance}

### 2023-10-07 src/gxhash.rs

@@ -169,7 +169,7 @@ pub fn gxhash(input: &[u8]) -> u32 {
         let p = input.as_ptr() as *const i8;
         let mut v = p as *const state;
         let mut end_address: usize;
-
+        let mut remaining_blocks_count: isize = len / VECTOR_SIZE;
         let mut hash_vector: state = create_empty();
 
         macro_rules! count_for_tests {
@@ -219,13 +219,29 @@ pub fn gxhash(input: &[u8]) -> u32 {
         
             hash_vector = compress(compress(compress(compress(compress(compress(compress(s0, s1), s2), s3), s4), s5), s6), s7);
 
-            let remaining_blocks_count: isize = (len / VECTOR_SIZE) - unrollable_blocks_count;
-            end_address = v.offset(remaining_blocks_count) as usize;
+            remaining_blocks_count -= unrollable_blocks_count;
         }
-        else
-        {
-            end_address = v.offset(len / VECTOR_SIZE) as usize;
-        }
+
+        end_address = v.offset(remaining_blocks_count) as usize;
+
+        // Temp
+        // let unrollable_blocks_count: isize = (len / (VECTOR_SIZE * UNROLL_FACTOR)) * UNROLL_FACTOR;
+        // let remaining_blocks_count: isize = (len / VECTOR_SIZE) - unrollable_blocks_count;
+        // end_address = v.offset(unrollable_blocks_count) as usize;
+        // //let mut block = create_empty();
+        // while (v as usize) < end_address {
+                
+        //     count_for_tests!();
+        //     load_unaligned!(v0, v1, v2, v3, v4, v5, v6, v7);
+
+        //     prefetch(v);
+
+        //     //v0 = compress(compress(compress(compress(compress(compress(compress(v0, v1), v2), v3), v4), v5), v6), v7);
+        //     v0 = compress(v0, v1);
+
+        //     hash_vector = compress(hash_vector, v0);
+        // }
+        // end_address = v.offset(remaining_blocks_count) as usize;
 
         while (v as usize) < end_address {
             count_for_tests!();

### 2023-10-07 benches/throughput.rs
Use _mm256_aesdeclast for compression and finalize laned compression in a tree fashion

@@ -41,7 +41,7 @@ criterion_group! {
     name = benches;
     config = Criterion::default()
         .sample_size(1000)
-        .measurement_time(Duration::from_secs(3));
+        .measurement_time(Duration::from_secs(5));
     targets = gxhash_benchmark,
 }
 criterion_main!(benches);

### 2023-10-07 src/gxhash.rs
Use _mm256_aesdeclast for compression and finalize laned compression in a tree fashion

@@ -121,8 +121,9 @@ mod platform_defs {
 
     #[inline]
     pub unsafe fn compress(a: state, b: state) -> state {
-        let sum: state = _mm256_add_epi8(a, b);
-        _mm256_alignr_epi8(sum, sum, 1)
+        //let sum: state = _mm256_add_epi8(a, b);
+        //_mm256_alignr_epi8(sum, sum, 1)
+        _mm256_aesdeclast_epi128(a, b)
     }
 
     #[inline]
@@ -217,7 +218,10 @@ pub fn gxhash(input: &[u8]) -> u32 {
                 s7 = compress(s7, v7);
             }
         
-            hash_vector = compress(compress(compress(compress(compress(compress(compress(s0, s1), s2), s3), s4), s5), s6), s7);
+            //hash_vector = _mm256_aesdeclast_epi128(_mm256_aesdeclast_epi128(_mm256_aesdeclast_epi128(_mm256_aesdeclast_epi128(_mm256_aesdeclast_epi128(_mm256_aesdeclast_epi128(_mm256_aesdeclast_epi128(s0, s1), s2), s3), s4), s5), s6), s7);
+            let a = compress(compress(s0, s1), compress(s2, s3));
+            let b = compress(compress(s4, s5), compress(s6, s7));
+            hash_vector = compress(a, b);
 
             remaining_blocks_count -= unrollable_blocks_count;
         }
@@ -243,7 +247,7 @@ pub fn gxhash(input: &[u8]) -> u32 {
         // }
         // end_address = v.offset(remaining_blocks_count) as usize;
 
-        while (v as usize) < end_address {
+        while likely((v as usize) < end_address) {
             count_for_tests!();
             load_unaligned!(v0);
             hash_vector = compress(hash_vector, v0);

### 2023-10-09 src/gxhash.rs
Cleanup tests

@@ -154,18 +154,12 @@ use std::intrinsics::likely;
 
 pub use platform_defs::*;
 
-#[cfg(test)]
-pub static mut COUNTERS : Vec<usize> = vec![];
-
 #[inline] // To be disabled when profiling
 pub fn gxhash(input: &[u8]) -> u32 {
     unsafe {
         const VECTOR_SIZE: isize = std::mem::size_of::<state>() as isize;
-        const UNROLL_FACTOR: isize = 8;
-    
+        
         let len: isize = input.len() as isize;
-    
-        let remaining_bytes = len & (VECTOR_SIZE - 1);
     
         let p = input.as_ptr() as *const i8;
         let mut v = p as *const state;
@@ -173,16 +167,6 @@ pub fn gxhash(input: &[u8]) -> u32 {
         let mut remaining_blocks_count: isize = len / VECTOR_SIZE;
         let mut hash_vector: state = create_empty();
 
-        macro_rules! count_for_tests {
-            () => {
-                #[cfg(test)]
-                {
-                    let index = ((v as usize) - (p as usize)) / VECTOR_SIZE as usize;
-                    COUNTERS.push(index);
-                }
-            };
-        }
-        
         macro_rules! load_unaligned {
             ($($var:ident),+) => {
                 $(
@@ -193,17 +177,16 @@ pub fn gxhash(input: &[u8]) -> u32 {
             };
         }
 
+        const UNROLL_FACTOR: isize = 8;
         if len >= VECTOR_SIZE * UNROLL_FACTOR {
 
             let unrollable_blocks_count: isize = (len / (VECTOR_SIZE * UNROLL_FACTOR)) * UNROLL_FACTOR; 
             end_address = v.offset(unrollable_blocks_count) as usize;
     
-            count_for_tests!();
             load_unaligned!(s0, s1, s2, s3, s4, s5, s6, s7);
  
             while (v as usize) < end_address {
                 
-                count_for_tests!();
                 load_unaligned!(v0, v1, v2, v3, v4, v5, v6, v7);
 
                 prefetch(v);
@@ -218,7 +201,6 @@ pub fn gxhash(input: &[u8]) -> u32 {
                 s7 = compress(s7, v7);
             }
         
[…]

### 2023-10-09 article/article.tex
Add more benchmark results

@@
 \hline
-Int32 GxHash0(64)                & 0,0136\% & 0,001082  & 0,000002 & 0,00319 \\
-Int32 GxHash0(1000)              & 0,0119\% & 0,000894  & 0,000002 & 0,0034 \\
-Int32 HighwayHash(64)            & 0,0123\% & 0,000809  & 0,000002 & 0,00048 \\
-Int32 HighwayHash(1000)          & 0,0117\% & 0,00092   & 0,000002 & 0,00078 \\
-Int32 T1ha(64)                   & 0,0111\% & 0,000803  & 0,000002 & 0,00064 \\
-Int32 T1ha(1000)                 & 0,0123\% & 0,001175  & 0,000002 & 0,00135 \\
+UInt32 GxHash0(64)                & 0,0136\% & 0,001082  & 0,000002 & 0,00319 \\
+UInt32 GxHash0(1000)              & 0,0119\% & 0,000894  & 0,000002 & 0,0034 \\
+UInt32 HighwayHash(64)            & 0,0123\% & 0,000809  & 0,000002 & 0,00048 \\
+UInt32 HighwayHash(1000)          & 0,0117\% & 0,00092   & 0,000002 & 0,00078 \\
+UInt32 T1ha(64)                   & 0,0111\% & 0,000803  & 0,000002 & 0,00064 \\
+UInt32 T1ha(1000)                 & 0,0123\% & 0,001175  & 0,000002 & 0,00135 \\
 UInt32 XxHash(64)                & 0,0106\% & 0,000766  & 0,000002 & 0,00046 \\
@@
 
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\textwidth]{quality-markov.png}
+\caption{Distribution map for markov dataset}
+\label{fig:quality-sequential}
+\end{figure}
+
 \clearpage
@@
 \includegraphics[width=1\textwidth]{throughput.png}
-\caption{Throughput Benchmark Results}
 \label{fig:benchmark-throughput}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\textwidth]{throughput-gcp.png}
+\label{fig:benchmark-throughput-gcp}
 \end{figure}

### 2023-10-10 article/article.tex
Adapt gxhash for arm neon

@@
 This ensures that, when used in applications like hash tables, the data is spread evenly, reducing clustering and the frequency of collisions.
+
+    We can estimate the uniformity of the distribution by counting the number of times each bit is set and computing a standard deviation.
+This "bit distribution" criteria however does not qualifies the distributiono of the hashes a whole, so a complementary estimator is the "bucketed distribution", which be computed by placing generated hashes into a fixed size grid and counting occurences.
+This can also be easily displayed as a bitmap as a convenient way to visualize distribution.
     \item \textbf{Minimal Collisions:} While no hash function can be entirely collision-free due to the pigeonhole principle, a good non-cryptographic hash should minimize collisions for typical input sets, ensuring that different inputs usually produce distinct outputs.
+
+    The collison rate can be computed by counting unique values with the help of an hash table.
     \item \textbf{Avalanche Effect:} A subtle change in the input should result in a considerably different output, ensuring sensitivity to input variations.
 This also contributes to lessen the risk of clustered hashes in applications like hash tables.
+
+    The avalanche effect can be computed by fliping a single random bit for given input and checking the differences between the hashes generated before and after the bit was flipped.
+Ideally, half of the bit should change on average.
     \item \textbf{Performance:} The performance of a non cryptographic hash function is usually reflected by the performance of the application using it.
@@
 This specific criteria will be tackled in the next section which is dedicated to it.
+
 \end{itemize}
@@
 
-Todo: Actual funcs used ? Like what is bits distribution vs distribution ?
+For comparison, we'll also include qualification results for a few other popular non-cryptographic hash algorithms such as:
+
+\begin{itemize}
+\item \textbf{HighwayHash}\cite{highwayhash} The latest non-cryptographic hash algorithm from Google Research
+\item \textbf{xxHash}\cite{twox-hash} Recently a very popular algorithm for fast non-cryptographic hashing
+\item \textbf{t1ha0}\cite{rust-t1ha} Supposedly the fastest algorithm
+\end{itemize}
 
@@
 \paragraph{Random Blobs}\leavevmode\\
-Randomly generated inputs to observe how the hash function behaves with truly unpredictable data
+For the first scenario we randomly generate 1,000,000 inputs of size 4 bytes, 64 and 1000 to observe how the hash function behaves with truly unpredictable data, and for different input sizes.
 
@@
 \hline
-Int32 GxHash0(4)            & 0,0241\% & 0,001094  & 0,000002 & 0,00412 \\
-Int32 GxHash0(64)           & 0,0103\% & 0,001081  & 0,000002 & 0,00296 \\
-Int32 GxHash0(1000)         & 0,012\%  & 0,001148  & 0,000002 & 0,00336 \\
-Int32 HighwayHash(4)        & 0,0237\% & 0,001135  & 0,000002 & 0,00001 \\
-Int32 HighwayHash(64)       & 0,0117\% & 0,001028  & 0,000002 & 0,00078 \\
-Int32 HighwayHash(1000)     & 0,0103\% & 0,00092   & 0,000002 & 0,00032 \\
-Int32 T1ha(4)               & 0,021\%  & 0,001034  & 0,000002 & 0,00002 \\
-Int32 T1ha(64)              & 0,0123\% & 0,000933  & 0,000002 & 0,00047 \\
-Int32 T1ha(1000)            & 0,0114\% & 0,001087  & 0,000002 & 0,00027 \\
+UInt32 GxHash0(4)            & 0,0241\% & 0,001094  & 0,000002 & 0,00412 \\
+UInt32 GxHash0(64)           & 0,0103\% & 0,001081  & 0,000002 & 0,00296 \\
+UInt32 GxHash0(1000)         & 0,012\%  & 0,001148  & 0,000002 & 0,00336 \\
+UInt32 HighwayHash(4)        & 0,0237\% & 0,001135  & 0,000002 & 0,00001 \\
+UInt32 HighwayHash(64)       & 0,0117\% & 0,001028  & 0,000002 & 0,00078 \\
+UInt32 HighwayHash(1000)     & 0,0103\% & 0,00092   & 0,000002 & 0,00032 \\
+UInt32 T1ha(4)               & 0,021\%  & 0,001034  & 0,000002 & 0,00002 \\
+UInt32 T1ha(64)              & 0,0123\% & 0,000933  & 0,000002 & 0,00047 \\
+UInt32 T1ha(1000)            & 0,0114\% & 0,001087  & 0,000002 & 0,00027 \\
 UInt32 XxHash(4)            & 0,0119\% & 0,00102   & 0,000002 & 0,00027 \\
@@
 UInt32 XxHash(1000)         & 0,0131\% & 0,001214  & 0,000002 & 0,00038 \\
-UInt32 Fnv1a(4)             & 0,031\%  & 0,001008  & 0,000002 & 0,20155 \\
-UInt32 Fnv1a(64)            & 0,0094\% & 0,000748  & 0,000002 & 0,08599 \\
-UInt32 Fnv1a(1000)          & 0,0138\% & 0,000821  & 0,000002 & 0,07861 \\
-UInt32 Crc(4)               & 0,0119\% & 0,000811  & 0,000002 & 0,11689 \\
-UInt32 Crc(64)              & 0,0117\% & 0,001041  & 0,000002 & 0,02473 \\
+UInt32 Fnv1a(4)             & 0,031\%  & 0,001008  & 0,000002 & \textcolor{red}{0,20155} \\
+UInt32 Fnv1a(64)            & 0,0094\% & 0,000748  & 0,000002 & \textcolor{orange}{0,08599} \\
+UInt32 Fnv1a(1000)          & 0,0138\% & 0,000821  & 0,000002 & \textcolor{orange}{0,07861} \\
+UInt32 Crc(4)               & 0,0119\% & 0,000811  & 0,000002 & \textcolor{red}{0,11689} \\
+UInt32 Crc(64)              & 0,0117\% & 0,001041  & 0,000002 & \textcolor{orange}{0,02473} \\
 UInt32 Crc(1000)            & 0,0123\% & 0,001097  & 0,000002 & 0,00514 \\
@@
 \caption{Your Table Caption Here}
-\label{tab:my_label}
+\label{tab:quality-data-random}
 \end{table}
 
-Du blabla
+All numbers are very low, and GxHash0 quality results is of the same order of magnitude as for other algoririthms.
+We can notice however a collision rate of about 0.011\% and even 0.022\% for a few of them for the 4 bytes input.
+There is however an explanation: we can derive from the birthday paradox problem the following formula to
+estimate the \% of collisions:
+
+\begin{align*}
+    100 \times \frac{n^2}{2 \times m \times n}
+\end{align*}
+
+Where \(n\) is the number of samples and \(m\) the number of possible of values. When \(n=1000000\) and \(m=2^32\) we obtain 0.0116\%.
+You can see that this value closely matches most of the collision rates benchmarked. This is because the generated hashes are of 32 bit size,
+thus naturally colliding at this rate.
+For inputs of size 4, the inputs themselves are also likely to collide with the same odds (because inputs are randomly generated).
+For this reason, the collision rate is expected to be about 2 \(\times\) 0.0116\%.
+We can however see however that Crc and XxHash have lower odds of collisions for 4 bytes input, which can be explained by a size-specific logic to handle small inputs bijectively.
 
@@
 \hline
-Int32 GxHash0(4)                & 0,0104\% & 0,000009  & 0,000002 & 0,00308 \\
-Int32 GxHash0(64)               & 0,0106\% & 0,000009  & 0,0000019 & 0,00225 \\
-Int32 GxHash0(1000)             & 0,0104\% & 0,000009  & 0,000002 & 0,00283 \\
-Int32 HighwayHash(4)            & 0,0117\% & 0,00112   & 0,000002 & 0,00011 \\
-Int32 HighwayHash(64)           & 0,0104\% & 0,001204  & 0,000002 & 0,00044 \\
-Int32 HighwayHash(1000)         & 0,0112\% & 0,001188  & 0,000002 & 0,00131 \\
-Int32 T1ha(4)                   & 0,012\%  & 0,000746  & 0,000002 & 0,00076 \\
-Int32 T1ha(64)                  & 0,0125\% & 0,000987  & 0,000002 & 0,00071 \\
-Int32 T1ha(1000)                & 0,0113\% & 0,000944  & 0,000002 & 0,00003 \\
+UInt32 GxHash0(4)                & 0,0104\% & 0,000009  & 0,000002 & 0,00308 \\
+UInt32 GxHash0(64)               & 0,0106\% & 0,000009  & 0,0000019 & 0,00225 \\
+UInt32 GxHash0(1000)             & 0,0104\% & 0,000009  & 0,000002 & 0,00283 \\
+UInt32 HighwayHash(4)            & 0,0117\% & 0,00112   & 0,000002 & 0,00011 \\
+UInt32 HighwayHash(64)           & 0,0104\% & 0,001204  & 0,000002 & 0,00044 \\
+UInt32 HighwayHash(1000)         & 0,0112\% & 0,001188  & 0,000002 & 0,00131 \\
+UInt32 T1ha(4)                   & 0,012\%  & 0,000746  & 0,000002 & 0,00076 \\
+UInt32 T1ha(64)                  & 0,0125\% & 0,000987  & 0,000002 & 0,00071 \\
+UInt32 T1ha(1000)                & 0,0113\% & 0,000944  & 0,000002 & 0,00003 \\
 UInt32 XxHash(4)                & 0\%      & 0,000933  & 0,000002 & 0,00018 \\
@@
 UInt32 XxHash(1000)             & 0\%      & 0,001081  & 0,000002 & 0,0007 \\
-UInt32 Fnv1a(4)                 & 0\%      & 0,00009   & 0,0000017 & 0,18255 \\
-UInt32 Fnv1a(64)                & 0\%      & 0,000064  & 0,0000022 & 0,08281 \\
-UInt32 Fnv1a(1000)              & 0\%      & 0,000042  & 0,0000018 & 0,08416 \\
-UInt32 Crc(4)                   & 0\%      & 0,000003  & 0,000002 & 0,11729 \\
-UInt32 Crc(64)                  & 0\%      & 0,000003  & 0,0000004 & 0,02542 \\
+UInt32 Fnv1a(4)                 & 0\%      & 0,00009   & 0,0000017 & \textcolor{red}{0,18255} \\
+UInt32 Fnv1a(64)                & 0\%      & 0,000064  & 0,0000022 & \textcolor{orange}{0,08281} \\
+UInt32 Fnv1a(1000)              & 0\%      & 0,000042  & 0,0000018 & \textcolor{orange}{0,08416} \\
+UInt32 Crc(4)                   & 0\%      & 0,000003  & 0,000002 & \textcolor{red}{0,11729} \\
+UInt32 Crc(64)                  & 0\%      & 0,000003  & 0,0000004 & \textcolor{orange}{0,02542} \\
 UInt32 Crc(1000)                & 0\%      & 0,00001   & 0,0000004 & 0,0046 \\
@@
 UInt32 XxHash(1000)              & 0,01\%   & 0,000892  & 0,000002 & 0,00021 \\
-UInt32 Fnv1a(64)                 & 0,0122\% & 0,000998  & 0,000002 & 0,08585 \\
-UInt32 Fnv1a(1000)               & 0,0127\% & 0,000993  & 0,000002 & 0,08143 \\
-UInt32 Crc(64)                   & 0,0124\% & 0,000965  & 0,000002 & 0,02467 \\
+UInt32 Fnv1a(64)                 & 0,0122\% & 0,000998  & 0,000002 & \textcolor{orange}{0,08585} \\
+UInt32 Fnv1a(1000)               & 0,0127\% & 0,000993  & 0,000002 & \textcolor{orange}{0,08143} \\
+UInt32 Crc(64)                   & 0,0124\% & 0,000965  & 0,000002 & \textcolor{orange}{0,02467} \\
 UInt32 Crc(1000)                 & 0,0123\% & 0,000708  & 0,000002 & 0,00499 \\
@@
 \includegraphics[width=1\textwidth]{throughput.png}
+\caption{Gibibytes of data hashed per second (throughput) per input size}
 \label{fig:benchmark-throughput}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=1\textwidth]{throughput-gcp.png}
-\label{fig:benchmark-throughput-gcp}
 \end{figure}

### 2023-10-10 src/gxhash.rs
Adapt gxhash for arm neon

@@ -42,20 +42,47 @@ mod platform_defs {
 
     #[inline]
     pub unsafe fn compress(a: state, b: state) -> state {
-        let sum: state = vaddq_s8(a, b);
-        vextq_s8(sum, sum, 1) 
+        ReinterpretUnion{ uint8: aes_encrypt_last(
+            ReinterpretUnion{ int8: a }.uint8, 
+            ReinterpretUnion{ int8: b }.uint8) }.int8
+    }
+
+    #[inline]
+    // See https://blog.michaelbrase.com/2018/05/08/emulating-x86-aes-intrinsics-on-armv8-a
+    unsafe fn aes_encrypt(data: uint8x16_t, keys: uint8x16_t) -> uint8x16_t {
+        // Encrypt
+        let encrypted = vaeseq_u8(data, vdupq_n_u8(0));
+        // Mix columns
+        let mixed = vaesmcq_u8(encrypted);
+        // Xor keys
+        veorq_u8(mixed, keys)
+    }
+
+    #[inline]
+    // See https://blog.michaelbrase.com/2018/05/08/emulating-x86-aes-intrinsics-on-armv8-a
+    unsafe fn aes_encrypt_last(data: uint8x16_t, keys: uint8x16_t) -> uint8x16_t {
+        // Encrypt
+        let encrypted = vaeseq_u8(data, vdupq_n_u8(0));
+        // Xor keys
+        veorq_u8(encrypted, keys)
     }
 
     #[inline]
     pub unsafe fn finalize(hash: state) -> u32 {
-        let salt = vcombine_s64(vcreate_s64(4860325414534694371), vcreate_s64(8120763769363581797));
-        let keys = vmulq_s32(
-            ReinterpretUnion { int64: salt }.int32,
-            ReinterpretUnion { int8: hash }.int32);
-        let a = vaeseq_u8(ReinterpretUnion { int8: hash }.uint8, vdupq_n_u8(0));
-        let b = vaesmcq_u8(a);
-        let c = veorq_u8(b, ReinterpretUnion{ int32: keys }.uint8);
-        let p = &ReinterpretUnion{ uint8: c }.int8 as *const state as *const u32;
+        // Hardcoded AES keys
+        let salt1 = vld1q_u32([0x713B01D0, 0x8F2F35DB, 0xAF163956, 0x85459F85].as_ptr());
[…]

### 2023-10-11 article/article.tex
More writing  🤓

@@
 \item \textbf{xxHash}\cite{twox-hash} Recently a very popular algorithm for fast non-cryptographic hashing
-\item \textbf{t1ha0}\cite{rust-t1ha} Supposedly the fastest algorithm
+\item \textbf{t1ha0}\cite{rust-t1ha} Supposedly the fastest algorithm at the time of writing
 \end{itemize}
@@
 \end{tabular}
-\caption{Your Table Caption Here}
+\caption{Quality benchmark results for random datasets at 1,000,000 iterations}
 \label{tab:quality-data-random}
@@
 
-All numbers are very low, and GxHash0 quality results is of the same order of magnitude as for other algoririthms.
-We can notice however a collision rate of about 0.011\% and even 0.022\% for a few of them for the 4 bytes input.
-There is however an explanation: we can derive from the birthday paradox problem the following formula to
+All numbers are very low, and GxHash0 quality results are of the same order of magnitude as for other algorithms.
+Distribution is very good for all algorithms.
+Avalanche is good for most algorithms, excepted for FNV-1a and CRC.
+
+We can notice a collision rate of about 0.011\% and even 0.022\% for the 4 bytes inputs. There is an explanation: we can derive from the birthday paradox problem the following formula to
 estimate the \% of collisions:
@@
 
-Where \(n\) is the number of samples and \(m\) the number of possible of values. When \(n=1000000\) and \(m=2^32\) we obtain 0.0116\%.
+Where \(n\) is the number of samples and \(m\) the number of possible of values. When \(n=1000000\) and \(m=2^{32}\) we obtain 0.0116\%.
 You can see that this value closely matches most of the collision rates benchmarked. This is because the generated hashes are of 32 bit size,
@@
 For this reason, the collision rate is expected to be about 2 \(\times\) 0.0116\%.
-We can however see however that Crc and XxHash have lower odds of collisions for 4 bytes input, which can be explained by a size-specific logic to handle small inputs bijectively.
+We can see however that CRC and XxHash have lower odds of collisions for 4 bytes input, which can be explained by a size-specific logic to handle small inputs bijectively.
 
@@
 
-Encore du blabla
+Here is a visualization of the distribution represented by bitmap, whith each pixel being a bucket for generated hashes to fill.
+A black pixel is an empty pixel, and the whiter a pixel is the fuller of hashes the bucket is.
+
+We can see that all algorithms benchmarked have similar output in the case of random inputs, which is similar to noise noise.
+The lack of visible frequencies or "patterns" is a sign of good distriubtion.
+At a glance, we can see that all algorithms benchmarks have a good distribution for this dataset.
 
 \clearpage
-\paragraph{Sequential Number}\leavevmode\\
-Sequential inputs to observe how the function handles closely related values. Typically, close values would highlight weaknesses in distribution.
+\paragraph{Sequential Numbers}\leavevmode\\
+For the second scenario we generate consecutive integers as inputs to observe how the function handles closely related values.
+Typically, close values could highlight potential weaknesses in distribution.
+We still run a number of 1,000,000 iterations, meaning that inputs will be integers from 1 to 1,000,000.
+Consequently, input bytes after the 4th will always remain 0, even for larger inputs.
+This can also be a challenge for a hash algorithms to keep entropy from the first few bytes of the input despite having to process many 0-bytes afterwards.
 
@@
 \end{tabular}
-\caption{Your Table Caption Here}
+\caption{Quality benchmark results for sequential datasets at 1,000,000 iterations}
 \label{tab:my_label}
@@
 
-Some blabla
+We still observe about 0.0116\% of collisions, which is still expected given the size of the hashes generated and the number of iterations.
+We can notice however that a few algorithms have managed to have 0 collisions.
+This is an interesting feature but nevertheless anecdotical: as inputs of this dataset may only have at most the four first bytes different than zero, some algorithms are able to keep the possible bijectivity.
+
+Regarding distribution, we can notice that GxHash0 outperforms HighwayHash, XxHash and T1ha0.
+Avalanche is slightly worse however, possibily due to the tradeoff of doing less operations for greater performances.
+Overall, the numbers are all still very low and remain in the same ballpark, except for FNV-1a and CRC that still suffers from a relatively "high" avalanche.
 

### 2023-10-12 article/article.tex
Article ready for review

@@
 
-In light of these practical challenges, tree-based constructions might not be the best fit given our high performance goals and the architecture of today's general-purpose computers.
+In light of these practical challenges, tree-based constructions might not be the best fit given our high-performance goals and the architecture of today's general-purpose computers.
 
@@
 
-In practice, a program usually allocates memory with some degree of alignment, and so data is generally aligned.
+In practice, programs typically allocate memory with alignment, ensuring data is generally aligned.
 However, a given input message to our hash function is still not guaranteed to be aligned.
@@
 In practice, a naive implementation for \( p \) for GxHash in computer code implies copying the remaining bytes into a zero-initialized buffer of size \( s_b \), which can then be loaded onto an SIMD registry and then handed to the compression.
-In our performance-critical context, these allocations and copies have a substantial overhead.
+In our performance-critical context, these allocations and copies introduce significant overhead.
 
@@
     We can estimate the uniformity of the distribution by counting the number of times each bit is set and computing a standard deviation.
-This "bit distribution" criteria however does not qualifies the distributiono of the hashes a whole, so a complementary estimator is the "bucketed distribution", which be computed by placing generated hashes into a fixed size grid and counting occurences.
+This "bit distribution" criteria however does not qualify the distribution of the hashes as a whole, so a complementary estimator is the "bucketed distribution", which be computed by placing generated hashes into a fixed-size grid and counting occurrences.
 This can also be easily displayed as a bitmap as a convenient way to visualize distribution.
@@
 
-    The collison rate can be computed by counting unique values with the help of an hash table.
+    The collision rate can be computed by counting unique values with the help of an hash table.
     \item \textbf{Avalanche Effect:} A subtle change in the input should result in a considerably different output, ensuring sensitivity to input variations.
-This also contributes to lessen the risk of clustered hashes in applications like hash tables.
+This also contributes to lessening the risk of clustered hashes in applications like hash tables.
 
-    The avalanche effect can be computed by fliping a single random bit for given input and checking the differences between the hashes generated before and after the bit was flipped.
+    The avalanche effect can be computed by flipping a single random bit for a given input and checking the differences between the hashes generated before and after the bit was flipped.
 Ideally, half of the bit should change on average.
-    \item \textbf{Performance:} The performance of a non cryptographic hash function is usually reflected by the performance of the application using it.
+    \item \textbf{Performance:} The performance of a noncryptographic hash function is usually reflected by the performance of the application using it.
 For instance, a fast non-cryptographic hash function generally implies a fast hash table.
@@
 While we can compute quality metrics, the result will greatly vary depending on the actual inputs used for our hash function.
-Let's see how the GxHash0 algorithm qualifies against a few well known non-cryptographic algorithm in a few scenarios.
+Let's see how the GxHash0 algorithm qualifies against a few well-known non-cryptographic algorithms in a few scenarios.
 
@@
 \item \textbf{HighwayHash}\cite{highwayhash} The latest non-cryptographic hash algorithm from Google Research
-\item \textbf{xxHash}\cite{twox-hash} Recently a very popular algorithm for fast non-cryptographic hashing
+\item \textbf{xxHash}\cite{xxhash} Recently a very popular algorithm for fast non-cryptographic hashing
 \item \textbf{t1ha0}\cite{rust-t1ha} Supposedly the fastest algorithm at the time of writing
@@
 \paragraph{Random Blobs}\leavevmode\\
-For the first scenario we randomly generate 1,000,000 inputs of size 4 bytes, 64 and 1000 to observe how the hash function behaves with truly unpredictable data, and for different input sizes.
+For the first scenario, we randomly generate 1,000,000 inputs of size 4 bytes, 64 and 1000 to observe how the hash function behaves with truly unpredictable data, and for different input sizes.
 
@@
 \end{tabular}
-\caption{Quality benchmark results for random datasets at 1,000,000 iterations}
+\caption{Quality benchmark results for the random dataset at 1,000,000 iterations}
 \label{tab:quality-data-random}
@@
 Distribution is very good for all algorithms.
-Avalanche is good for most algorithms, excepted for FNV-1a and CRC.
+Avalanche is good for most algorithms, except for FNV-1a and CRC.
 
@@
 
-Where \(n\) is the number of samples and \(m\) the number of possible of values. When \(n=1000000\) and \(m=2^{32}\) we obtain 0.0116\%.
-You can see that this value closely matches most of the collision rates benchmarked. This is because the generated hashes are of 32 bit size,
+Where \(n\) is the number of samples and \(m\) is the number of possible values. When \(n=1000000\) and \(m=2^{32}\) we obtain 0.0116\%.
+You can see that this value closely matches most of the collision rates benchmarked. This is because the generated hashes are of 32-bit size,
 thus naturally colliding at this rate.
@@
 
-Here is a visualization of the distribution represented by bitmap, whith each pixel being a bucket for generated hashes to fill.
+Here is a visualization of the distribution represented by bitmap, which each pixel being a bucket for generated hashes to fill.
 A black pixel is an empty pixel, and the whiter a pixel is the fuller of hashes the bucket is.
@@
 We can see that all algorithms benchmarked have similar output in the case of random inputs, which is similar to noise noise.
-The lack of visible frequencies or "patterns" is a sign of good distriubtion.
-At a glance, we can see that all algorithms benchmarks have a good distribution for this dataset.
+The lack of visible frequencies or "patterns" is a sign of good distribution.
+At a glance, we can see that all algorithm benchmarks have a good distribution for this dataset.
 
@@
 \paragraph{Sequential Numbers}\leavevmode\\
-For the second scenario we generate consecutive integers as inputs to observe how the function handles closely related values.
+For the second scenario, we generate consecutive integers as inputs to observe how the function handles closely related values.
 Typically, close values could highlight potential weaknesses in distribution.
@@
 Consequently, input bytes after the 4th will always remain 0, even for larger inputs.
-This can also be a challenge for a hash algorithms to keep entropy from the first few bytes of the input despite having to process many 0-bytes afterwards.
+This can also be a challenge for a hash algorithm to keep entropy from the first few bytes of the input despite having to process many 0-bytes afterward.
 
@@
 \end{tabular}
-\caption{Quality benchmark results for sequential datasets at 1,000,000 iterations}
+\caption{Quality benchmark results for the sequential dataset at 1,000,000 iterations}
 \label{tab:my_label}
@@
 
-Regarding distribution, we can notice that GxHash0 outperforms HighwayHash, XxHash and T1ha0.
-Avalanche is slightly worse however, possibily due to the tradeoff of doing less operations for greater performances.
-Overall, the numbers are all still very low and remain in the same ballpark, except for FNV-1a and CRC that still suffers from a relatively "high" avalanche.
+Regarding distribution, we can notice that GxHash0 outperforms HighwayHash\cite{highwayhash}, XxHash\cite{xxhash} and T1ha0\cite{rust-t1ha}.
+Avalanche is slightly worse, however, possibly due to the tradeoff of doing fewer operations for greater performances.
+Overall, the numbers are all still very low and remain in the same ballpark, except for FNV-1a and CRC which still suffer from a relatively "high" avalanche.
 
@@
 
-Some more blabla
+The distribution map is more interesting for sequential inputs.
+As a matter of fact, we clearly identify distribution patterns for FNV-1a and CRC.
+It isn't necessarily a bad thing, because a hash function can distribute the hash in a way that the distribution map looks evenly distributed (such as what we observe with CRC with 1000-bytes long inputs), however it implies that values hashes are correlated in a way, which a property we prefer to avoid for a non-cryptographic hash function.
+GxHash0 performs well in that matter, with a distribution that looks as uniform and uncorrelated than its counterparts HighwayHash\cite{highwayhash}, XxHash\cite{xxhash} and T1ha0\cite{rust-t1ha}.
 
@@
 \paragraph{English Words}\leavevmode\\
-English words inputs to observe how the function behaves in a "real world scenario"
+For the third scenario, we generate English-looking words as inputs by deriving a set of "real" English words with Markov chains to be able to generate many unique strings for any size.
+This allows us to observe how the function behaves in a close to "real-world scenario".
+We ignore on-purpose inputs of size 4 since we are not able to generate enough unique strings for that size.
 
@@
 \end{tabular}
-\caption{Your Table Caption Here}
+\caption{Quality benchmark results for words dataset at 1,000,000 iterations}
 \label{tab:my_label}
 \end{table}
+
+We still observe about 0.0116\% of collisions for all algorithms, explainable by the birthday paradox as seen previously.
+This time however, XxHash\cite{xxhash}, Fnv1a and Crc are not able to beep bijectivity as inputs use more bytes compared to the sequential case, making the bijectivity property impossible and thus leading to inevitable collision.
+The bits distribution is very close for all algorithms benchmarked, at about 0.001.
+The avalanche is a little worse for GxHash0 compared to HighwayHash\cite{highwayhash}, XxHash\cite{xxhash} and T1ha\cite{rust-t1ha}, but remains quite good, and is still higher than Fnv1a and Crc avalanche scores.
 
@@
 \includegraphics[width=1\textwidth]{quality-markov.png}
-\caption{Distribution map for markov dataset}
+\caption{Distribution map for words dataset}
 \label{fig:quality-sequential}
 \end{figure}
+
+Bucketed distribution is looking good in all cases for the English words case.
+
+\subsubsection{Conclusion}
+
+This was just an overview of the quality of the hashes produced by GxHash0 and a few comparisons to some established non-cryptographic algorithms.
+
+Our results demonstrate promising quality characteristics of GxHash0 with low collisions, good distribution, and a high avalanche effect, and its quality is comparable to other well-established non-cryptographic algorithms.
+However, it is essential to acknowledge the limitations of the presented evaluation scenarios.
+The benchmarks presented herein, namely random inputs, sequential inputs, and English word inputs, offer a glimpse into the algorithm's quality but are by no means exhaustive.
+In real-world applications, the behavior of a hash algorithm can be influenced by a myriad of factors and specific data patterns.
+As such, while our findings provide a foundational understanding of GxHash0's quality, potential users should be cognizant that results may vary based on the actual use case and the nature of the input data.
 
@@
 
-t1ha\cite{rust-t1ha} xxhash\cite{twox-hash} HighwayHash\cite{highway-rs}
+Performance is measured as a throughput, in gibibytes of data hashed per second (higher is better).
+This is a common measurement unit for performance in this field.
+Performance is measured against inputs of size 4, 16, 64, 246, 1024, 4096 and 16384 to cover a broad range of use cases.
+
+For reference, we'll also benchmark other non-cryptographic algorithms under the same conditions, thanks to their Rust implementations, namely: t1ha\cite{rust-t1ha}, xxhash\cite{twox-hash} and HighwayHash\cite{highway-rs}.
+
+The benchmark is run on three different setups:
+\begin{itemize}
+    \item A Ryzen 5 equipped low-budget desktop PC
+    \item An n2-standard-2 compute GCP virtual machine (likely equipped with an Intel Xeon 8376H). Cloud computing is very popular nowadays and the hardware is quite different from the desktop PC.
+    \item A Macbook Pro with an M1 Pro chip, to test the algorithm on an ARM architecture which implies different SIMD intrinsics and likely different performance results.
+Note that the T1ha-0 implementation benchmarked does not leverage ARM intrinsics, and this is why it is not benchmarked for this platform (the portable version would perform too poorly).
+\end{itemize}
 
@@
 \includegraphics[width=1\textwidth]{throughput.png}
-\caption{Gibibytes of data hashed per second (throughput) per input size}
+\caption{Gibibytes of data hashed per second (throughput) per input size. Log10 scale.}
 \label{fig:benchmark-throughput}
@@
 
+The results are compelling: GxHash0 consistently outperforms its counterparts, achieving throughput rates that are an order of magnitude higher in many instances.
+Depending on the input size, we observed performance gains ranging from x5 to an impressive x210.
+On the GCP and Apple M1 Pro benchmarks, the algorithm reaches an impressive 10 Gb/s for 4 bytes inputs, likely showing that the algorithm is memory-bound (and thus can hardly be faster).
+A second observation is a substantial gap in performances between 64 and 256 bytes inputs, which can be explained by the 8-lane processing starting to kick in when inputs are large enough, leveraging ILP for even more throughput.
+
+While these results are promising, it's essential to approach them with a balanced perspective.
+The benchmarks serve as an indicator of GxHash0's potential in specific scenarios, and while the performance advantage is clear, it's always prudent to consider the broader context and the specific requirements of any given application before drawing definitive conclusions.
+
 \section{Discussion}
-\subsection{Implications}
 \subsection{Limitations}
+
+\subsubsection{Portability}
+As mentioned at the beginning of this paper, portability wasn't a design goal for GxHash-0.
+Consequently, while GxHash-0 can work on different platforms (x86, ARM, and possibly more), it is not recommended to have the hashes outlive the process lifetime, as there is a risk for persistent hashes to imply a hardware dependency afterward, which is something we generally want to avoid.
+We think it is an acceptable limitation when GxHash0 is used at the process scope, such as for hashtables for instance.
+It would be possible however to derive from the GxHash0 implementation presented in this paper to come up with a portable version, but likely at the cost of performance.
+
+\subsubsection{Compiler Dependencies} 
+The Laned Construction presented in this paper is implemented for GxHash0 by declaring each lane with its own variable.
+While it worked at the time of writing (rustc 1.68.0), it is in the end the compiler's responsibility to decide how many registers to use.
+We cannot exclude that in another context (different version, different language/compiler, ...) the compiler will undo the ILP we tried to implicitly introduce.
+This could be countered by writing the algorithm directly in assembly code, at the cost of complexity.
+
 \subsection{Future Work}
+Despite the outstanding benchmark results, we think there are still many possible paths for research and improvement. Here is a non-exhaustive list:
+\begin{itemize}
+    \item Leveraging larger SIMD intrinsics, such as Intel AVX-512 or ARM SVE2.
+    \item Using leading zero count intrinsics followed by a C-style fallthrough to process small inputs faster.
+    \item Rewrite the algorithm in assembly code or a language that is more explicit about registers.
+    \item Introduce more than one stage of laning. For instance 16 lanes, then 8 lanes, then 4 lanes, and finally 2 lanes, to leverage ILP as much as possible.
+    \item Fine-tune the finalization stage to find the perfect balance between performance and avalanche effect.
+\end{itemize}
 
 \section{Conclusion}
+
+By leveraging the capabilities of modern CPUs, such as Single Instruction, Multiple Data (SIMD), GxHash0 achieves unparalleled throughput, setting a new standard for efficiency and performance amongst non-cryptographic hashing algorithms.
+A pivotal innovation in this endeavor is the "Laned Construction," which is specifically designed to harness Instruction-Level Parallelism (ILP), further optimizing the hashing process.
+
+However, it's essential to note that while GxHash0 offers significant improvements, the behavior of any hash algorithm can be influenced by various factors.
+As such, potential users should approach with an understanding that results might vary based on specific use cases and input data.\\
+
+The capabilities of GxHash0 represent a significant step forward in non-cryptographic hashing.
+In a world where real-time processing is becoming a standard, this algorithm not only enables systems to respond more swiftly but also promotes greater energy efficiency.
 

### 2023-10-12 article/article.tex
Update readme

@@
 
+\subsubsection{Multithreading}
+
 This paper primarily investigates methods for enhancing the throughput of non-cryptographic hashing algorithms, which are commonly used in a variety of time-sensitive applications, including but not limited to hashmap lookups.
 In such contexts, hash computation is often expected to be extremely fast, typically requiring execution times ranging from nanoseconds to microseconds.
-Given these considerations, the paper intentionally excludes Thread-Level Parallelism
+Given these consideration, the paper intentionally excludes Thread-Level Parallelism
 (TLP) as a viable strategy for performance optimization.\\\\
@@
 \subsubsection{Portability}
+
+Ensuring portability (algorithm generating the same hashes consistently accross different platforms for a given input) is a constrain that may hinder some potential optimization.
+Our goal being performance first, and our scope of application mainly focused on in-process usages such as hashtables, portability can be left out for these researches.
+Yet, it remains crutial for the algorithm to work under both x86 and ARM 64-bit platforms that represent most of today's general purpose computing systems.
 
@@
 
+\clearpage
 \subsection{The Wide-Pipe Construction Variant} \label{widepipe}
@@
 \end{figure}
+
+An alternative to chaining usages of \( f \) is to compress lane hashes by pair, and subsequently compressing the resulting hashes also by pair until we are left with a single hash (for instance \(f(f(f(H_1, H_2), f(H_3, H_4)), f(...))\)).
+In practice, this would allow some form of ILP on the final hash composition as well, decreasing as we get closer to the final hash.
 

### 2023-10-13 article/article.tex
Fix some typos

@@
 Traditional hashing methods, while effective, often fail to fully utilize the computational capabilities of modern processors.
-This paper introduces the GxHash hashing algorithm, a novel approach that harnesses the power of high instruction-level parallelism (ILP) and Single Instruction, Multiple Data (SIMD) capabilities of contemporary CPUs to achieve high-throughput non-cryptographic hashing.
+This paper introduces the GxHash hashing algorithm, a novel approach that harnesses the power of high Instruction-Level Parallelism (ILP) and Single Instruction, Multiple Data (SIMD) capabilities of contemporary CPUs to achieve high-throughput non-cryptographic hashing.
 Through a comprehensive analysis, including benchmarks and comparisons with existing methods, we demonstrate that GxHash significantly outperforms conventional algorithms in terms of speed and computational efficiency without compromising on security.
@@
 In this high-stakes environment, every millisecond counts, and the performance of underlying data structures becomes critically important.
-We heavily rely on in-memory caches and other hash-based data structures, making the efficiency of hashing algorithms a non-trivial concern in our system's overall performance.\\\\
+As we heavily rely on in-memory caches and other hash-based data structures, making the efficiency of hashing algorithms a non-trivial concern in our system's overall performance.\\\\
 While diving into the theory of hashing out of both necessity and intellectual curiosity, I discovered that existing hashing algorithms, including those built on well-known constructions like Merkle–Damgård, are not optimized to exploit the full capabilities of modern general-purpose CPUs.
@@
 While we can compute quality metrics, the result will greatly vary depending on the actual inputs used for our hash function.
-Let's see how the GxHash0 algorithm qualifies against a few well-known non-cryptographic algorithms in a few scenarios.
-
-For comparison, we'll also include qualification results for a few other popular non-cryptographic hash algorithms such as:
+Let's see how the GxHash0 algorithm qualifies in specific scenarios against some well-known non-cryptographic algorithms, such as:
 
@@
 For this reason, the collision rate is expected to be about 2 \(\times\) 0.0116\%.
-We can see however that CRC and XxHash have lower odds of collisions for 4 bytes input, which can be explained by a size-specific logic to handle small inputs bijectively.
+We can see however that CRC and XxHash\cite{xxhash} have lower odds of collisions for 4 bytes input, which can be explained by a size-specific logic to handle small inputs bijectively.
 
@@
 \begin{itemize}
-    \item Leveraging larger SIMD intrinsics, such as Intel AVX-512 or ARM SVE2.
-    \item Using leading zero count intrinsics followed by a C-style fallthrough to process small inputs faster.
+    \item Leverage larger SIMD intrinsics, such as Intel AVX-512 or ARM SVE2.
+    \item Use leading zero count intrinsics followed by a C-style fallthrough to process small inputs faster.
     \item Rewrite the algorithm in assembly code or a language that is more explicit about registers.
@@
     \item Fine-tune the finalization stage to find the perfect balance between performance and avalanche effect.
+    \item Run GxHash0 against more quality benchmarks, such as SMHasher\cite{smhasher}.
 \end{itemize}

### 2023-10-13 c/gxhash.c
Add C implementation

@@ -1,0 +1,136 @@
+#include <stdint.h>
+#include <arm_neon.h>
+#include "gxhash.h"
+
+typedef int8x16_t state;
+
+union ReinterpretUnion {
+    int64x2_t int64;
+    int32x4_t int32;
+    uint32x4_t uint32;
+    int8x16_t int8;
+    uint8x16_t uint8;
+};
+
+static inline state create_empty() {
+    return vdupq_n_s8(0);
+}
+
+static inline void prefetch(const state* p) {
+    // __pld(p); // Uncomment if needed
+}
+
+static inline state load_unaligned(const state* p) {
+    return vld1q_s8((const int8_t*)p);
+}
+
+static inline state get_partial(const state* p, int len) {
+    static const int8_t MASK[32] = {
+        0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF,
+        0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00
+    };
+    int8x16_t mask = vld1q_s8(&MASK[16 - len]);
+    return vandq_s8(load_unaligned(p), mask);
+}
+
+static inline uint8x16_t aes_encrypt(uint8x16_t data, uint8x16_t keys) {
+    uint8x16_t encrypted = vaeseq_u8(data, vdupq_n_u8(0));
+    uint8x16_t mixed = vaesmcq_u8(encrypted);
+    return veorq_u8(mixed, keys);
+}
+
+static inline uint8x16_t aes_encrypt_last(uint8x16_t data, uint8x16_t keys) {
+    uint8x16_t encrypted = vaeseq_u8(data, vdupq_n_u8(0));
+    return veorq_u8(encrypted, keys);
+}
+
+static inline state compress(state a, state b) {
+    union ReinterpretUnion au = { .int8 = a };
+    union ReinterpretUnion bu = { .int8 = b };
+    union ReinterpretUnion result = { .uint8 = aes_encrypt_last(au.uint8, bu.uint8) };
+    return result.int8;
+}
+
+static inline uint64_t finalize(state hash) {
[…]

### 2023-10-13 c/gxhash.h

@@ -1,0 +1,9 @@
+#ifndef GXHASH_H
+#define GXHASH_H
+
+#include <stdint.h>
+
+// Function prototype for gxhash
+uint64_t gxhash(const uint8_t* input, int len);
+
+#endif // GXHASH_H

### 2023-10-13 src/gxhash.rs
Prevent right padded zeros from triggering collisions

@@ -37,7 +37,12 @@ mod platform_defs {
             0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00 ];
 
         let mask = vld1q_s8((MASK.as_ptr() as *const i8).offset(size_of::<state>() as isize - len));
-        vandq_s8(load_unaligned(p), mask)
+        let mut vec = vandq_s8(load_unaligned(p), mask);
+
+        // To avoid collisions for zero right padded inputs, we mutate this vector using its used length
+        vec = vaddq_s8(vec, vdupq_n_s8(len as i8));
+
+        return vec;
     }
 
     #[inline]
@@ -256,6 +261,7 @@ pub fn gxhash(input: &[u8]) -> u32 {
 mod tests {
 
     use super::*;
+    use rand::Rng;
 
     #[test]
     fn all_blocks_are_consumed() {
@@ -270,6 +276,22 @@ mod tests {
             bytes[i] = swap;
 
             assert_ne!(ref_hash, new_hash, "byte {i} not processed");
+        }
+    }
+
+    #[test]
+    fn add_zeroes_mutates_hash() {
+        let mut bytes = [0u8; 1200];
+
+        let mut rng = rand::thread_rng();
+        rng.fill(&mut bytes[..32]);
+
+        let mut ref_hash = 0;
+
+        for i in 32..100 {
+            let new_hash = gxhash(&mut bytes[..i]);
+            assert_ne!(ref_hash, new_hash, "Same hash at size {i} ({new_hash})");
+            ref_hash = new_hash;
         }
     }
 

### 2023-11-04 src/gxhash/platform/arm_128.rs
Format throughput as CSV and inject seed as add

@@ -110,7 +110,8 @@ pub unsafe fn finalize(hash: state, seed: i32) -> state {
 
     // 3 rounds of AES
     let mut hash = ReinterpretUnion{ int8: hash }.uint8;
-    hash = aes_encrypt(hash, ReinterpretUnion{ int32: vdupq_n_s32(seed) }.uint8);
+    //hash = aes_encrypt(hash, ReinterpretUnion{ int32: vdupq_n_s32(seed) }.uint8);
+    hash = vaddq_u8(hash, ReinterpretUnion{ int32: vdupq_n_s32(seed) }.uint8);
     hash = aes_encrypt(hash, ReinterpretUnion{ uint32: keys_1 }.uint8);
     hash = aes_encrypt(hash, ReinterpretUnion{ uint32: keys_2 }.uint8);
     hash = aes_encrypt_last(hash, ReinterpretUnion{ uint32: keys_3 }.uint8);

### 2023-11-04 benches/throughput2.rs
Remove warnings and try out different order for 8 by 8 compression

@@ -13,7 +13,7 @@ fn main() {
 }
 
 #[inline(never)]
-fn noop(data: &[u8], seed: i32) -> u64 {
+fn noop(_: &[u8], seed: i32) -> u64 {
     return seed as u64;
 }
 
@@ -21,8 +21,8 @@ fn benchmark<F>(data: &[u8], name: &str, delegate: F)
     where F: Fn(&[u8], i32) -> u64
 {
     print!("{}, ", name);
-    for i in 1.. {
-        let len = usize::pow(4, i);
+    for i in 2.. {
+        let len = usize::pow(2, i);
         if len > data.len() {
             break;
         }  
@@ -59,8 +59,8 @@ fn time<F>(len: usize, data: &[u8], delegate: &F) -> f64
     let iterations = isize::max(100_000 - len as isize, 100);
 
     let now = Instant::now();
-    for j in 0..iterations {   
-        let slice_start: usize = (seed & 0xFF) as usize;
+    for _ in 0..iterations {   
+        let slice_start: usize = (seed & 1) as usize;
         let slice_end = slice_start + len;
         let slice = &data[slice_start..slice_end];
         let hash = black_box(noop(slice, seed));
@@ -69,8 +69,8 @@ fn time<F>(len: usize, data: &[u8], delegate: &F) -> f64
     let overhead = now.elapsed().as_nanos();
     
     let now = Instant::now();
-    for j in 0..iterations {   
-        let slice_start: usize = (seed & 0xFF) as usize;
+    for _ in 0..iterations {   
+        let slice_start: usize = (seed & 1) as usize;
         let slice_end = slice_start + len;
         let slice = &data[slice_start..slice_end];
         let hash = black_box(delegate(slice, seed));
@@ -90,6 +90,16 @@ fn benchmark_all() {
 
     // Fill with random bytes
     rng.fill(slice);
+
+    print!("Input size (bytes), ");
+    for i in 2.. {
+        let len = usize::pow(2, i);
+        if len > slice.len() {
+            break;
+        }  
+        print!("{}, ", len); 
+    }
+    println!();
 
     // GxHash
     let algo_name = if cfg!(feature = "avx2") { "gxhash-avx2" } else { "gxhash" };

### 2023-11-04 src/gxhash/mod.rs

@@ -5,7 +5,7 @@ use platform::*;
 #[inline(always)]
 pub fn gxhash32(input: &[u8], seed: i32) -> u32 {
     unsafe {
-        let p = &gxhash(input, seed) as *const state as *const u32;
+        let p = &gxhash(input, seed) as *const State as *const u32;
         *p
     }
 }
@@ -13,7 +13,7 @@ pub fn gxhash32(input: &[u8], seed: i32) -> u32 {
 #[inline(always)]
 pub fn gxhash64(input: &[u8], seed: i32) -> u64 {
     unsafe {
-        let p = &gxhash(input, seed) as *const state as *const u64;
+        let p = &gxhash(input, seed) as *const State as *const u64;
         *p
     }
 }
@@ -28,7 +28,7 @@ macro_rules! load_unaligned {
     };
 }
 
-const VECTOR_SIZE: isize = std::mem::size_of::<state>() as isize;
+const VECTOR_SIZE: isize = std::mem::size_of::<State>() as isize;
 
 const RANGE_1_BEGIN: isize  = VECTOR_SIZE + 1;
 const RANGE_1_END: isize    = VECTOR_SIZE * 2;
@@ -38,10 +38,10 @@ const RANGE_3_BEGIN: isize  = RANGE_2_BEGIN + 1;
 const RANGE_3_END: isize    = VECTOR_SIZE * 4;
 
 #[inline(always)]
-unsafe fn gxhash(input: &[u8], seed: i32) -> state {
+unsafe fn gxhash(input: &[u8], seed: i32) -> State {
 
     let len: isize = input.len() as isize;
-    let mut ptr = input.as_ptr() as *const state;
+    let mut ptr = input.as_ptr() as *const State;
 
     let (mut hash_vector, remaining_bytes, p) = match len {
         // Fast path with no compression for payloads that fit in a single state
@@ -73,7 +73,7 @@ unsafe fn gxhash(input: &[u8], seed: i32) -> state {
 }
 
 #[inline(always)]
-unsafe fn gxhash_process_8(mut ptr: *const state, hash_vector: state, remaining_bytes: isize) -> (state, isize, *const state) {
+unsafe fn gxhash_process_8(mut ptr: *const State, hash_vector: State, remaining_bytes: isize) -> (State, isize, *const State) {
 
     const UNROLL_FACTOR: isize = 8;
 
@@ -84,16 +84,24 @@ unsafe fn gxhash_process_8(mut ptr: *const state, hash_vector: state, remaining_
[…]

### 2023-11-04 src/gxhash/platform/arm_128.rs
Remove warnings and try out different order for 8 by 8 compression

@@ -1,7 +1,7 @@
 use std::{mem::size_of, intrinsics::likely, thread::sleep, time::Duration};
 use core::arch::aarch64::*;
 
-pub type state = int8x16_t;
+pub type State = int8x16_t;
 
 #[repr(C)]
 union ReinterpretUnion {
@@ -13,23 +13,23 @@ union ReinterpretUnion {
 }
 
 #[inline(always)]
-pub unsafe fn create_empty() -> state {
+pub unsafe fn create_empty() -> State {
     vdupq_n_s8(0)
 }
 
 #[inline(always)]
-pub unsafe fn prefetch(p: *const state) {
+pub unsafe fn prefetch(p: *const State) {
     //__pld(p as *const i8);
 }
 
 #[inline(always)]
-pub unsafe fn load_unaligned(p: *const state) -> state {
+pub unsafe fn load_unaligned(p: *const State) -> State {
     vld1q_s8(p as *const i8)
 }
 
 #[inline(always)]
-pub unsafe fn get_partial(p: *const state, len: isize) -> state {
-    let partial_vector: state;
+pub unsafe fn get_partial(p: *const State, len: isize) -> State {
+    let partial_vector: State;
     if likely(check_same_page(p)) {
         // Unsafe (hence the check) but much faster
         let indices = vld1q_s8([0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15].as_ptr());
@@ -46,18 +46,18 @@ pub unsafe fn get_partial(p: *const state, len: isize) -> state {
 const PAGE_SIZE: usize = 0x1000;
 
 #[inline(always)]
-unsafe fn check_same_page(ptr: *const state) -> bool {
+unsafe fn check_same_page(ptr: *const State) -> bool {
     let address = ptr as usize;
     // Mask to keep only the last 12 bits (3 bytes)
     let offset_within_page = address & PAGE_SIZE;
     // Check if the 16nd byte from the current offset exceeds the page boundary
-    offset_within_page <= PAGE_SIZE - size_of::<state>()
+    offset_within_page <= PAGE_SIZE - size_of::<State>()
 }
 
 #[inline(never)]
-unsafe fn get_partial_safe(data: *const i8, len: usize) -> state {
+unsafe fn get_partial_safe(data: *const i8, len: usize) -> State {
[…]

### 2023-11-04 src/gxhash/platform/x86_128.rs

@@ -1,26 +1,26 @@
 use core::arch::x86_64::*;
 use std::mem::size_of;
 
-pub type state = __m128i;
+pub type State = __m128i;
 
 #[inline]
-pub unsafe fn create_empty() -> state {
+pub unsafe fn create_empty() -> State {
     _mm_setzero_si128()
 }
 
 #[inline]
-pub unsafe fn prefetch(p: *const state) {
+pub unsafe fn prefetch(p: *const State) {
     _mm_prefetch(p as *const i8, 3);
 }
 
 #[inline]
-pub unsafe fn load_unaligned(p: *const state) -> state {
+pub unsafe fn load_unaligned(p: *const State) -> State {
     _mm_loadu_si128(p)
 }
 
 #[inline]
-pub unsafe fn get_partial(p: *const state, len: isize) -> state {
-    let partial_vector: state;
+pub unsafe fn get_partial(p: *const State, len: isize) -> State {
+    let partial_vector: State;
     // Safety check
     if check_same_page(p) {
         let indices = _mm_set_epi8(15, 14, 13, 12, 11, 10, 9, 8, 7, 6, 5, 4, 3, 2, 1, 0);
@@ -37,27 +37,27 @@ pub unsafe fn get_partial(p: *const state, len: isize) -> state {
 const PAGE_SIZE: usize = 0x1000;
 
 #[inline]
-unsafe fn check_same_page(ptr: *const state) -> bool {
+unsafe fn check_same_page(ptr: *const State) -> bool {
     let address = ptr as usize;
     // Mask to keep only the last 12 bits (3 bytes)
     let offset_within_page = address & 0xFFF;
     // Check if the 32nd byte from the current offset exceeds the page boundary
-    offset_within_page <= PAGE_SIZE - size_of::<state>()
+    offset_within_page <= PAGE_SIZE - size_of::<State>()
 }
 
 #[inline]
-unsafe fn get_partial_safe(data: *const u8, len: usize) -> state {
+unsafe fn get_partial_safe(data: *const u8, len: usize) -> State {
     // Temporary buffer filled with zeros
-    let mut buffer = [0u8; size_of::<state>()];
+    let mut buffer = [0u8; size_of::<State>()];
     // Copy data into the buffer
     std::ptr::copy(data, buffer.as_mut_ptr(), len);
[…]

### 2023-11-04 src/gxhash/platform/x86_256.rs

@@ -1,26 +1,26 @@
 use core::arch::x86_64::*;
 use std::mem::size_of;
 
-pub type state = __m256i;
+pub type State = __m256i;
 
 #[inline]
-pub unsafe fn create_empty() -> state {
+pub unsafe fn create_empty() -> State {
     _mm256_setzero_si256()
 }
 
 #[inline]
-pub unsafe fn prefetch(p: *const state) {
-    //_mm_prefetch(p as *const i8, 3);
+pub unsafe fn prefetch(p: *const State) {
+    _mm_prefetch(p as *const i8, 3);
 }
 
 #[inline]
-pub unsafe fn load_unaligned(p: *const state) -> state {
+pub unsafe fn load_unaligned(p: *const State) -> State {
     _mm256_loadu_si256(p)
 }
 
 #[inline]
-pub unsafe fn get_partial(p: *const state, len: isize) -> state {
-    let partial_vector: state;
+pub unsafe fn get_partial(p: *const State, len: isize) -> State {
+    let partial_vector: State;
     // Safety check
     if check_same_page(p) {
         let indices = _mm256_set_epi8(31, 30, 29, 28, 27, 26, 25, 24, 23, 22, 21, 20, 19, 18, 17, 16, 15, 14, 13, 12, 11, 10, 9, 8, 7, 6, 5, 4, 3, 2, 1, 0);
@@ -37,27 +37,27 @@ pub unsafe fn get_partial(p: *const state, len: isize) -> state {
 const PAGE_SIZE: usize = 0x1000;
 
 #[inline]
-unsafe fn check_same_page(ptr: *const state) -> bool {
+unsafe fn check_same_page(ptr: *const State) -> bool {
     let address = ptr as usize;
     // Mask to keep only the last 12 bits (3 bytes)
     let offset_within_page = address & 0xFFF;
     // Check if the 32nd byte from the current offset exceeds the page boundary
-    offset_within_page <= PAGE_SIZE - size_of::<state>()
+    offset_within_page <= PAGE_SIZE - size_of::<State>()
 }
 
 #[inline]
-unsafe fn get_partial_safe(data: *const u8, len: usize) -> state {
+unsafe fn get_partial_safe(data: *const u8, len: usize) -> State {
[…]

### 2023-11-04 benches/throughput2.rs
Improve benchmark (close to criterion results)

@@ -1,5 +1,5 @@
 use std::hint::black_box;
-use std::time::Instant;
+use std::time::{Instant, Duration};
 use std::alloc::{alloc, dealloc, Layout};
 use std::slice;
 
@@ -8,79 +8,11 @@ use rand::Rng;
 use gxhash::*;
 mod fnv;
 
+const ITERATIONS: u32 = 1000;
+const MAX_RUN_DURATION: Duration = Duration::from_millis(500);
+const FORCE_NO_INLINING: bool = false;
+
 fn main() {
-    benchmark_all();
-}
-
-#[inline(never)]
-fn noop(_: &[u8], seed: i32) -> u64 {
-    return seed as u64;
-}
-
-fn benchmark<F>(data: &[u8], name: &str, delegate: F)
-    where F: Fn(&[u8], i32) -> u64
-{
-    print!("{}, ", name);
-    for i in 2.. {
-        let len = usize::pow(2, i);
-        if len > data.len() {
-            break;
-        }  
-
-        // Warmup
-        black_box( time(len, data, &delegate)); 
-
-        let mut total_time: f64 = 0f64;
-        let mut runs: usize = 0;
-        let now = Instant::now();
-        while runs == 0 || now.elapsed().as_millis() < 500 {
-            let time = time(len, data, &delegate);
-            if time < 0.1f64 {
-                // Invalid timing, ignore
-                continue;
-            }
-            total_time += time;
-            runs += 1;
-        }
-        let average_time = total_time / (runs as f64);
-        let throughput = (len as f64) / (0.00_000_0001f64 * 1024f64 * 1024f64 * average_time);
-
-        //println!("{}/{}\t\t{:.0} MiB/s", name, len, throughput);
-        print!("{:.2}, ", throughput); 
-    }
-    println!();
-}
-
-#[inline(never)]
-fn time<F>(len: usize, data: &[u8], delegate: &F) -> f64
-    where F: Fn(&[u8], i32) -> u64 {
-
-    let mut seed: i32 = 0;
-    let iterations = isize::max(100_000 - len as isize, 100);
-
-    let now = Instant::now();
-    for _ in 0..iterations {   
-        let slice_start: usize = (seed & 1) as usize;
-        let slice_end = slice_start + len;
-        let slice = &data[slice_start..slice_end];
-        let hash = black_box(noop(slice, seed));
-        seed = hash as i32;
-    }
-    let overhead = now.elapsed().as_nanos();
-    
-    let now = Instant::now();
-    for _ in 0..iterations {   
[…]

### 2023-11-04 src/gxhash/mod.rs

@@ -84,24 +84,24 @@ unsafe fn gxhash_process_8(mut ptr: *const State, hash_vector: State, remaining_
         
         load_unaligned!(ptr, v0, v1, v2, v3, v4, v5, v6, v7);
 
-        // let mut tmp: state;
-        // tmp = compress_fast(v0, v1);
-        // tmp = compress_fast(tmp, v2);
-        // tmp = compress_fast(tmp, v3);
-        // tmp = compress_fast(tmp, v4);
-        // tmp = compress_fast(tmp, v5);
-        // tmp = compress_fast(tmp, v6);
-        // tmp = compress_fast(tmp, v7);
+        let mut tmp: State;
+        tmp = compress_fast(v0, v1);
+        tmp = compress_fast(tmp, v2);
+        tmp = compress_fast(tmp, v3);
+        tmp = compress_fast(tmp, v4);
+        tmp = compress_fast(tmp, v5);
+        tmp = compress_fast(tmp, v6);
+        tmp = compress_fast(tmp, v7);
 
-        let t1 = compress_fast(v0, v1);
-        let t2 = compress_fast(v2, v3);
-        let t3 = compress_fast(v4, v5);
-        let t4 = compress_fast(v6, v7);
+        // let t1 = compress(v0, v3);
+        // let t2 = compress(v2, v1);
+        // let t3 = compress(v4, v7);
+        // let t4 = compress(v6, v5);
 
-        let t5 = compress_fast(t1, t2);
-        let t6 = compress_fast(t3, t4);
+        // let t5 = compress_fast(t1, t3);
+        // let t6 = compress_fast(t2, t4);
         
-        let tmp = compress_fast(t5, t6);
+        // let tmp = compress_fast(t6, t5);
 
         hash_vector = compress(hash_vector, tmp);
     }

### 2023-11-04 src/gxhash/platform/arm_128.rs
Add seed instead of AES-ing it

@@ -1,4 +1,4 @@
-use std::{mem::size_of, intrinsics::likely, thread::sleep, time::Duration};
+use std::{mem::size_of, intrinsics::likely};
 use core::arch::aarch64::*;
 
 pub type State = int8x16_t;

### 2023-11-04 src/gxhash/platform/x86_128.rs
Add seed instead of AES-ing it

@@ -82,7 +82,8 @@ pub unsafe fn finalize(hash: State, seed: i32) -> State {
     let keys_3 = _mm_set_epi32(0xC78B122B, 0x5544B1B7, 0x689D2B7D, 0xD0012E32);
 
     // 4 rounds of AES
-    let mut hash = _mm_aesenc_si128(hash, _mm_set1_epi32(seed));
+    //let mut hash = _mm_aesenc_si128(hash, _mm_set1_epi32(seed));
+    let mut hash = _mm_add_epi8(hash, _mm_set1_epi32(seed));
     hash = _mm_aesenc_si128(hash, keys_1);
     hash = _mm_aesenc_si128(hash, keys_2);
     hash = _mm_aesenclast_si128(hash, keys_3);

### 2023-11-04 src/gxhash/platform/x86_256.rs
Add seed instead of AES-ing it

@@ -82,6 +82,7 @@ pub unsafe fn finalize(hash: State, seed: i32) -> State {
     let keys_3 = _mm256_set_epi32(0xC78B122B, 0x5544B1B7, 0x689D2B7D, 0xD0012E32, 0xE2784542, 0x4155EE07, 0xC897CCE2, 0x780BF2C2);
 
     // 4 rounds of AES
+    //let mut hash = _mm256_aesenc_epi128(hash, _mm256_set1_epi32(seed));
     let mut hash = _mm256_add_epi8(hash, _mm256_set1_epi32(seed));
     hash = _mm256_aesenc_epi128(hash, keys_1);
     hash = _mm256_aesenc_epi128(hash, keys_2);

### 2023-11-04 benches/throughput/result_processor.rs
Add csv and markdown exports in benchmarks

@@ -1,0 +1,88 @@
+#[cfg(feature = "bench-csv")]
+#[derive(Default)]
+pub struct ResultProcessor {
+    header_written: bool,
+    row_data: Vec<String>,
+    header_data: Vec<String>,
+}
+
+#[cfg(feature = "bench-csv")]
+impl ResultProcessor {
+    pub fn on_start(&mut self, name: &str) {
+        self.row_data.push(name.to_string());
+        if !self.header_written {
+            self.header_data.push("Throughput (MiB/s)".to_string());
+        }
+    }
+
+    pub fn on_result(&mut self, input_size: usize, throughput: f64) {
+        self.row_data.push(format!("{:.2}", throughput));
+        if !self.header_written {
+            self.header_data.push(input_size.to_string());
+        }
+    }
+
+    pub fn on_end(&mut self) {
+        if !self.header_written {
+            println!("{}", self.header_data.join(", "));
+            self.header_written = true;
+        }
+        println!("{}", self.row_data.join(", "));
+        self.row_data.clear();
+    }
+}
+
+#[cfg(feature = "bench-md")]
+#[derive(Default)]
+pub struct ResultProcessor {
+    header_written: bool,
+    row_data: Vec<String>,
+    header_data: Vec<String>,
+}
+
+#[cfg(feature = "bench-md")]
+impl ResultProcessor {
+    pub fn on_start(&mut self, name: &str) {
+        self.row_data.push(name.to_string());
+        if !self.header_written {
+            self.header_data.push("Throughput (MiB/s)".to_string());
+        }
+    }
+
+    pub fn on_result(&mut self, input_size: usize, throughput: f64) {
+        self.row_data.push(format!("{:.2}", throughput));
+        if !self.header_written {
+            self.header_data.push(input_size.to_string());
+        }
+    }
+
+    pub fn on_end(&mut self) {
+        if !self.header_written {
+            println!("| {} |", self.header_data.join(" | "));
+            let separator: Vec<String> = self.header_data.iter().map(|_| "---".to_string()).collect();
+            println!("|{}|", separator.join("|"));
+            self.header_written = true;
+        }
+        println!("| {} |", self.row_data.join(" | "));
+        self.row_data.clear();
+    }
+}
+
+#[cfg(all(not(feature = "bench-csv"),not(feature = "bench-md")))]
+#[derive(Default)]
+pub struct ResultProcessor;
+
[…]

### 2023-11-04 src/gxhash/platform/arm_128.rs

@@ -110,8 +110,7 @@ pub unsafe fn finalize(hash: State, seed: i32) -> State {
 
     // 3 rounds of AES
     let mut hash = ReinterpretUnion{ int8: hash }.uint8;
-    //hash = aes_encrypt(hash, ReinterpretUnion{ int32: vdupq_n_s32(seed) }.uint8);
-    hash = vaddq_u8(hash, ReinterpretUnion{ int32: vdupq_n_s32(seed) }.uint8);
+    hash = aes_encrypt(hash, ReinterpretUnion{ int32: vdupq_n_s32(seed) }.uint8);
     hash = aes_encrypt(hash, ReinterpretUnion{ uint32: keys_1 }.uint8);
     hash = aes_encrypt(hash, ReinterpretUnion{ uint32: keys_2 }.uint8);
     hash = aes_encrypt_last(hash, ReinterpretUnion{ uint32: keys_3 }.uint8);

### 2023-11-04 src/gxhash/platform/x86_128.rs

@@ -82,8 +82,7 @@ pub unsafe fn finalize(hash: State, seed: i32) -> State {
     let keys_3 = _mm_set_epi32(0xC78B122B, 0x5544B1B7, 0x689D2B7D, 0xD0012E32);
 
     // 4 rounds of AES
-    //let mut hash = _mm_aesenc_si128(hash, _mm_set1_epi32(seed));
-    let mut hash = _mm_add_epi8(hash, _mm_set1_epi32(seed));
+    let mut hash = _mm_aesenc_si128(hash, _mm_set1_epi32(seed));
     hash = _mm_aesenc_si128(hash, keys_1);
     hash = _mm_aesenc_si128(hash, keys_2);
     hash = _mm_aesenclast_si128(hash, keys_3);

### 2023-11-04 benches/throughput/main.rs
Add csv and markdown exports in benchmarks

@@ -1,3 +1,9 @@
+include!("../fnv.rs");
+
+mod result_processor;
+
+use result_processor::*;
+
 use std::hint::black_box;
 use std::time::{Instant, Duration};
 use std::alloc::{alloc, dealloc, Layout};
@@ -6,7 +12,6 @@ use std::slice;
 use rand::Rng;
 
 use gxhash::*;
-mod fnv;
 
 const ITERATIONS: u32 = 1000;
 const MAX_RUN_DURATION: Duration = Duration::from_millis(500);
@@ -23,57 +28,49 @@ fn main() {
     // Fill with random bytes
     rng.fill(slice);
 
-    print!("Input size (bytes), ");
-    for i in 2.. {
-        let len = usize::pow(2, i);
-        if len > slice.len() {
-            break;
-        }  
-        print!("{}, ", len); 
-    }
-    println!();
+    let mut processor = ResultProcessor::default();
 
     // GxHash
     let algo_name = if cfg!(feature = "avx2") { "gxhash-avx2" } else { "gxhash" };
-    benchmark(slice, algo_name, |data: &[u8], seed: i32| -> u64 {
+    benchmark(&mut processor, slice, algo_name, |data: &[u8], seed: i32| -> u64 {
         gxhash64(data, seed)
     });
     
     // AHash
     let ahash_hasher = ahash::RandomState::with_seeds(0, 0, 0, 0);
-    benchmark(slice, "ahash", |data: &[u8], _: i32| -> u64 {
+    benchmark(&mut processor, slice, "ahash", |data: &[u8], _: i32| -> u64 {
         ahash_hasher.hash_one(data)
     });
 
     // T1ha0
-    benchmark(slice, "t1ha0", |data: &[u8], seed: i32| -> u64 {
+    benchmark(&mut processor, slice, "t1ha0", |data: &[u8], seed: i32| -> u64 {
         t1ha::t1ha0(data, seed as u64)
     });
 
     // XxHash (twox-hash)
-    benchmark(slice, "xxhash", |data: &[u8], seed: i32| -> u64 {
+    benchmark(&mut processor, slice, "xxhash", |data: &[u8], seed: i32| -> u64 {
         twox_hash::xxh3::hash64_with_seed(data, seed as u64)
     });
 
     // HighwayHash
-    benchmark(slice, "highwayhash", |data: &[u8], _: i32| -> u64 {
[…]

### 2023-11-04 src/gxhash/platform/x86_256.rs

@@ -82,8 +82,7 @@ pub unsafe fn finalize(hash: State, seed: i32) -> State {
     let keys_3 = _mm256_set_epi32(0xC78B122B, 0x5544B1B7, 0x689D2B7D, 0xD0012E32, 0xE2784542, 0x4155EE07, 0xC897CCE2, 0x780BF2C2);
 
     // 4 rounds of AES
-    //let mut hash = _mm256_aesenc_epi128(hash, _mm256_set1_epi32(seed));
-    let mut hash = _mm256_add_epi8(hash, _mm256_set1_epi32(seed));
+    let mut hash = _mm256_aesenc_epi128(hash, _mm256_set1_epi32(seed));
     hash = _mm256_aesenc_epi128(hash, keys_1);
     hash = _mm256_aesenc_epi128(hash, keys_2);
     hash = _mm256_aesenclast_epi128(hash, keys_3);

### 2023-11-04 benches/throughput/main.rs
Add fnv, seahash and metrohash to benchmarks

@@ -1,5 +1,3 @@
-include!("../fnv.rs");
-
 mod result_processor;
 
 use result_processor::*;
@@ -8,6 +6,7 @@ use std::hint::black_box;
 use std::time::{Instant, Duration};
 use std::alloc::{alloc, dealloc, Layout};
 use std::slice;
+use std::hash::Hasher;
 
 use rand::Rng;
 
@@ -35,6 +34,11 @@ fn main() {
     benchmark(&mut processor, slice, algo_name, |data: &[u8], seed: i32| -> u64 {
         gxhash64(data, seed)
     });
+
+    // XxHash (twox-hash)
+    benchmark(&mut processor, slice, "xxhash", |data: &[u8], seed: i32| -> u64 {
+        twox_hash::xxh3::hash64_with_seed(data, seed as u64)
+    });
     
     // AHash
     let ahash_hasher = ahash::RandomState::with_seeds(0, 0, 0, 0);
@@ -47,9 +51,16 @@ fn main() {
         t1ha::t1ha0(data, seed as u64)
     });
 
-    // XxHash (twox-hash)
-    benchmark(&mut processor, slice, "xxhash", |data: &[u8], seed: i32| -> u64 {
-        twox_hash::xxh3::hash64_with_seed(data, seed as u64)
+    // SeaHash
+    benchmark(&mut processor, slice, "seahash", |data: &[u8], seed: i32| -> u64 {
+        seahash::hash_seeded(data, seed as u64, 0, 0, 0)
+    });
+
+    // MetroHash
+    benchmark(&mut processor, slice, "metrohash", |data: &[u8], seed: i32| -> u64 {
+        let mut metrohash_hasher = metrohash::MetroHash64::with_seed(seed as u64);
+        metrohash_hasher.write(data);
+        metrohash_hasher.finish()
     });
 
     // HighwayHash
@@ -60,7 +71,9 @@ fn main() {
 
     // FNV-1a
     benchmark(&mut processor, slice, "fnv-1a", |data: &[u8], seed: i32| -> u64 {
-        fnv_hash(data, seed as u64)
+        let mut fnv_hasher = fnv::FnvHasher::with_key(seed as u64);
+        fnv_hasher.write(data);
+        fnv_hasher.finish()
     });
 
     // Free benchmark data

### 2023-11-04 benches/throughput_criterion.rs

@@ -1,13 +1,13 @@
 use std::time::Duration;
 use std::alloc::{alloc, dealloc, Layout};
 use std::slice;
+use std::hash::Hasher;
 
 use criterion::measurement::WallTime;
 use criterion::{criterion_group, criterion_main, Criterion, Throughput, PlotConfiguration, AxisScale, BenchmarkGroup, BenchmarkId};
 use rand::Rng;
 
 use gxhash::*;
-mod fnv;
 
 fn benchmark<F>(c: &mut BenchmarkGroup<WallTime>, data: &[u8], name: &str, delegate: F)
     where F: Fn(&[u8], i32) -> u64
@@ -73,7 +73,9 @@ fn benchmark_all(c: &mut Criterion) {
 
     // FNV-1a
     benchmark(&mut group, slice, "fnv-1a", |data: &[u8], seed: i32| -> u64 {
-        fnv::fnv_hash(data, seed as u64)
+        let mut fnv_hasher = fnv::FnvHasher::with_key(seed as u64);
+        fnv_hasher.write(data);
+        fnv_hasher.finish()
     });
 
     group.finish();

### 2023-11-04 benches/fnv.rs
Add fnv, seahash and metrohash to benchmarks

@@ -1,14 +1,0 @@
-const INITIAL_STATE: u64 = 0xcbf29ce484222325;
-const PRIME: u64 = 0x100000001b3;
-
-#[inline]
-pub const fn fnv_hash(bytes: &[u8], seed: u64) -> u64 {
-    let mut hash = seed + INITIAL_STATE;
-    let mut i = 0;
-    while i < bytes.len() {
-        hash = hash ^ (bytes[i] as u64);
-        hash = hash.wrapping_mul(PRIME);
-        i += 1;
-    }
-    hash
-}

### 2023-11-04 src/gxhash/mod.rs

@@ -93,16 +93,6 @@ unsafe fn gxhash_process_8(mut ptr: *const State, hash_vector: State, remaining_
         tmp = compress_fast(tmp, v6);
         tmp = compress_fast(tmp, v7);
 
-        // let t1 = compress(v0, v3);
-        // let t2 = compress(v2, v1);
-        // let t3 = compress(v4, v7);
-        // let t4 = compress(v6, v5);
-
-        // let t5 = compress_fast(t1, t3);
-        // let t6 = compress_fast(t2, t4);
-        
-        // let tmp = compress_fast(t6, t5);
-
         hash_vector = compress(hash_vector, tmp);
     }
 
@@ -248,5 +238,14 @@ mod tests {
         assert_ne!(0, gxhash32(&[0u8; 0], 0));
         assert_ne!(0, gxhash32(&[0u8; 1], 0));
         assert_ne!(0, gxhash32(&[0u8; 1200], 0));
+    }
+
+    // GxHash with a 128-bit state must be stable despite the different endianesses / CPU instrinsics
+    #[cfg(not(feature = "avx2"))]
+    #[test]
+    fn is_stable() {
+        assert_eq!(456576800, gxhash32(&[0u8; 0], 0));
+        assert_eq!(978957914, gxhash32(&[0u8; 1], 0));
+        assert_eq!(3128839713, gxhash32(&[42u8; 1000], 1234));
     }
 }

### 2023-11-04 src/gxhash/platform/arm_128.rs
Remove unecessary prefetching

@@ -18,11 +18,6 @@ pub unsafe fn create_empty() -> State {
 }
 
 #[inline(always)]
-pub unsafe fn prefetch(p: *const State) {
-    //__pld(p as *const i8);
-}
-
-#[inline(always)]
 pub unsafe fn load_unaligned(p: *const State) -> State {
     vld1q_s8(p as *const i8)
 }

### 2023-11-04 src/gxhash/platform/x86_128.rs

@@ -9,11 +9,6 @@ pub unsafe fn create_empty() -> State {
 }
 
 #[inline]
-pub unsafe fn prefetch(p: *const State) {
-    _mm_prefetch(p as *const i8, 3);
-}
-
-#[inline]
 pub unsafe fn load_unaligned(p: *const State) -> State {
     _mm_loadu_si128(p)
 }

### 2023-11-04 src/gxhash/platform/x86_256.rs
Remove unecessary prefetching

@@ -9,11 +9,6 @@ pub unsafe fn create_empty() -> State {
 }
 
 #[inline]
-pub unsafe fn prefetch(p: *const State) {
-    _mm_prefetch(p as *const i8, 3);
-}
-
-#[inline]
 pub unsafe fn load_unaligned(p: *const State) -> State {
     _mm256_loadu_si256(p)
 }

### 2023-11-04 article/article.tex
Update article benchmarks

@@
 
-In the next sections, we'll delve into the specific operations and transformations chosen for the compression and finalization functions of the \textbf{GxHash-0} (version 0) algorithm.
+In the next sections, we'll delve into the specific operations and transformations chosen for the compression and finalization functions of the \textbf{GxHash} algorithm (version 1.0.0).
 
@@
 
-In practice, the \textbf{GxHash-0} uses a combination of SIMD 8-bit wrapping add and state-wide circular shift of one.
+TODO
+In practice, the \textbf{GxHash} uses the AES block cipher intrinsics to combines two 128-bit SIMD vectors together combination of SIMD 8-bit wrapping add and state-wide circular shift of one.
 The addition is a simple way to mix the state with the next message block bits, while providing an arithmetic carry which helps in regard to distribution (as opposed to a XOR for instance).
@@
 \end{itemize}
-
-While mathematically collisions are inevitable due to the inherent non-bijectivity, odds of collisions using the GxHash-0 compression remain statically low given the uniformity of distribution, although those collisions are predictable due to the inherent simplicity of the function.
 
@@
 \end{multicols}
-\caption{GxHash-0 Compression in Rust}
+\caption{GxHash Compression in Rust}
 \label{fig:compression_rust_example}
@@
 
-The finalization process in the GxHash-0 algorithm is crucial to ensure the transformation of its internal state into a fixed-size, uniformly distributed hash output.
+The finalization process in the GxHash algorithm is crucial to ensure the transformation of its internal state into a fixed-size, uniformly distributed hash output.
 This process is delineated into two primary steps: mixing the bits and reducing to the desired hash size.
@@
 This mixing step is responsible for ensuring the even distribution of bits in the state, thereby reducing patterns or biases that might arise from the input data or the compression process.
-Given the inherent simplicity of the GxHash-0 compression, it is worth for the finalization to incorporate slightly more intricate bit mixing operations, especially given it runs only once per message hashed, as opposed to the compression that occurs once for each block.\\
+Given the inherent simplicity of the GxHash compression, it is worth for the finalization to incorporate slightly more intricate bit mixing operations, especially given it runs only once per message hashed, as opposed to the compression that occurs once for each block.\\
 Leveraging SIMD capabilities can help in regard to performance and efficiency, which remains for us a primary consideration.
@@
 There are several approaches to this, one being combiniting the \( X \)-bit integer parts of the mixed state together (by xoring them together for instance).
-GxHash0 takes a simpler path by reinterpreting our state into a smaller \( X \)-bit value, assuming an uniform distribution at the mixing stage thanks to the 3 rounds of AES.
-This allow the GxHash0 algorithm to generate hashes of any size up to \( s_b \) bits with virtually no additional computational cost.
+GxHash takes a simpler path by reinterpreting our state into a smaller \( X \)-bit value, assuming an uniform distribution at the mixing stage thanks to the 3 rounds of AES.
+This allow the GxHash algorithm to generate hashes of any size up to \( s_b \) bits with virtually no additional computational cost.
 
@@
 
-Benchmarks conducted show a less than 20\% performance degradation on both our x86 and ARM hardware when using the second solution. This is the chosen solution for GxHash-0.
+Benchmarks conducted show a less than 20\% performance degradation on both our x86 and ARM hardware when using the second solution.
+For simplicity, GxHash treats aligned and unaligned data the same way.
 
@@
 While the looping semantics will vary from one language to another, any overhead from looping over the input message blocks is likely to directly affect the overall throughput of the algorithm, given how optimized the rest of the algorithm is meant to be.
-In some cases, compilers might do a great job at generating loop instructions with minimal overhead, but it isn't the case in the language where GxHash-0 was ported, where looping using pointer arithmetics was needed.
+In some cases, compilers might do a great job at generating loop instructions with minimal overhead, but it isn't the case in the language where GxHash was ported, where looping using pointer arithmetics was needed.
 
 Unrolling the loop is a complementary optimization that diminishes greatly any loop overhead.
-In the case of GxHash, the laned construction implies some kind of unrolling, which is sufficient for achieving the high throughput numbers we see in our benchmarks.
+In the case of GxHash, the temporal construction implies some kind of unrolling, which is sufficient for achieving the high throughput numbers we see in our benchmarks.
 
@@
 The read bytes can then be masked with the help of a sliding mask, transforming the trailing bytes that don't belong to our message into zeros, in a single SIMD operation.
-Compared to the naive method, this solution is up to ten times faster on our test machine (Ryzen 5, x86 64-bit, AVX2).
+Compared to the naive method, this solution is up to ten times faster on our test machine (Ryzen 5, x86 64-bit).
 
@@
 
-unsafe fn read_padded(p: *const __m256i, len: isize) -> __m256i {
-    // The mask array is twice as long as the SIMD registry size (32*2 here), so that
-    // each 32-byte slice accounts for a different number of trailing bytes to mask out
-    const MASK: [u8; 64] = [
-        0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF,
-        0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF,
-        0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00,
-        0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00 ];
-    // Loading the mask slice
-    let mask = _mm256_loadu_epi8((MASK.as_ptr() as *const i8).offset(32 - len));
+unsafe fn read_padded(p: *const __m128i, len: isize) -> __m128i {
+    // Consecuive indices on which we compare the length against, byte per byte, to retreive our mask.
+    // The order is descending or ascending depending on the endianness
+    let indices = _mm_set_epi8(15, 14, 13, 12, 11, 10, 9, 8, 7, 6, 5, 4, 3, 2, 1, 0);
+    // Computing the mask
+    let mask = _mm_cmpgt_epi8(_mm_set1_epi8(len as i8), indices);
     // Read beyond and mask
-    return _mm256_and_si256(_mm256_loadu_si256(p), mask);
+    partial_vector = _mm_and_si128(_mm_loadu_si128(p), mask);
 }
 \end{lstlisting}
-\caption{GxHash-0 Padding in Rust}
+\caption{GxHash Padding in Rust}
 \label{fig:read_beyond_example}
@@
 \begin{lstlisting}[language=Rust, style=boxed]
-unsafe fn is_same_page(ptr: *const __m256i) -> bool {
+unsafe fn is_same_page(ptr: *const __m128i) -> bool {
     // Usual minimal page size on modern computers
@@
     let offset_within_page = address & 0xFFF;
-    // Check if the 32nd byte from the current offset exceeds the page boundary
+    // Check if the 16th byte from the current offset exceeds the page boundary
     offset_within_page <= (PAGE_SIZE - 31)
@@
 While we can compute quality metrics, the result will greatly vary depending on the actual inputs used for our hash function.
-Let's see how the GxHash0 algorithm qualifies in specific scenarios against some well-known non-cryptographic algorithms, such as:
+Let's see how the GxHash algorithm qualifies in specific scenarios against some well-known non-cryptographic algorithms, such as:
 
@@
 \hline
-UInt32 GxHash0(4)            & 0,0241\% & 0,001094  & 0,000002 & 0,00412 \\
-UInt32 GxHash0(64)           & 0,0103\% & 0,001081  & 0,000002 & 0,00296 \\
-UInt32 GxHash0(1000)         & 0,012\%  & 0,001148  & 0,000002 & 0,00336 \\
+UInt32 GxHash(4)            & 0,0241\% & 0,001094  & 0,000002 & 0,00034 \\
+UInt32 GxHash(64)           & 0,0115\% & 0,000795  & 0,000002 & 0,00002 \\
+UInt32 GxHash(1000)         & 0,0108\%  & 0,001007  & 0,000002 & 0,00007 \\
 UInt32 HighwayHash(4)        & 0,0237\% & 0,001135  & 0,000002 & 0,00001 \\
@@
 
-All numbers are very low, and GxHash0 quality results are of the same order of magnitude as for other algorithms.
+All numbers are very low, and GxHash quality results are of the same order of magnitude as for other algorithms.
 Distribution is very good for all algorithms.
 Avalanche is good for most algorithms, except for FNV-1a and CRC.
+We can notice that avalanche score for GxHash is an order of magnitude better than other algorithms for larger input sizes.
 
-We can notice a collision rate of about 0.011\% and even 0.022\% for the 4 bytes inputs. There is an explanation: we can derive from the birthday paradox problem the following formula to
-estimate the \% of collisions:
+We can notice a collision rate of about 0.011\% and even 0.022\% for the 4 bytes inputs.
+There is an explanation: we can derive from the birthday paradox problem the following formula to estimate the \% of collisions:
 
@@
 \hline
-UInt32 GxHash0(4)                & 0,0104\% & 0,000009  & 0,000002 & 0,00308 \\
-UInt32 GxHash0(64)               & 0,0106\% & 0,000009  & 0,0000019 & 0,00225 \\
-UInt32 GxHash0(1000)             & 0,0104\% & 0,000009  & 0,000002 & 0,00283 \\
+UInt32 GxHash(4)                & 0,013\% & 0,001132  & 0,000002 & 0,00044 \\
+UInt32 GxHash(64)               & 0,0112\% & 0,000651  & 0,0000019 & 0,00039 \\
+UInt32 GxHash(1000)             & 0,0126\% & 0,000818  & 0,000002 & 0,00029 \\
 UInt32 HighwayHash(4)            & 0,0117\% & 0,00112   & 0,000002 & 0,00011 \\
@@
 
-Regarding distribution, we can notice that GxHash0 outperforms HighwayHash\cite{highwayhash}, XxHash\cite{xxhash} and T1ha0\cite{rust-t1ha}.
+TODO
+Regarding distribution, we can notice that GxHash outperforms HighwayHash\cite{highwayhash}, XxHash\cite{xxhash} and T1ha0\cite{rust-t1ha}.
 Avalanche is slightly worse, however, possibly due to the tradeoff of doing fewer operations for greater performances.
@@
 It isn't necessarily a bad thing, because a hash function can distribute the hash in a way that the distribution map looks evenly distributed (such as what we observe with CRC with 1000-bytes long inputs), however it implies that values hashes are correlated in a way, which a property we prefer to avoid for a non-cryptographic hash function.
-GxHash0 performs well in that matter, with a distribution that looks as uniform and uncorrelated than its counterparts HighwayHash\cite{highwayhash}, XxHash\cite{xxhash} and T1ha0\cite{rust-t1ha}.
+GxHash performs well in that matter, with a distribution that looks as uniform and uncorrelated than its counterparts HighwayHash\cite{highwayhash}, XxHash\cite{xxhash} and T1ha0\cite{rust-t1ha}.
 
@@
 \hline
-UInt32 GxHash0(64)                & 0,0136\% & 0,001082  & 0,000002 & 0,00319 \\
-UInt32 GxHash0(1000)              & 0,0119\% & 0,000894  & 0,000002 & 0,0034 \\
+UInt32 GxHash(64)                & 0,0108\% & 0,00122  & 0,000002 & 0,00044 \\
+UInt32 GxHash(1000)              & 0,0121\% & 0,001106  & 0,000002 & 0,00035 \\
 UInt32 HighwayHash(64)            & 0,0123\% & 0,000809  & 0,000002 & 0,00048 \\
@@
 The bits distribution is very close for all algorithms benchmarked, at about 0.001.
-The avalanche is a little worse for GxHash0 compared to HighwayHash\cite{highwayhash}, XxHash\cite{xxhash} and T1ha\cite{rust-t1ha}, but remains quite good, and is still higher than Fnv1a and Crc avalanche scores.
+The avalanche score for GxHash is very good, on pair with HighwayHash\cite{highwayhash}, XxHash\cite{xxhash} and T1ha\cite{rust-t1ha}.
 
@@
 
-This was just an overview of the quality of the hashes produced by GxHash0 and a few comparisons to some established non-cryptographic algorithms.
+This was just an overview of the quality of the hashes produced by GxHash and a few comparisons to some established non-cryptographic algorithms.
 
-Our results demonstrate promising quality characteristics of GxHash0 with low collisions, good distribution, and a high avalanche effect, and its quality is comparable to other well-established non-cryptographic algorithms.
+Our results demonstrate promising quality characteristics of GxHash with low collisions, good distribution, and a high avalanche effect, and its quality is comparable to other well-established non-cryptographic algorithms.
 However, it is essential to acknowledge the limitations of the presented evaluation scenarios.
@@
 In real-world applications, the behavior of a hash algorithm can be influenced by a myriad of factors and specific data patterns.
-As such, while our findings provide a foundational understanding of GxHash0's quality, potential users should be cognizant that results may vary based on the actual use case and the nature of the input data.
+As such, while our findings provide a foundational understanding of GxHash's quality, potential users should be cognizant that results may vary based on the actual use case and the nature of the input data.
 
@@
 \includegraphics[width=1\textwidth]{throughput.png}
-\caption{Gibibytes of data hashed per second (throughput) per input size. Log10 scale.}
+\caption{Mibibytes of data hashed per second (throughput) per input size.}
 \label{fig:benchmark-throughput}
@@
 
-The results are compelling: GxHash0 consistently outperforms its counterparts, achieving throughput rates that are an order of magnitude higher in many instances.
-Depending on the input size, we observed performance gains ranging from x5 to an impressive x210.
-On the GCP and Apple M1 Pro benchmarks, the algorithm reaches an impressive 10 Gb/s for 4 bytes inputs, likely showing that the algorithm is memory-bound (and thus can hardly be faster).
-A second observation is a substantial gap in performances between 64 and 256 bytes inputs, which can be explained by the 8-lane processing starting to kick in when inputs are large enough, leveraging ILP for even more throughput.
+The results are compelling: GxHash consistently outperforms its counterparts, achieving throughput rates that are an order of magnitude higher in many instances.
+For almost any input size and on all platforms used for the benchmark, the 128-bit state GxHash was the fastest.
+The 256-bit GxHash reaches almost two times the maximum throughput of the 128-bit GxHash implementation, as excepted.
+We can notice however that it performs slightly worse for inputs of small sizes, which can be explained by the overhead of extracting and xoring the two 128-bit parts of the state.
+Ahash slightly outperforms the 256-bit GxHash for inputs smaller than 128 bytes, but becomes much slower as input size grows.
 
-While these results are promising, it's essential to approach them with a balanced perspective.
-The benchmarks serve as an indicator of GxHash0's potential in specific scenarios, and while the performance advantage is clear, it's always prudent to consider the broader context and the specific requirements of any given application before drawing definitive conclusions.
+\paragraph{A word on inlining}\leavevmode\\
+On the GCP and Apple M1 Pro benchmarks, the algorithm reaches an impressive 11 Gb/s for 8 bytes inputs.
+While some algorithms that are supposed to be heavily optimized for small input sizes such as XxHash, they only reach up to a quarter of that throughput.
+After some analysis, a theory was that assembly code for XxHash was much larger than GxHash, thus preventing the algorithm to be inlined in the benchmark itself.
+After analysis using cargo asm, it turned out that on ARM XxHash produces 10 times as much assembly than GxHash.
+Forcing all methods not to be inlined in the benchmarks tend to prove this theory, as timing for small inputs are now all in the same ballpark.
+Inlining being a important part of the optimization done by compilers is also why special care was taken to make GxHash implementation leading to as little as bytecode as possible.
+Since criterion.rs benchmarking fixture is also leading the GxHash to be inlined, we think those benchmark results are viable and representative of the real world usage.
 
@@
 \subsubsection{Portability}
-As mentioned at the beginning of this paper, portability wasn't a design goal for GxHash-0.
-Consequently, while GxHash-0 can work on different platforms (x86, ARM, and possibly more), it is not recommended to have the hashes outlive the process lifetime, as there is a risk for persistent hashes to imply a hardware dependency afterward, which is something we generally want to avoid.
-We think it is an acceptable limitation when GxHash0 is used at the process scope, such as for hashtables for instance.
-It would be possible however to derive from the GxHash0 implementation presented in this paper to come up with a portable version, but likely at the cost of performance.
+As previously stated, portability between different state sizes was not a design goal for GxHash.
+The algorithm functions across a variety of platforms, such as x86 and ARM, with consistent results within the same state size implementation.
+However, it is important to note that the 128-bit and 256-bit state versions of GxHash will produce distinct hashes for the same input.
+This discrepancy means that hashes generated by one state size are not directly comparable to those generated by another.
+To prevent any potential confusion, it is recommended that users choose one state size and maintain consistency throughout the hashing process, especially when hashes may need to be compared or persisted.
+This limitation is deemed acceptable for use-cases such as in-process hash tables where the state size does not change.
+Developing a version of GxHash that harmonizes the outputs of different state sizes would involve trade-offs, likely affecting the algorithm’s performance or complexity.
 
 \subsubsection{Compiler Dependencies} 
-The Laned Construction presented in this paper is implemented for GxHash0 by declaring each lane with its own variable.
+The Temporal Construction presented in this paper is implemented for GxHash by declaring each lane with its own variable.
 While it worked at the time of writing (rustc 1.68.0), it is in the end the compiler's responsibility to decide how many registers to use.
@@
     \item Leverage larger SIMD intrinsics, such as Intel AVX-512 or ARM SVE2.
-    \item Use leading zero count intrinsics followed by a C-style fallthrough to process small inputs faster.
+    \item Run more quality benchmarks
+    \item Analyze security properties.
     \item Rewrite the algorithm in assembly code or a language that is more explicit about registers.
     \item Introduce more than one stage of laning. For instance 16 lanes, then 8 lanes, then 4 lanes, and finally 2 lanes, to leverage ILP as much as possible.
+    \item Organize processing loop to result in even less bytecode to be generated, favoring inlining opportunities.
     \item Fine-tune the finalization stage to find the perfect balance between performance and avalanche effect.
-    \item Run GxHash0 against more quality benchmarks, such as SMHasher\cite{smhasher}.
 \end{itemize}
@@
 
-By leveraging the capabilities of modern CPUs, such as Single Instruction, Multiple Data (SIMD), GxHash0 achieves unparalleled throughput, setting a new standard for efficiency and performance amongst non-cryptographic hashing algorithms.
-A pivotal innovation in this endeavor is the "Laned Construction," which is specifically designed to harness Instruction-Level Parallelism (ILP), further optimizing the hashing process.
+By leveraging the capabilities of modern CPUs, such as Single Instruction, Multiple Data (SIMD), GxHash achieves unparalleled throughput, setting a new standard for efficiency and performance amongst non-cryptographic hashing algorithms.
+A pivotal innovation in this endeavor is the "Temporal Construction," which is specifically designed to harness Instruction-Level Parallelism (ILP), further optimizing the hashing process.
 
-However, it's essential to note that while GxHash0 offers significant improvements, the behavior of any hash algorithm can be influenced by various factors.
+However, it's essential to note that while GxHash offers significant improvements, the behavior of any hash algorithm can be influenced by various factors.
 As such, potential users should approach with an understanding that results might vary based on specific use cases and input data.\\
 
-The capabilities of GxHash0 represent a significant step forward in non-cryptographic hashing.
+The capabilities of GxHash represent a significant step forward in non-cryptographic hashing.
 In a world where real-time processing is becoming a standard, this algorithm not only enables systems to respond more swiftly but also promotes greater energy efficiency.

### 2023-11-04 article/article.tex
Change laned for temporal construction in benchmarks

@@
 \author{Olivier Giniaux}
-\date{}
+\date{Revision 1 - November 2023}
 
@@
 It also includes timing for the function \texttt{unrolled}, to show that performance increase comes indeed from ILP and not the loop unrolling itself.
-We can see that \texttt{temp} and \texttt{laned} performed equally, leveraging ILP for a significant performance increase over the \texttt{baseline}.
+We can see that \texttt{temporal} and \texttt{laned} performed equally, leveraging ILP for a significant performance increase over the \texttt{baseline}.
 
@@
 \hline
-CPU & \texttt{baseline} & \texttt{unrolled} & \texttt{temp} & \texttt{laned} \\
+CPU & \texttt{baseline} & \texttt{unrolled} & \texttt{temporal} & \texttt{laned} \\
 \hline
@@
 
-While the \texttt{temp} and \texttt{laned} functions won't yield exactly the same hashes as the \texttt{baseline}, they serve the same purpose, while being much faster.
-Both approaches have their pros and cons.
-As the \texttt{laned} explicitly declares \( n \) variables for our lanes, this approach is simpler in regards to compiler analysis and is thus more likely to benefit from ILP, regardless of the compiler or programming language used.
-The following section will delve more in depth into the definition of a \textbf{Laned Construction}.
+While the \texttt{temporal} and \texttt{laned} functions won't yield exactly the same hashes as the \texttt{baseline}, they serve the same purpose, while being much faster.
+Both approaches have their pros and cons. The \texttt{temporal} approach is simpler to implement and will lead to less bytecode generation.
+The following section will delve more in depth into the definition of a \textbf{Temporal Construction}.
 
 \clearpage
-\subsection{The Laned Construction}
+\subsection{The Temporal Construction}
 
-The \textbf{Laned Construction} introduces \( k_b \) lanes, and processes the message by groups of \( k_b \) blocks, so that for a given group each of the \( k_b \) block and be processed on its own lane.
-This way, we have \( k_b \) independent dependency chains.
-The lane hashes can then be compressed altogether thereafter upon exiting the loop.
+The \textbf{Temporal Construction} processes the message by groups of \( k_b \) blocks.
+Blocks of a given group are compress together into a temporary variable, which is then compressed into our state.
+This way, we break a large part of dependency chains because each group can be independently compressed.
+The remaining dependency chain that remains consists in compressing the resulting temporary variable computed for each group.
 
@@
 \begin{align*}
-H_{1} &= f(\ldots f(f(f(0^{s_b}, M_{0k_b + 1}), M_{1k_b + 1}), M_{2k_b + 1})\ldots, M_{n_g + 1}) \\
-H_{2} &= f(\ldots f(f(f(0^{s_b}, M_{0k_b + 2}), M_{1k_b + 2}), M_{2k_b + 2})\ldots, M_{n_g + 2}) \\
+H_{1} &= f(\ldots f(f(0^{s_b}, M_1), M_2)\ldots, M_{k_b}), \\
+H_{2} &= f(\ldots f(f(0^{s_b}, M_{k_g+1}), M_{k_g+2})\ldots, M_{2k_b}), \\
 &\vdots \\
-H_{k_b} &= f(\ldots f(f(f(0^{s_b}, M_{0k_b + k_b}), M_{1k_b + k_b}), M_{2k_b + k_b})\ldots, M_{n_g + k_b}) \\
+H_{n_g} &= f(\ldots f(f(0^{s_b}, M_{n_g+1}), M_{n_g+2})\ldots, M_{n_g+k_b})
 \end{align*}
@@
 \begin{equation*}
-h(M) = g\left( f( \ldots f(f(\ldots f(f(0^{s_b}, H_1), H_2) \ldots, H_{k_b}), M_{{k_b}{n_g}+1}) \ldots, M_{n_b} ) \right).
+h(M) = g\left( f( \ldots f(f(\ldots f(f(0^s, H_1), H_2) \ldots, H_{n_g}), M_{4{n_g}+1}) \ldots, M_{n_b} ) \right).
 \end{equation*}
@@
 \centering
-\includegraphics[width=1\textwidth]{laned-construction.png}
-\caption{Laned Construction Overview}
+\includegraphics[width=1\textwidth]{temporal-construction.png}
+\caption{Temporal Construction Overview}
 \label{fig:linear-construction}
@@
 
-An alternative to chaining usages of \( f \) is to compress lane hashes by pair, and subsequently compressing the resulting hashes also by pair until we are left with a single hash (for instance \(f(f(f(H_1, H_2), f(H_3, H_4)), f(...))\)).
-In practice, this would allow some form of ILP on the final hash composition as well, decreasing as we get closer to the final hash.
+The yellow and cyan blocks represent two separate dependency chains from the processing of two groups of 4 blocks each.
+Thanks to this separation, instruction level parallelism is possible and will in theory allow intructions parallelization of each group, limited to the number of registry available and the memory bandwidth.
 
@@
 
-TODO
-In practice, the \textbf{GxHash} uses the AES block cipher intrinsics to combines two 128-bit SIMD vectors together combination of SIMD 8-bit wrapping add and state-wide circular shift of one.
-The addition is a simple way to mix the state with the next message block bits, while providing an arithmetic carry which helps in regard to distribution (as opposed to a XOR for instance).
-Adding on a 8-bit basis also helps in regards to distribution, as opposed to adding on larger bit widths.
-This operation alone however comes with several weaknesses:
-\begin{itemize}
-\item Such a simple operation is inherently weak to different kind of attacks.
-This can however be partially addressed with a more robust bit mixing for the finalization function.
-In the context of non-cryptographic hashing, which is the scope of usage of our algorithm, we think it is an acceptable compromise.
-\item A major issue lies in the addition being associative (\(a \cdot b) \cdot c = a \cdot (b \cdot c \)).
-An associative compression function would make the hashing algorithm insensitive to the ordering of the input message blocks, which is something we want to avoid.
-To address this, we circularly shift the state bits by one.
-\end{itemize}
+Modern CPUs feature SIMD instructions for the AES block cipher, which we have adopted in \textbf{GxHash} to combine vectors, allowing robust bit mixing at a low computational cost.
+In practice, we employ a compression with 3 AES rounds, and a faster alternative employing a single AES round for compressing the \( k_b \) blocks of the temporal construction.
+
+The AES block cipher instrinsics is pivotal in GxHash, allowing high quality properties without compromising too much on performance.
 
@@
 \begin{lstlisting}[language=Rust, style=boxed]
-// For ARM 64-bit
+use core::arch::x86_64::*;
 
-use core::arch::aarch64::*;
-
-pub fn compress(a: int8x16_t, b: int8x16_t)
--> int8x16_t {
-    let sum: int8x16_t = vaddq_s8(a, b);
-    return vextq_s8(sum, sum, 1);
+pub fn compress_fast(a: __m128i, b: __m128i)
+-> __m128i {
+    return _mm_aesenc_si128(a, b);
 }
@@
 \begin{lstlisting}[language=Rust, style=boxed]
-// For x86 64-bit
+pub fn compress(a: __m128i, b: __m128i)
+-> __m128i {
+    let keys_1 = _mm_set_epi32(0xFC3BC28E, 0x89C222E5, 0xB09D3E21, 0xF2784542);
+    let keys_2 = _mm_set_epi32(0x03FCE279, 0xCB6B2E9B, 0xB361DC58, 0x39136BD9);
 
-use core::arch::x86_64::*;
-
-pub fn compress(a: __m256i, b: __m256i)
--> __m256i {
-    let sum: state = _mm256_add_epi8(a, b);
-    return _mm256_alignr_epi8(sum, sum, 1);
+    let mut b = _mm_aesenc_si128(b, keys_1);
+    b = _mm_aesenc_si128(b, keys_2);
+    return _mm_aesenclast_si128(a, b);
 }
@@
 Fortunately, both x86 and ARM architectures provide AES (Advanced Encryption Standard) intrinsics that serve as efficient tools for bit mixing.
-The use of three AES block cipher rounds ensures a robust diffusion of bits across the state at a cheap computational cost.\\
+The use of four AES block cipher rounds ensures a robust diffusion of bits across the state at a cheap computational cost.\\
 The AES keys can be set changed, providing a way to have unique hashes per-application and even per-process, protecting from eventual precomputed or replay attack attempts.
@@
 There are several approaches to this, one being combiniting the \( X \)-bit integer parts of the mixed state together (by xoring them together for instance).
-GxHash takes a simpler path by reinterpreting our state into a smaller \( X \)-bit value, assuming an uniform distribution at the mixing stage thanks to the 3 rounds of AES.
+GxHash takes a simpler path by reinterpreting our state into a smaller \( X \)-bit value, assuming an uniform distribution at the mixing stage thanks to the four rounds of AES.
 This allow the GxHash algorithm to generate hashes of any size up to \( s_b \) bits with virtually no additional computational cost.
@@
 
+\paragraph{Random Blobs}\leavevmode\\
+
 \subsubsection{Conclusion}
@@
 
+\paragraph{SMHasher}\leavevmode\\
+GxHash has been rigorously evaluated using the SMHasher\cite{smhasher} test suite, a comprehensive set of tests designed to assess the quality of hash functions.
+SMHasher is widely recognized in the industry for its ability to identify a wide range of potential weaknesses in hash functions, such as poor distribution, bias, and collision resistance.
+Passing the SMHasher test suite is a notable achievement that indicates a hash function's reliability and suitability for practical applications.
+Our GxHash algorithm has successfully met all the criteria set forth by SMHasher, demonstrating its robustness and confirming its effectiveness in producing high-quality, collision-resistant hashes.
+
 \clearpage
@@
 
-Performance is measured as a throughput, in gibibytes of data hashed per second (higher is better).
+Performance is measured as a throughput, in mibibytes of data hashed per second (higher is better).
 This is a common measurement unit for performance in this field.
-Performance is measured against inputs of size 4, 16, 64, 246, 1024, 4096 and 16384 to cover a broad range of use cases.
+Performance is measured against inputs of power-of-two sizes (4, 8, 16, ..., 32768) to cover a broad range of use cases.
 
-For reference, we'll also benchmark other non-cryptographic algorithms under the same conditions, thanks to their Rust implementations, namely: t1ha\cite{rust-t1ha}, xxhash\cite{twox-hash} and HighwayHash\cite{highway-rs}.
+For reference, we'll also benchmark other non-cryptographic algorithms under the same conditions, thanks to their Rust implementations, namely: T1ha-0\cite{rust-t1ha}, XxHash\cite{twox-hash} and HighwayHash\cite{highway-rs}.
 
@@
     \item A Macbook Pro with an M1 Pro chip, to test the algorithm on an ARM architecture which implies different SIMD intrinsics and likely different performance results.
-Note that the T1ha-0 implementation benchmarked does not leverage ARM intrinsics, and this is why it is not benchmarked for this platform (the portable version would perform too poorly).
 \end{itemize}
@@
     \item Leverage larger SIMD intrinsics, such as Intel AVX-512 or ARM SVE2.
-    \item Run more quality benchmarks
+    \item Make use of compiler hints to improve branching predictions.
+    \item Run more quality benchmarks.
     \item Analyze security properties.

### 2023-11-05 src/gxhash/platform/x86_128.rs
Fix 128-bit endianess portability

@@ -53,8 +53,8 @@ unsafe fn get_partial_safe(data: *const u8, len: usize) -> State {
 #[inline]
 #[allow(overflowing_literals)]
 pub unsafe fn compress(a: State, b: State) -> State {
-    let keys_1 = _mm_set_epi32(0xFC3BC28E, 0x89C222E5, 0xB09D3E21, 0xF2784542);
-    let keys_2 = _mm_set_epi32(0x03FCE279, 0xCB6B2E9B, 0xB361DC58, 0x39136BD9);
+    let keys_1 = _mm_set_epi32(0xF2784542, 0xB09D3E21, 0x89C222E5, 0xFC3BC28E);
+    let keys_2 = _mm_set_epi32(0x39136BD9, 0xB361DC58, 0xCB6B2E9B, 0x03FCE279);
 
     // 2+1 rounds of AES for compression
     let mut b = _mm_aesenc_si128(b, keys_1);
@@ -72,9 +72,9 @@ pub unsafe fn compress_fast(a: State, b: State) -> State {
 #[allow(overflowing_literals)]
 pub unsafe fn finalize(hash: State, seed: i32) -> State {
     // Hardcoded AES keys
-    let keys_1 = _mm_set_epi32(0x713B01D0, 0x8F2F35DB, 0xAF163956, 0x85459F85);
-    let keys_2 = _mm_set_epi32(0x1DE09647, 0x92CFA39C, 0x3DD99ACA, 0xB89C054F);
-    let keys_3 = _mm_set_epi32(0xC78B122B, 0x5544B1B7, 0x689D2B7D, 0xD0012E32);
+    let keys_1 = _mm_set_epi32(0x85459F85, 0xAF163956, 0x8F2F35DB, 0x713B01D0);
+    let keys_2 = _mm_set_epi32(0xB89C054F, 0x3DD99ACA, 0x92CFA39C, 0x1DE09647);
+    let keys_3 = _mm_set_epi32(0xD0012E32, 0x689D2B7D, 0x5544B1B7, 0xC78B122B);
 
     // 4 rounds of AES
     let mut hash = _mm_aesenc_si128(hash, _mm_set1_epi32(seed));

### 2023-11-05 article/article.tex
Update article

@@
 
-In the rapidly evolving landscape of data processing and cybersecurity, hashing algorithms play a pivotal role in ensuring data integrity and security.
-Traditional hashing methods, while effective, often fail to fully utilize the computational capabilities of modern processors.
-This paper introduces the GxHash hashing algorithm, a novel approach that harnesses the power of high Instruction-Level Parallelism (ILP) and Single Instruction, Multiple Data (SIMD) capabilities of contemporary CPUs to achieve high-throughput non-cryptographic hashing.
-Through a comprehensive analysis, including benchmarks and comparisons with existing methods, we demonstrate that GxHash significantly outperforms conventional algorithms in terms of speed and computational efficiency without compromising on security.
-The paper also explores the implications, limitations, and avenues for future research in this burgeoning field.
+Efficiency and speed are the keystones of modern data processing, especially when handling vast datasets or operating within latency-critical applications.
+In this landscape, non-cryptographic hashing functions are fundamental, offering rapid data organization and retrieval mechanisms.
+Recognizing the limitations of existing hashing techniques, which often underutilize modern processing capabilities, this paper presents GxHash—an high-throughput non-cryptographic hashing algorithm.
+GxHash is meticulously engineered to exploit the full spectrum of Instruction-Level Parallelism (ILP) and Single Instruction, Multiple Data (SIMD) features available in contemporary CPUs.
+Our empirical analysis, corroborated by extensive benchmarks, reveals that GxHash substantially surpasses traditional hashing functions in processing velocity while maintaining a reliable distribution of hash values.
+The subsequent discussions delineate the algorithm's practical significance, explore its operational boundaries, and suggest trajectories for further innovation in the domain of high-speed data hashing.
 
@@
 
-As a software engineer at Equativ, a company specializing in high-performance AdServing backends that handle billions of auctions daily,
-I face unique challenges in maximizing throughput while minimizing latency.
-In this high-stakes environment, every millisecond counts, and the performance of underlying data structures becomes critically important.
-As we heavily rely on in-memory caches and other hash-based data structures, making the efficiency of hashing algorithms a non-trivial concern in our system's overall performance.\\\\
+As a software engineer at Equativ, which specializes in high-performance AdServing backends managing billions of auctions daily, I encounter unique challenges in maximizing throughput and minimizing latency.
+In this critical environment, where every millisecond is valuable, the performance of underlying data structures is crucial.
+Our significant reliance on in-memory caches and other hash-based data structures makes the efficiency of hashing algorithms an essential factor in our system's overall performance.\\\\
 While diving into the theory of hashing out of both necessity and intellectual curiosity, I discovered that existing hashing algorithms, including those built on well-known constructions like Merkle–Damgård, are not optimized to exploit the full capabilities of modern general-purpose CPUs.
@@
 The primary motivation behind this research is to bridge the existing performance gap by designing a hashing algorithm that fully leverages SIMD and ILP capabilities.
-The aim is to achieve an order-of-magnitude improvement in hashing speed, thereby revolutionizing the efficiency of various applications, from databases to real-time analytics and beyond.\\\\
-In summary, this work is driven by both the practical needs of my professional environment and a personal passion for pushing the boundaries of what is technically possible in the realm of hashing algorithms.
+The aim is to achieve an order-of-magnitude improvement in hashing speed, thereby revolutionizing the efficiency of various applications, from databases to real-time analytics and beyond.
 
@@
 These overheads, while perhaps manageable in applications that can afford greater latencies, become less justifiable when aiming for high-throughput, low-latency operations that are typical in non-cryptographic hashing scenarios.\\\\
-In summary, while TLP might be a suitable performance optimization strategy in other computational contexts, we chose to leave it aside in this paper.
+For these reasons, TLP has been left aside in this paper.
 
@@
 \begin{itemize}
-\item \textbf{Synchronization Overhead:} The parallel nature of the algorithm necessitates synchronization between different processing threads or units, especially at higher tree levels where dependencies exist.
-This overhead counters the gains from parallelization.
 \item \textbf{Memory Consumption:} Tree constructions typically require more memory to store intermediate hash values, particularly when branching factors are high.
@@
 \item \textbf{Implementation Complexity:} The algorithmic and data-structure requirements for implementing tree-based hashing are more complex than those of a straightforward sequential hashing algorithm.
-The increased complexity can introduce more room for errors and maintenance challenges.
+The increased complexity can introduce more room for errors, maintenance challenges, and less inlining opportunities as the bytecode for a given implementation will be subtantially larger compared to a simpler construction.
 \end{itemize}
@@
 
-While compilers and CPUs employ various techniques to optimize ILP, their capabilities are often constrained by the inherent data dependencies in the code.
+While compilers and CPUs employ various techniques to optimize ILP, their capabilities are constrained by the inherent data dependencies in the code.
 It's for this reason that algorithmic design can be pivotal.
@@
 
-To make ILP possible, for the function \texttt{temp} we unroll the loop and hash a few inputs altogether, independently from \texttt{h}, and mix it once thereafter with \texttt{h}.
+To make ILP possible, for the function \texttt{temporal} we unroll the loop and hash a few inputs altogether, independently from \texttt{h}, and mix it once thereafter with \texttt{h}.
 We still have a dependency chain on \texttt{h}, but for fewer iterations.
@@
 \begin{lstlisting}[language=Rust, style=boxed]
-fn temp(input: &[u64]) -> u64 {
+fn temporal(input: &[u64]) -> u64 {
     let mut h: u64 = OFFSET;
@@
 The \textbf{Temporal Construction} processes the message by groups of \( k_b \) blocks.
-Blocks of a given group are compress together into a temporary variable, which is then compressed into our state.
+Blocks of a given group are compressed together into a temporary variable, which is then compressed into our state.
 This way, we break a large part of dependency chains because each group can be independently compressed.
-The remaining dependency chain that remains consists in compressing the resulting temporary variable computed for each group.
+The remaining dependency chain consists in compressing the resulting temporary variable computed for each group.
 
@@
 \begin{align*}
-H_{1} &= f(\ldots f(f(0^{s_b}, M_1), M_2)\ldots, M_{k_b}), \\
-H_{2} &= f(\ldots f(f(0^{s_b}, M_{k_g+1}), M_{k_g+2})\ldots, M_{2k_b}), \\
+H_{1} &= f(\ldots f(f(M_1, M_2), M_3)\ldots, M_{k_b}), \\
+H_{2} &= f(\ldots f(f(M_{k_g+1}, M_{k_g+2}), M_{k_g+3})\ldots, M_{2k_b}), \\
 &\vdots \\
-H_{n_g} &= f(\ldots f(f(0^{s_b}, M_{n_g+1}), M_{n_g+2})\ldots, M_{n_g+k_b})
+H_{n_g} &= f(\ldots f(f(M_{n_g+1}, M_{n_g+2}), M_{n_g+3})\ldots, M_{n_g+k_b})
 \end{align*}
@@
     \item \textbf{Efficiency through Simplicity:} Minimizing the number of operations is crucial, as fewer operations typically translate to faster execution.
+Also, less operations often translates to less bytecode, which increases the odds of inlining, further improving performance.
     \item \textbf{Hash Quality Assurance:} Despite these performance optimizations, the algorithm must ensure a minimum level of hash quality to maintain low collision probabilities.
@@
 
-To optimize throughput, the pipe width \( s_b \) is set to match the native width of the CPU's SIMD registers.
+To optimize throughput, the pipe width \( s_b \) is set to match the width of the CPU's SIMD registers.
 This alignment ensures that each SIMD instruction operates on the entire pipe width, maximizing data processed per instruction.
@@
 Consequently, the GxHash design aligns with the characteristics of a wide-pipe construction, as discussed in section \ref{widepipe}.
-This makes GxHash more resistant to multicollision attacks.
+This makes GxHash more resistant to collisions.
 
@@
 
-Given the nature of the compression function \( f: \{0,1\}^{s_b} \times \{0,1\}^{s_b} \to \{0,1\}^{s_b} \), where the domain is much larger than the codomain (\( s_b \times s_b > s_b \)), it becomes mathematically impossible for the function to be one-to-one.
-There will inevitably be multiple different inputs that map to the same output, known as collisions.\\
+Given the nature of the compression function \( f: \{0,1\}^{s_b} \times \{0,1\}^{s_b} \to \{0,1\}^{s_b} \), where the domain is much larger than the codomain (\( s_b \times s_b > s_b \)), it becomes mathematically impossible for the function to be injective.
+There will inevitably be multiple different inputs that map to the same output, known as collisions.
+Given this, the selection for the compression has to be empirical.
 
-With the inevitable non-bijectivity, the performance requirements and the limited set of available SIMD intrinsics, the selection for the compression has to be empirical, thus implying specifying a version to account for these current choices that may be improved in future versions.\\
-
-Modern CPUs feature SIMD instructions for the AES block cipher, which we have adopted in \textbf{GxHash} to combine vectors, allowing robust bit mixing at a low computational cost.
+Modern CPUs feature SIMD instructions for the AES (Advanced Encryption Standard) block cipher, which we have adopted in \textbf{GxHash} to combine vectors, allowing robust bit mixing at a low computational cost.
 In practice, we employ a compression with 3 AES rounds, and a faster alternative employing a single AES round for compressing the \( k_b \) blocks of the temporal construction.
@@
 Given the inherent simplicity of the GxHash compression, it is worth for the finalization to incorporate slightly more intricate bit mixing operations, especially given it runs only once per message hashed, as opposed to the compression that occurs once for each block.\\
-Leveraging SIMD capabilities can help in regard to performance and efficiency, which remains for us a primary consideration.
-Fortunately, both x86 and ARM architectures provide AES (Advanced Encryption Standard) intrinsics that serve as efficient tools for bit mixing.
-The use of four AES block cipher rounds ensures a robust diffusion of bits across the state at a cheap computational cost.\\
-The AES keys can be set changed, providing a way to have unique hashes per-application and even per-process, protecting from eventual precomputed or replay attack attempts.
+As performance and efficiency remains for us a primary consideration, we once again leverage SIMD capabilities with AES intrinsics, ensuring a robust diffusion of bits across the state at a cheap computational cost.\\
+A seed is injected at this finalization stage, more specifically as a key for the first AES round, providing a way to have unique hashes per-application and even per-process, protecting from eventual precomputed or replay attack attempts.
 
@@
     \item Make use of compiler hints to improve branching predictions.
-    \item Run more quality benchmarks.
+    \item Benchmark in more test suite to further assess the distribution and avalanche properties.
     \item Analyze security properties.
@@
 
+\clearpage
 \section{Conclusion}

### 2023-11-07 article/article.tex
Fix typo in article
Fix confusion with laning in article

@@
 Let's define \( n_g = \lfloor {n_b}/{k_b} \rfloor \) as the number of whole groups of \( k_b \) message blocks. \\
-For each lane we compute an intermediate hash, \( H_i \), as follows:
+For each group we compute an intermediate hash, \( H_i \), as follows:
 
@@
 
-\paragraph{Random Blobs}\leavevmode\\
-
 \subsubsection{Conclusion}
@@
 \subsubsection{Compiler Dependencies} 
-The Temporal Construction presented in this paper is implemented for GxHash by declaring each lane with its own variable.
+The Temporal Construction presented in this paper is implemented for GxHash by declaring at temporary variable on each group iteration, assuming that the compilers understands that most of each iteration can be parallelized.
 While it worked at the time of writing (rustc 1.68.0), it is in the end the compiler's responsibility to decide how many registers to use.
@@
     \item Rewrite the algorithm in assembly code or a language that is more explicit about registers.
-    \item Introduce more than one stage of laning. For instance 16 lanes, then 8 lanes, then 4 lanes, and finally 2 lanes, to leverage ILP as much as possible.
     \item Organize processing loop to result in even less bytecode to be generated, favoring inlining opportunities.

### 2023-11-18 src/hasher.rs
Make GxHash DOS resistant thanks to seed randomization

@@ -1,20 +1,51 @@
 use std::hash::{Hasher, BuildHasherDefault};
 use std::collections::{HashMap, HashSet};
+
+use rand::Rng;
+
 use crate::gxhash::*;
 use crate::gxhash::platform::*;
 
 /// A `Hasher` for hashing an arbitrary stream of bytes.
+/// # Features
+/// - The fastest [`Hasher`] of its class<sup>1</sup>, for all input sizes
+/// - Highly collision resitant
+/// - DOS resistant thanks to seed randomization when using [`GxHasher::default()`]
+/// 
+/// *<sup>1</sup>There might me faster alternatives, such as `fxhash` for very small input sizes, but that usually have low quality properties.*
 pub struct GxHasher(State);
 
 impl Default for GxHasher {
+    /// Create a new hasher with a random seed for DOS resistance.
+    /// 
+    /// # Example
+    ///
+    /// ```
+    /// use std::hash::Hasher;
+    /// use gxhash::GxHasher;
+    ///
+    /// let mut hasher = GxHasher::default();
+    ///
+    /// hasher.write(b"Hello");
+    /// hasher.write_u32(123);
+    /// hasher.write_u8(42);
+    ///
+    /// println!("Hash is {:x}!", hasher.finish());
+    /// ```
     #[inline]
     fn default() -> GxHasher {
-        GxHasher(unsafe { create_empty() })
+        let mut rng = rand::thread_rng();
+        let seed: i64 = rng.gen::<i64>();
+        GxHasher(unsafe { create_seed(seed) })
     }
 }
 
 impl GxHasher {
     /// Creates a new hasher using the provided seed.
+    /// 
+    /// # Warning ⚠️
+    /// Hardcoding a seed may make your [`Hasher`] vulnerable to DOS attacks.  
+    /// It is recommended to use [`GxHasher::default()`] to create a DOS resistant [`Hasher`].
     ///
     /// # Example
     ///

### 2023-11-18 src/hasher.rs
Make GxHash DOS resistant thanks to seed randomization

@@ -1,12 +1,41 @@
-use std::hash::{Hasher, BuildHasherDefault};
+use std::hash::{Hasher, BuildHasher};
 use std::collections::{HashMap, HashSet};
+
+use rand::Rng;
+
 use crate::gxhash::*;
 use crate::gxhash::platform::*;
 
 /// A `Hasher` for hashing an arbitrary stream of bytes.
+/// # Features
+/// - The fastest [`Hasher`] of its class<sup>1</sup>, for all input sizes
+/// - Highly collision resitant
+/// - DOS resistant thanks to seed randomization when using [`GxHasher::default()`]
+/// 
+/// *<sup>1</sup>There might me faster alternatives, such as `fxhash` for very small input sizes, but that usually have low quality properties.*
 pub struct GxHasher(State);
 
 impl Default for GxHasher {
+    /// Creates a new hasher with a empty seed.
+    /// 
+    /// # Warning ⚠️
+    /// Not using a seed may make your [`Hasher`] vulnerable to DOS attacks.  
+    /// It is recommended to use [`GxBuildHasher::default()`] to create a DOS resistant [`Hasher`]s.
+    /// 
+    /// # Example
+    ///
+    /// ```
+    /// use std::hash::Hasher;
+    /// use gxhash::GxHasher;
+    ///
+    /// let mut hasher = GxHasher::default();
+    ///
+    /// hasher.write(b"Hello");
+    /// hasher.write_u32(123);
+    /// hasher.write_u8(42);
+    ///
+    /// println!("Hash is {:x}!", hasher.finish());
+    /// ```
     #[inline]
     fn default() -> GxHasher {
         GxHasher(unsafe { create_empty() })
@@ -15,6 +44,10 @@ impl Default for GxHasher {
 
 impl GxHasher {
     /// Creates a new hasher using the provided seed.
+    /// 
+    /// # Warning ⚠️
+    /// Hardcoding a seed may make your [`Hasher`] vulnerable to DOS attacks.  
+    /// It is recommended to use [`GxBuildHasher::default()`] to create a DOS resistant [`Hasher`]s.
     ///
     /// # Example
     ///
@@ -65,13 +98,30 @@ impl Hasher for GxHasher {
     }
 }
 
-/// A builder for default GxHash hashers.
-pub type GxBuildHasher = BuildHasherDefault<GxHasher>;
+/// A builder for building DOS-resistant [`GxHasher`]s.
[…]

### 2023-11-18 src/hasher.rs
Fix missing inline attribute

@@ -112,7 +112,7 @@ impl Default for GxBuildHasher {
 
 impl BuildHasher for GxBuildHasher {
     type Hasher = GxHasher;
-
+    #[inline]
     fn build_hasher(&self) -> GxHasher {
         GxHasher::with_seed(self.0)
     }

### 2023-11-18 benches/hashset.rs
Add AHash to HashSet benchmark

@@ -1,3 +1,4 @@
+use ahash::AHashSet;
 use criterion::{criterion_group, criterion_main, Criterion};
 use fnv::FnvHashSet;
 use gxhash::*;
@@ -32,6 +33,11 @@ fn benchmark_for_string(c: &mut Criterion, string: &str) {
 
     let mut set = HashSet::<&str, BuildHasherDefault<xxh3::Hash64>>::default();
     group.bench_function("XxHash", |b| {
+        b.iter(|| set.insert(string))
+    });
+
+    let mut set = AHashSet::default();
+    group.bench_function("AHash", |b| {
         b.iter(|| set.insert(string))
     });
 

### 2023-11-18 src/hasher.rs
Tone down "DOS resistant" claim

@@ -10,7 +10,7 @@ use crate::gxhash::platform::*;
 /// # Features
 /// - The fastest [`Hasher`] of its class<sup>1</sup>, for all input sizes
 /// - Highly collision resitant
-/// - DOS resistant thanks to seed randomization when using [`GxHasher::default()`]
+/// - DOS resistance thanks to seed randomization when using [`GxHasher::default()`]
 /// 
 /// *<sup>1</sup>There might me faster alternatives, such as `fxhash` for very small input sizes, but that usually have low quality properties.*
 pub struct GxHasher(State);
@@ -20,7 +20,7 @@ impl Default for GxHasher {
     /// 
     /// # Warning ⚠️
     /// Not using a seed may make your [`Hasher`] vulnerable to DOS attacks.  
-    /// It is recommended to use [`GxBuildHasher::default()`] to create a DOS resistant [`Hasher`]s.
+    /// It is recommended to use [`GxBuildHasher::default()`] for improved DOS resistance.
     /// 
     /// # Example
     ///
@@ -47,7 +47,7 @@ impl GxHasher {
     /// 
     /// # Warning ⚠️
     /// Hardcoding a seed may make your [`Hasher`] vulnerable to DOS attacks.  
-    /// It is recommended to use [`GxBuildHasher::default()`] to create a DOS resistant [`Hasher`]s.
+    /// It is recommended to use [`GxBuildHasher::default()`] for improved DOS resistance.
     ///
     /// # Example
     ///
@@ -98,7 +98,7 @@ impl Hasher for GxHasher {
     }
 }
 
-/// A builder for building DOS-resistant [`GxHasher`]s.
+/// A builder for building GxHasher with randomized seeds by default, for improved DOS resistance.
 pub struct GxBuildHasher(i64);
 
 impl Default for GxBuildHasher {

### 2023-11-18 src/gxhash/platform/arm_128.rs
Only finalize on Hasher::finish

@@ -95,7 +95,7 @@ unsafe fn aes_encrypt_last(data: uint8x16_t, keys: uint8x16_t) -> uint8x16_t {
 }
 
 #[inline(always)]
-pub unsafe fn finalize(hash: State, seed: State) -> State {
+pub unsafe fn finalize(hash: State) -> State {
     // Hardcoded AES keys
     let keys_1 = vld1q_u32([0x713B01D0, 0x8F2F35DB, 0xAF163956, 0x85459F85].as_ptr());
     let keys_2 = vld1q_u32([0x1DE09647, 0x92CFA39C, 0x3DD99ACA, 0xB89C054F].as_ptr());
@@ -103,7 +103,6 @@ pub unsafe fn finalize(hash: State, seed: State) -> State {
 
     // 3 rounds of AES
     let mut hash = ReinterpretUnion{ int8: hash }.uint8;
-    hash = aes_encrypt(hash, ReinterpretUnion{ int8: seed }.uint8);
     hash = aes_encrypt(hash, ReinterpretUnion{ uint32: keys_1 }.uint8);
     hash = aes_encrypt(hash, ReinterpretUnion{ uint32: keys_2 }.uint8);
     hash = aes_encrypt_last(hash, ReinterpretUnion{ uint32: keys_3 }.uint8);

### 2023-11-18 src/gxhash/platform/x86_256.rs

@@ -68,15 +68,14 @@ pub unsafe fn compress_fast(a: State, b: State) -> State {
 
 #[inline(always)]
 #[allow(overflowing_literals)]
-pub unsafe fn finalize(hash: State, seed: State) -> State {
+pub unsafe fn finalize(hash: State) -> State {
     // Hardcoded AES keys
     let keys_1 = _mm256_set_epi32(0x713B01D0, 0x8F2F35DB, 0xAF163956, 0x85459F85, 0xB49D3E21, 0xF2784542, 0x2155EE07, 0xC197CCE2);
     let keys_2 = _mm256_set_epi32(0x1DE09647, 0x92CFA39C, 0x3DD99ACA, 0xB89C054F, 0xCB6B2E9B, 0xC361DC58, 0x39136BD9, 0x7A83D76F);
     let keys_3 = _mm256_set_epi32(0xC78B122B, 0x5544B1B7, 0x689D2B7D, 0xD0012E32, 0xE2784542, 0x4155EE07, 0xC897CCE2, 0x780BF2C2);
 
     // 4 rounds of AES
-    let mut hash = _mm256_aesenc_epi128(hash, seed);
-    hash = _mm256_aesenc_epi128(hash, keys_1);
+    let mut hash = _mm256_aesenc_epi128(hash, keys_1);
     hash = _mm256_aesenc_epi128(hash, keys_2);
     hash = _mm256_aesenclast_epi128(hash, keys_3);
 

### 2023-11-18 src/gxhash/platform/x86_128.rs
Only finalize on Hasher::finish

@@ -68,15 +68,14 @@ pub unsafe fn compress_fast(a: State, b: State) -> State {
 
 #[inline(always)]
 #[allow(overflowing_literals)]
-pub unsafe fn finalize(hash: State, seed: State) -> State {
+pub unsafe fn finalize(hash: State) -> State {
     // Hardcoded AES keys
     let keys_1 = _mm_set_epi32(0x85459F85, 0xAF163956, 0x8F2F35DB, 0x713B01D0);
     let keys_2 = _mm_set_epi32(0xB89C054F, 0x3DD99ACA, 0x92CFA39C, 0x1DE09647);
     let keys_3 = _mm_set_epi32(0xD0012E32, 0x689D2B7D, 0x5544B1B7, 0xC78B122B);
 
     // 4 rounds of AES
-    let mut hash = _mm_aesenc_si128(hash, seed);
-    hash = _mm_aesenc_si128(hash, keys_1);
+    let mut hash = _mm_aesenc_si128(hash, keys_1);
     hash = _mm_aesenc_si128(hash, keys_2);
     hash = _mm_aesenclast_si128(hash, keys_3);
 

### 2023-11-18 src/hasher.rs

@@ -1,7 +1,8 @@
 use std::hash::{Hasher, BuildHasher};
 use std::collections::{HashMap, HashSet};
+use std::mem::MaybeUninit;
 
-use rand::Rng;
+use rand::{Rng, RngCore};
 
 use crate::gxhash::*;
 use crate::gxhash::platform::*;
@@ -13,7 +14,16 @@ use crate::gxhash::platform::*;
 /// - DOS resistance thanks to seed randomization when using [`GxHasher::default()`]
 /// 
 /// *<sup>1</sup>There might me faster alternatives, such as `fxhash` for very small input sizes, but that usually have low quality properties.*
-pub struct GxHasher(State);
+pub struct GxHasher {
+    state: State
+}
+
+impl GxHasher {
+    #[inline]
+    fn with_state(state: State) -> GxHasher {
+        GxHasher { state: state }
+    }
+}
 
 impl Default for GxHasher {
     /// Creates a new hasher with a empty seed.
@@ -38,7 +48,7 @@ impl Default for GxHasher {
     /// ```
     #[inline]
     fn default() -> GxHasher {
-        GxHasher(unsafe { create_empty() })
+        GxHasher::with_state(unsafe { create_empty() })
     }
 }
 
@@ -66,7 +76,7 @@ impl GxHasher {
     #[inline]
     pub fn with_seed(seed: i64) -> GxHasher {
         // Use gxhash64 to generate an initial state from a seed
-        GxHasher(unsafe { gxhash(&[], create_seed(seed)) })
+        GxHasher::with_state(unsafe { create_seed(seed) })
     }
 
     /// Finish this hasher and return the hashed value as a 128 bit
@@ -76,7 +86,7 @@ impl GxHasher {
         debug_assert!(std::mem::size_of::<State>() >= std::mem::size_of::<u128>());
 
         unsafe {
-            let p = &self.0 as *const State as *const u128;
+            let p = &finalize(self.state) as *const State as *const u128;
             *p
         }
     }
@@ -86,7 +96,7 @@ impl Hasher for GxHasher {
     #[inline]
     fn finish(&self) -> u64 {
         unsafe {
-            let p = &self.0 as *const State as *const u64;
+            let p = &finalize(self.state) as *const State as *const u64;
             *p
         }
     }
@@ -94,19 +104,24 @@ impl Hasher for GxHasher {
     #[inline]
     fn write(&mut self, bytes: &[u8]) {
[…]

### 2023-11-18 src/gxhash/mod.rs
Only finalize on Hasher::finish

@@ -68,11 +68,11 @@ macro_rules! load_unaligned {
 
 #[inline(always)]
 pub(crate) unsafe fn gxhash(input: &[u8], seed: State) -> State {
-    finalize(compress_all(input), seed)
+    finalize(compress_fast(compress_all(input), seed))
 }
 
 #[inline(always)]
-unsafe fn compress_all(input: &[u8]) -> State {
+pub(crate) unsafe fn compress_all(input: &[u8]) -> State {
 
     let len = input.len();
     let mut ptr = input.as_ptr() as *const State;

### 2023-11-18 article/article.tex
Fix typo in article

@@
 Once the state's bits have been thoroughly mixed, the next step is to reduce this state into a smaller, fixed-size hash output, typically 32 or 64 bits.
-There are several approaches to this, one being combiniting the \( X \)-bit integer parts of the mixed state together (by xoring them together for instance).
+There are several approaches to this, one being combining the \( X \)-bit integer parts of the mixed state together (by xoring them together for instance).
 GxHash takes a simpler path by reinterpreting our state into a smaller \( X \)-bit value, assuming an uniform distribution at the mixing stage thanks to the four rounds of AES.
@@
     The avalanche effect can be computed by flipping a single random bit for a given input and checking the differences between the hashes generated before and after the bit was flipped.
-Ideally, half of the bit should change on average.
+Ideally, half of the hash bits should change on average.
     \item \textbf{Performance:} The performance of a noncryptographic hash function is usually reflected by the performance of the application using it.

### 2023-11-19 article/article.tex
Fix spelling and grammar mistakes

@@
 In this landscape, non-cryptographic hashing functions are fundamental, offering rapid data organization and retrieval mechanisms.
-Recognizing the limitations of existing hashing techniques, which often underutilize modern processing capabilities, this paper presents GxHash—an high-throughput non-cryptographic hashing algorithm.
+Recognizing the limitations of existing hashing techniques, which often underutilize modern processing capabilities, this paper presents GxHash—a high-throughput non-cryptographic hashing algorithm.
 GxHash is meticulously engineered to exploit the full spectrum of Instruction-Level Parallelism (ILP) and Single Instruction, Multiple Data (SIMD) features available in contemporary CPUs.
@@
 While diving into the theory of hashing out of both necessity and intellectual curiosity, I discovered that existing hashing algorithms, including those built on well-known constructions like Merkle–Damgård, are not optimized to exploit the full capabilities of modern general-purpose CPUs.
-These CPUs offer advanced features such as Single Instruction, Multiple Data (SIMD) and Instruction-Level Parallelism (ILP), which remain largely untapped by current hashing methods.\\\\
+These CPUs offer advanced features such as Single Instruction, Multiple Data (SIMD), and Instruction-Level Parallelism (ILP), which remain largely untapped by current hashing methods.\\\\
 The challenge of creating a faster, more efficient hashing algorithm became not just a professional necessity but also a personal quest.
@@
 In such contexts, hash computation is often expected to be extremely fast, typically requiring execution times ranging from nanoseconds to microseconds.
-Given these consideration, the paper intentionally excludes Thread-Level Parallelism
+Given these considerations, the paper intentionally excludes Thread-Level Parallelism
 (TLP) as a viable strategy for performance optimization.\\\\
@@
 
-Ensuring portability (algorithm generating the same hashes consistently accross different platforms for a given input) is a constrain that may hinder some potential optimization.
+Ensuring portability (algorithm generating the same hashes consistently across different platforms for a given input) is a constraint that may hinder some potential optimization.
 Our goal being performance first, and our scope of application mainly focused on in-process usages such as hashtables, portability can be left out for these researches.
-Yet, it remains crutial for the algorithm to work under both x86 and ARM 64-bit platforms that represent most of today's general purpose computing systems.
+Yet, it remains crucial for the algorithm to work under both x86 and ARM 64-bit platforms that represent most of today's general-purpose computing systems.
 
@@
 
-The Sponge construction,  proceeds in two phases: absorption and squeezing.
+The Sponge construction proceeds in two phases: absorption and squeezing.
 During the absorption phase, blocks of input data are XORed into a portion of the internal state, followed by a cryptographic permutation of the entire state.
@@
 The HAsh Iterative FrAmework (HAIFA) not only mitigates vulnerabilities but also incorporates features like support for a configurable number of rounds and real-time incremental hashing.
-However, like the standard Merkle–Damgård and Sponge constructions, the HAsh Iterative FrAmework (HAIFA) is also inherently sequential in its processing of message blocks.
+However, like the standard Merkle–Damgård, and Sponge constructions, the HAsh Iterative FrAmework (HAIFA) is also inherently sequential in its processing of message blocks.
 Each iteration of the compression function in HAIFA depends on the outcome of the previous iteration.
@@
 \item \textbf{Implementation Complexity:} The algorithmic and data-structure requirements for implementing tree-based hashing are more complex than those of a straightforward sequential hashing algorithm.
-The increased complexity can introduce more room for errors, maintenance challenges, and less inlining opportunities as the bytecode for a given implementation will be subtantially larger compared to a simpler construction.
+The increased complexity can introduce more room for errors, maintenance challenges, and less inlining opportunities as the bytecode for a given implementation will be substantially larger compared to a simpler construction.
 \end{itemize}
@@
 
-Most modern general-purpose CPUs employ a superscalar architecture which enables Instruction-Level Parallelism (ILP). 
+Most modern general-purpose CPUs employ a superscalar architecture, which enables Instruction-Level Parallelism (ILP). 
 Minimizing dependencies in an algorithm allows a superscalar processor to execute more instructions concurrently, thus maximizing its inherent parallelism and overall performance.
@@
 Both approaches have their pros and cons. The \texttt{temporal} approach is simpler to implement and will lead to less bytecode generation.
-The following section will delve more in depth into the definition of a \textbf{Temporal Construction}.
+The following section will delve more in-depth into the definition of a \textbf{Temporal Construction}.
 
@@
 This way, we break a large part of dependency chains because each group can be independently compressed.
-The remaining dependency chain consists in compressing the resulting temporary variable computed for each group.
+The remaining dependency chain consists of compressing the resulting temporary variable computed for each group.
 
@@
 Let's define \( n_g = \lfloor {n_b}/{k_b} \rfloor \) as the number of whole groups of \( k_b \) message blocks. \\
-For each group we compute an intermediate hash, \( H_i \), as follows:
+For each group, we compute an intermediate hash, \( H_i \), as follows:
 
@@
 The yellow and cyan blocks represent two separate dependency chains from the processing of two groups of 4 blocks each.
-Thanks to this separation, instruction level parallelism is possible and will in theory allow intructions parallelization of each group, limited to the number of registry available and the memory bandwidth.
+Thanks to this separation, instruction level parallelism is possible and will in theory allow intructions parallelization of each group, limited to the number of registries available and the memory bandwidth.
 
@@
     \item \textbf{Efficiency through Simplicity:} Minimizing the number of operations is crucial, as fewer operations typically translate to faster execution.
-Also, less operations often translates to less bytecode, which increases the odds of inlining, further improving performance.
+Also, fewer operations often translate to less bytecode, which increases the odds of inlining, further improving performance.
     \item \textbf{Hash Quality Assurance:} Despite these performance optimizations, the algorithm must ensure a minimum level of hash quality to maintain low collision probabilities.
@@
 
-The AES block cipher instrinsics is pivotal in GxHash, allowing high quality properties without compromising too much on performance.
+The AES block cipher intrinsic is pivotal in GxHash, allowing high-quality properties without compromising too much on performance.
 
@@
 The finalization process in the GxHash algorithm is crucial to ensure the transformation of its internal state into a fixed-size, uniformly distributed hash output.
-This process is delineated into two primary steps: mixing the bits and reducing to the desired hash size.
+This process is delineated into two primary steps: mixing the bits and reducing output to the desired hash size.
 
@@
 Given the inherent simplicity of the GxHash compression, it is worth for the finalization to incorporate slightly more intricate bit mixing operations, especially given it runs only once per message hashed, as opposed to the compression that occurs once for each block.\\
-As performance and efficiency remains for us a primary consideration, we once again leverage SIMD capabilities with AES intrinsics, ensuring a robust diffusion of bits across the state at a cheap computational cost.\\
+As performance and efficiency remain a primary consideration, we once again leverage SIMD capabilities with AES intrinsics, ensuring a robust diffusion of bits across the state at a cheap computational cost.\\
 A seed is injected at this finalization stage, more specifically as a key for the first AES round, providing a way to have unique hashes per-application and even per-process, protecting from eventual precomputed or replay attack attempts.
@@
 There are several approaches to this, one being combining the \( X \)-bit integer parts of the mixed state together (by xoring them together for instance).
-GxHash takes a simpler path by reinterpreting our state into a smaller \( X \)-bit value, assuming an uniform distribution at the mixing stage thanks to the four rounds of AES.
-This allow the GxHash algorithm to generate hashes of any size up to \( s_b \) bits with virtually no additional computational cost.
+GxHash takes a simpler path by reinterpreting our state into a smaller \( X \)-bit value, assuming a uniform distribution at the mixing stage thanks to the four rounds of AES.
+This allows the GxHash algorithm to generate hashes of any size up to \( s_b \) bits with virtually no additional computational cost.
 
@@
 
-Unrolling the loop is a complementary optimization that diminishes greatly any loop overhead.
+Unrolling the loop is a complementary optimization that greatly diminishes any loop overhead.
 In the case of GxHash, the temporal construction implies some kind of unrolling, which is sufficient for achieving the high throughput numbers we see in our benchmarks.
@@
 
-In practice, a naive implementation for \( p \) for GxHash in computer code implies copying the remaining bytes into a zero-initialized buffer of size \( s_b \), which can then be loaded onto an SIMD registry and then handed to the compression.
+In practice, a naive implementation for \( p \) for GxHash in computer code implies copying the remaining bytes into a zero-initialized buffer of size \( s_b \), which can then be loaded onto a SIMD registry and then handed to the compression.
 In our performance-critical context, these allocations and copies introduce significant overhead.
@@
 unsafe fn read_padded(p: *const __m128i, len: isize) -> __m128i {
-    // Consecuive indices on which we compare the length against, byte per byte, to retreive our mask.
+    // Consecutive indices on which we compare the length against, byte per byte, to retrieve our mask.
     // The order is descending or ascending depending on the endianness
@@
 We can check if an unsafe operation is within a single page.
-If it is, we can use the optimized method; if not, we fallback to the naive method.
+If it is, we can use the optimized method; if not, we fall back to the naive method.
 
@@
     We can estimate the uniformity of the distribution by counting the number of times each bit is set and computing a standard deviation.
-This "bit distribution" criteria however does not qualify the distribution of the hashes as a whole, so a complementary estimator is the "bucketed distribution", which be computed by placing generated hashes into a fixed-size grid and counting occurrences.
+This "bit distribution" criteria however does not qualify the distribution of the hashes as a whole, so a complementary estimator is the "bucketed distribution", which can be computed by placing generated hashes into a fixed-size grid and counting occurrences.
 This can also be easily displayed as a bitmap as a convenient way to visualize distribution.
@@
 
-    The collision rate can be computed by counting unique values with the help of an hash table.
+    The collision rate can be computed by counting unique values with the help of a hash table.
     \item \textbf{Avalanche Effect:} A subtle change in the input should result in a considerably different output, ensuring sensitivity to input variations.
@@
 Ideally, half of the hash bits should change on average.
-    \item \textbf{Performance:} The performance of a noncryptographic hash function is usually reflected by the performance of the application using it.
+    \item \textbf{Performance:} The performance of a non-cryptographic hash function is usually reflected by the performance of the application using it.
 For instance, a fast non-cryptographic hash function generally implies a fast hash table.
@@
 \paragraph{Random Blobs}\leavevmode\\
-For the first scenario, we randomly generate 1,000,000 inputs of size 4 bytes, 64 and 1000 to observe how the hash function behaves with truly unpredictable data, and for different input sizes.
+For the first scenario, we randomly generate 1,000,000 inputs of size 4 bytes, 64, and 1000 to observe how the hash function behaves with truly unpredictable data, and for different input sizes.
 
@@
 Avalanche is good for most algorithms, except for FNV-1a and CRC.
-We can notice that avalanche score for GxHash is an order of magnitude better than other algorithms for larger input sizes.
+We can notice that the avalanche score for GxHash is an order of magnitude better than other algorithms for larger input sizes.
 
@@
 For this reason, the collision rate is expected to be about 2 \(\times\) 0.0116\%.
-We can see however that CRC and XxHash\cite{xxhash} have lower odds of collisions for 4 bytes input, which can be explained by a size-specific logic to handle small inputs bijectively.
+We can see, however, that CRC and XxHash\cite{xxhash} have lower odds of collisions for 4-byte inputs, which can be explained by a size-specific logic to handle small inputs bijectively.
 
@@
 
-Here is a visualization of the distribution represented by bitmap, which each pixel being a bucket for generated hashes to fill.
+Here is a visualization of the distribution represented by bitmap, with each pixel being a bucket for generated hashes to fill.
 A black pixel is an empty pixel, and the whiter a pixel is the fuller of hashes the bucket is.
@@
 TODO
-Regarding distribution, we can notice that GxHash outperforms HighwayHash\cite{highwayhash}, XxHash\cite{xxhash} and T1ha0\cite{rust-t1ha}.
+Regarding distribution, we can notice that GxHash outperforms HighwayHash\cite{highwayhash}, XxHash\cite{xxhash}, and T1ha0\cite{rust-t1ha}.
 Avalanche is slightly worse, however, possibly due to the tradeoff of doing fewer operations for greater performances.
@@
 As a matter of fact, we clearly identify distribution patterns for FNV-1a and CRC.
-It isn't necessarily a bad thing, because a hash function can distribute the hash in a way that the distribution map looks evenly distributed (such as what we observe with CRC with 1000-bytes long inputs), however it implies that values hashes are correlated in a way, which a property we prefer to avoid for a non-cryptographic hash function.
+It isn't necessarily a bad thing, because a hash function can distribute the hash in a way that the distribution map looks evenly distributed (such as what we observe with CRC with 1000-byte long inputs), however, it implies that values hashes are correlated in a way, which a property we prefer to avoid for a non-cryptographic hash function.
 GxHash performs well in that matter, with a distribution that looks as uniform and uncorrelated than its counterparts HighwayHash\cite{highwayhash}, XxHash\cite{xxhash} and T1ha0\cite{rust-t1ha}.
@@
 
-We still observe about 0.0116\% of collisions for all algorithms, explainable by the birthday paradox as seen previously.
-This time however, XxHash\cite{xxhash}, Fnv1a and Crc are not able to beep bijectivity as inputs use more bytes compared to the sequential case, making the bijectivity property impossible and thus leading to inevitable collision.
+We still observe about 0.0116\% of collisions for all algorithms, explainable by the birthday paradox, as seen previously.
+This time however, XxHash\cite{xxhash}, Fnv1a, and Crc are not able to beep bijectivity as inputs use more bytes compared to the sequential case, making the bijectivity property impossible and thus leading to inevitable collision.
 The bits distribution is very close for all algorithms benchmarked, at about 0.001.
-The avalanche score for GxHash is very good, on pair with HighwayHash\cite{highwayhash}, XxHash\cite{xxhash} and T1ha\cite{rust-t1ha}.
+The avalanche score for GxHash is very good, on pair with HighwayHash\cite{highwayhash}, XxHash\cite{xxhash}, and T1ha\cite{rust-t1ha}.
 
@@
 For almost any input size and on all platforms used for the benchmark, the 128-bit state GxHash was the fastest.
-The 256-bit GxHash reaches almost two times the maximum throughput of the 128-bit GxHash implementation, as excepted.
+The 256-bit GxHash reaches almost two times the maximum throughput of the 128-bit GxHash implementation, as expected.
 We can notice however that it performs slightly worse for inputs of small sizes, which can be explained by the overhead of extracting and xoring the two 128-bit parts of the state.
@@
 On the GCP and Apple M1 Pro benchmarks, the algorithm reaches an impressive 11 Gb/s for 8 bytes inputs.
-While some algorithms that are supposed to be heavily optimized for small input sizes such as XxHash, they only reach up to a quarter of that throughput.
-After some analysis, a theory was that assembly code for XxHash was much larger than GxHash, thus preventing the algorithm to be inlined in the benchmark itself.
+While some algorithms are supposed to be heavily optimized for small input sizes, such as XxHash, they only reach up to a quarter of that throughput.
+After some analysis, a theory was that the assembly code for XxHash was much larger than GxHash, thus preventing the algorithm from being inlined in the benchmark itself.
 After analysis using cargo asm, it turned out that on ARM XxHash produces 10 times as much assembly than GxHash.
-Forcing all methods not to be inlined in the benchmarks tend to prove this theory, as timing for small inputs are now all in the same ballpark.
-Inlining being a important part of the optimization done by compilers is also why special care was taken to make GxHash implementation leading to as little as bytecode as possible.
-Since criterion.rs benchmarking fixture is also leading the GxHash to be inlined, we think those benchmark results are viable and representative of the real world usage.
+Forcing all methods not to be inlined in the benchmarks tends to prove this theory, as timing for small inputs is now all in the same ballpark.
+Inlining being an important part of the optimization done by compilers is also why special care was taken to make GxHash implementation leading to as little bytecode as possible.
+Since criterion.rs benchmarking fixture is also leading the GxHash to be inlined, we think those benchmark results are viable and representative of the real-world usage.
 
@@
 To prevent any potential confusion, it is recommended that users choose one state size and maintain consistency throughout the hashing process, especially when hashes may need to be compared or persisted.
-This limitation is deemed acceptable for use-cases such as in-process hash tables where the state size does not change.
-Developing a version of GxHash that harmonizes the outputs of different state sizes would involve trade-offs, likely affecting the algorithm’s performance or complexity.
+This limitation is deemed acceptable for use cases such as in-process hash tables where the state size does not change.
+Developing a version of GxHash that harmonizes the outputs of different state sizes would involve tradeoffs, likely affecting the algorithm's performance or complexity.
 
 \subsubsection{Compiler Dependencies} 
-The Temporal Construction presented in this paper is implemented for GxHash by declaring at temporary variable on each group iteration, assuming that the compilers understands that most of each iteration can be parallelized.
+The Temporal Construction presented in this paper is implemented for GxHash by declaring a temporary variable on each group iteration, assuming that the compilers understand that most of each iteration can be parallelized.
 While it worked at the time of writing (rustc 1.68.0), it is in the end the compiler's responsibility to decide how many registers to use.
@@
     \item Make use of compiler hints to improve branching predictions.
-    \item Benchmark in more test suite to further assess the distribution and avalanche properties.
+    \item Benchmark in more test suites to further assess the distribution and avalanche properties.
     \item Analyze security properties.

### 2023-11-19 benches/hashset.rs
Improve hashset benchmark (less biais)

@@ -4,49 +4,66 @@ use fnv::FnvHashSet;
 use gxhash::*;
 use twox_hash::xxh3;
 use std::collections::HashSet;
-use std::hash::BuildHasherDefault;
+use std::hash::{BuildHasherDefault, BuildHasher};
 
 fn hashmap_insertion(c: &mut Criterion) {
 
-    // Long keys
-    benchmark_for_string(c, "Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.");
+    // Short keys
+    benchmark_for_string(c, "gxhash");
 
     // Medium keys
     benchmark_for_string(c, "https://github.com/ogxd/gxhash");
 
-    // Short keys
-    benchmark_for_string(c, "gxhash");
+    // Long keys
+    benchmark_for_string(c, "Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.");
+
+    // Very long keys
[…]

### 2023-11-19 src/gxhash/mod.rs
Remove unstable pointer_byte_offsets requirement

@@ -96,7 +96,7 @@ pub(crate) unsafe fn compress_all(input: &[u8]) -> State {
         // so that we can safely read beyond since we expect the following bytes to still be part of
         // the input
         hash_vector = get_partial_unsafe(ptr,remaining_bytes as usize);
-        ptr = ptr.byte_add(remaining_bytes);
+        ptr = ptr.cast::<u8>().add(remaining_bytes).cast();
     }
 
     if len <= VECTOR_SIZE * 2 {

### 2023-11-19 src/lib.rs

@@ -1,5 +1,5 @@
 #![feature(core_intrinsics)]
-#![feature(pointer_byte_offsets)]
+//#![feature(pointer_byte_offsets)]
 #![feature(stdsimd)]
 #![feature(stmt_expr_attributes)]
 

### 2023-11-19 src/gxhash/mod.rs
Remove unstable core_intrinsics requirement ('likely' is not even working anyway, broken since LLVM update)

@@ -1,7 +1,5 @@
 pub(crate) mod platform;
 
-use std::intrinsics::likely;
-
 use platform::*;
 
 /// Hashes an arbitrary stream of bytes to an u32.
@@ -77,7 +75,7 @@ pub(crate) unsafe fn compress_all(input: &[u8]) -> State {
     let len = input.len();
     let mut ptr = input.as_ptr() as *const State;
 
-    if likely(len <= VECTOR_SIZE) {
+    if len <= VECTOR_SIZE {
         // Input fits on a single SIMD vector, however we might read beyond the input message
         // Thus we need this safe method that checks if it can safely read beyond or must copy
         return get_partial(ptr, len);

### 2023-11-19 src/gxhash/platform/arm_128.rs

@@ -1,4 +1,3 @@
-use std::intrinsics::likely;
 use core::arch::aarch64::*;
 
 use super::*;
@@ -31,7 +30,7 @@ pub unsafe fn load_unaligned(p: *const State) -> State {
 
 #[inline(always)]
 pub unsafe fn get_partial(p: *const State, len: usize) -> State {
-    if likely(check_same_page(p)) {
+    if check_same_page(p) {
         get_partial_unsafe(p, len)
     } else {
         get_partial_safe(p, len)

### 2023-11-19 src/lib.rs

@@ -1,4 +1,4 @@
-#![feature(core_intrinsics)]
+//#![feature(core_intrinsics)]
 //#![feature(pointer_byte_offsets)]
 #![feature(stdsimd)]
 #![feature(stmt_expr_attributes)]

### 2023-11-19 src/hasher.rs
Remove unstable core_intrinsics requirement ('likely' is not even working anyway, broken since LLVM update)

@@ -2,7 +2,7 @@ use std::hash::{Hasher, BuildHasher};
 use std::collections::{HashMap, HashSet};
 use std::mem::MaybeUninit;
 
-use rand::{Rng, RngCore};
+use rand::RngCore;
 
 use crate::gxhash::*;
 use crate::gxhash::platform::*;

### 2023-11-19 src/lib.rs
Remove unstable stmt_expr_attributes requirement

@@ -1,7 +1,7 @@
 //#![feature(core_intrinsics)]
 //#![feature(pointer_byte_offsets)]
 #![feature(stdsimd)]
-#![feature(stmt_expr_attributes)]
+//#![feature(stmt_expr_attributes)]
 
 mod gxhash;
 mod hasher;

### 2023-11-19 src/gxhash/mod.rs
Remove unstable stmt_expr_attributes requirement

@@ -58,7 +58,6 @@ macro_rules! load_unaligned {
         $(
             #[allow(unused_mut)]
             let mut $var = load_unaligned($ptr);
-            #[allow(unused_assignments)]
             $ptr = ($ptr).offset(1);
         )+
     };
@@ -97,6 +96,7 @@ pub(crate) unsafe fn compress_all(input: &[u8]) -> State {
         ptr = ptr.cast::<u8>().add(remaining_bytes).cast();
     }
 
+    #[allow(unused_assignments)]
     if len <= VECTOR_SIZE * 2 {
         // Fast path when input length > 16 and <= 32
         load_unaligned!(ptr, v0);

### 2023-11-19 src/lib.rs
Remove stdsimd requirement

@@ -1,7 +1,5 @@
-//#![feature(core_intrinsics)]
-//#![feature(pointer_byte_offsets)]
-#![feature(stdsimd)]
-//#![feature(stmt_expr_attributes)]
+// Feature 'avx2' currently requires unstable 'stdsimd'
+#![cfg_attr(all(feature = "avx2", target_arch = "x86_64"), feature(stdsimd))]
 
 mod gxhash;
 mod hasher;

### 2023-11-19 src/gxhash/platform/x86_128.rs
Remove stdsimd requirement

@@ -36,7 +36,7 @@ pub unsafe fn get_partial_safe(data: *const State, len: usize) -> State {
     // Copy data into the buffer
     std::ptr::copy(data as *const i8, buffer.as_mut_ptr(), len);
     // Load the buffer into a __m256i vector
-    let partial_vector = _mm_loadu_epi8(buffer.as_ptr());
+    let partial_vector = _mm_loadu_si128(buffer.as_ptr() as *const State);
     _mm_add_epi8(partial_vector, _mm_set1_epi8(len as i8))
 }
 

### 2023-11-19 src/gxhash/platform/x86_256.rs

@@ -36,7 +36,7 @@ pub unsafe fn get_partial_safe(data: *const State, len: usize) -> State {
     // Copy data into the buffer
     std::ptr::copy(data as *const i8, buffer.as_mut_ptr(), len);
     // Load the buffer into a __m256i vector
-    let partial_vector = _mm256_loadu_epi8(buffer.as_ptr());
+    let partial_vector = _mm256_loadu_si256(buffer.as_ptr() as *const State);
     _mm256_add_epi8(partial_vector, _mm256_set1_epi8(len as i8))
 }
 

### 2023-11-25 src/hasher.rs
Add rustfmt and fix pub mod platform conflict

@@ -1,21 +1,21 @@
-use std::hash::{Hasher, BuildHasher};
 use std::collections::{HashMap, HashSet};
+use std::hash::{BuildHasher, Hasher};
 use std::mem::MaybeUninit;
 
 use rand::RngCore;
 
-use crate::gxhash::*;
 use crate::gxhash::platform::*;
+use crate::gxhash::*;
 
 /// A `Hasher` for hashing an arbitrary stream of bytes.
 /// # Features
 /// - The fastest [`Hasher`] of its class<sup>1</sup>, for all input sizes
 /// - Highly collision resitant
 /// - DOS resistance thanks to seed randomization when using [`GxHasher::default()`]
-/// 
+///
 /// *<sup>1</sup>There might me faster alternatives, such as `fxhash` for very small input sizes, but that usually have low quality properties.*
 pub struct GxHasher {
-    state: State
+    state: State,
 }
 
 impl GxHasher {
@@ -27,11 +27,11 @@ impl GxHasher {
 
 impl Default for GxHasher {
     /// Creates a new hasher with a empty seed.
-    /// 
+    ///
     /// # Warning ⚠️
     /// Not using a seed may make your [`Hasher`] vulnerable to DOS attacks.  
     /// It is recommended to use [`GxBuildHasher::default()`] for improved DOS resistance.
-    /// 
+    ///
     /// # Example
     ///
     /// ```
@@ -54,7 +54,7 @@ impl Default for GxHasher {
 
 impl GxHasher {
     /// Creates a new hasher using the provided seed.
-    /// 
+    ///
     /// # Warning ⚠️
     /// Hardcoding a seed may make your [`Hasher`] vulnerable to DOS attacks.  
     /// It is recommended to use [`GxBuildHasher::default()`] for improved DOS resistance.

### 2023-11-25 src/lib.rs

@@ -1,6 +1,7 @@
 // Feature 'avx2' currently requires unstable 'stdsimd'
 #![cfg_attr(all(feature = "avx2", target_arch = "x86_64"), feature(stdsimd))]
 
+#[rustfmt::skip]
 mod gxhash;
 mod hasher;
 

### 2023-11-25 src/gxhash/platform/mod.rs
Add rustfmt and fix pub mod platform conflict

@@ -1,6 +1,6 @@
 #[cfg(target_arch = "aarch64")]
 #[path = "arm_128.rs"]
-pub mod platform;
+mod platform;
 
 #[cfg(all(
     feature = "avx2",
@@ -8,14 +8,14 @@ pub mod platform;
     target_feature = "avx2")
 )]
 #[path = "x86_256.rs"]
-pub mod platform;
+mod platform;
 
 #[cfg(all(
     not(feature = "avx2"),
     target_arch = "x86_64"
 ))]
 #[path = "x86_128.rs"]
-pub mod platform;
+mod platform;
 
 use std::mem::size_of;
 

### 2023-11-25 src/gxhash/mod.rs
Added common traits, `clippy`, `rustfmt`, deps,  (#27)
* Added `Clone` and `Debug` traits to `GxHasher` and `GxBuildHasher`.

* Updated deps.

* Made clippy (almost) happy.

* rustfmt.

---------

Co-authored-by: Olivier Giniaux <oginiaux@gmail.com>

@@ -79,7 +79,7 @@ pub(crate) unsafe fn compress_all(input: &[u8]) -> State {
         // Thus we need this safe method that checks if it can safely read beyond or must copy
         return get_partial(ptr, len);
     }
-    
+
     let remaining_bytes = len % VECTOR_SIZE;
 
     // The input does not fit on a single SIMD vector
@@ -92,7 +92,7 @@ pub(crate) unsafe fn compress_all(input: &[u8]) -> State {
         // it means we'll need to read a partial vector. We can start with the partial vector first,
         // so that we can safely read beyond since we expect the following bytes to still be part of
         // the input
-        hash_vector = get_partial_unsafe(ptr,remaining_bytes as usize);
+        hash_vector = get_partial_unsafe(ptr, remaining_bytes);
         ptr = ptr.cast::<u8>().add(remaining_bytes).cast();
     }
 
@@ -142,7 +142,6 @@ unsafe fn compress_many(mut ptr: *const State, hash_vector: State, remaining_byt
     let remaining_bytes = remaining_bytes - unrollable_blocks_count * VECTOR_SIZE;
     let end_address = ptr.add(remaining_bytes / VECTOR_SIZE) as usize;
 
-    let mut hash_vector = hash_vector;
     while (ptr as usize) < end_address {
         load_unaligned!(ptr, v0);
         hash_vector = compress(hash_vector, v0);

### 2023-11-25 src/gxhash/platform/arm_128.rs

@@ -101,10 +101,10 @@ pub unsafe fn finalize(hash: State) -> State {
     let keys_3 = vld1q_u32([0xC78B122B, 0x5544B1B7, 0x689D2B7D, 0xD0012E32].as_ptr());
 
     // 3 rounds of AES
-    let mut hash = ReinterpretUnion{ int8: hash }.uint8;
-    hash = aes_encrypt(hash, ReinterpretUnion{ uint32: keys_1 }.uint8);
-    hash = aes_encrypt(hash, ReinterpretUnion{ uint32: keys_2 }.uint8);
-    hash = aes_encrypt_last(hash, ReinterpretUnion{ uint32: keys_3 }.uint8);
+    let mut hash = ReinterpretUnion { int8: hash }.uint8;
+    hash = aes_encrypt(hash, ReinterpretUnion { uint32: keys_1 }.uint8);
+    hash = aes_encrypt(hash, ReinterpretUnion { uint32: keys_2 }.uint8);
+    hash = aes_encrypt_last(hash, ReinterpretUnion { uint32: keys_3 }.uint8);
 
-    ReinterpretUnion{ uint8: hash }.int8
+    ReinterpretUnion { uint8: hash }.int8
 }

### 2023-11-25 src/hasher.rs

@@ -14,6 +14,7 @@ use crate::gxhash::*;
 /// - DOS resistance thanks to seed randomization when using [`GxHasher::default()`]
 ///
 /// *<sup>1</sup>There might me faster alternatives, such as `fxhash` for very small input sizes, but that usually have low quality properties.*
+#[derive(Clone, Debug)]
 pub struct GxHasher {
     state: State,
 }
@@ -21,7 +22,7 @@ pub struct GxHasher {
 impl GxHasher {
     #[inline]
     fn with_state(state: State) -> GxHasher {
-        GxHasher { state: state }
+        GxHasher { state }
     }
 }
 
@@ -29,7 +30,7 @@ impl Default for GxHasher {
     /// Creates a new hasher with a empty seed.
     ///
     /// # Warning ⚠️
-    /// Not using a seed may make your [`Hasher`] vulnerable to DOS attacks.  
+    /// Not using a seed may make your [`Hasher`] vulnerable to DOS attacks.
     /// It is recommended to use [`GxBuildHasher::default()`] for improved DOS resistance.
     ///
     /// # Example
@@ -56,7 +57,7 @@ impl GxHasher {
     /// Creates a new hasher using the provided seed.
     ///
     /// # Warning ⚠️
-    /// Hardcoding a seed may make your [`Hasher`] vulnerable to DOS attacks.  
+    /// Hardcoding a seed may make your [`Hasher`] vulnerable to DOS attacks.
     /// It is recommended to use [`GxBuildHasher::default()`] for improved DOS resistance.
     ///
     /// # Example
@@ -109,6 +110,7 @@ impl Hasher for GxHasher {
 }
 
 /// A builder for building GxHasher with randomized seeds by default, for improved DOS resistance.
+#[derive(Clone, Debug)]
 pub struct GxBuildHasher(State);
 
 impl Default for GxBuildHasher {

### 2023-11-25 src/gxhash/platform/mod.rs
Added common traits, `clippy`, `rustfmt`, deps,  (#27)
* Added `Clone` and `Debug` traits to `GxHasher` and `GxBuildHasher`.

* Updated deps.

* Made clippy (almost) happy.

* rustfmt.

---------

Co-authored-by: Olivier Giniaux <oginiaux@gmail.com>

@@ -2,18 +2,11 @@
 #[path = "arm_128.rs"]
 mod platform;
 
-#[cfg(all(
-    feature = "avx2",
-    target_arch = "x86_64",
-    target_feature = "avx2")
-)]
+#[cfg(all(feature = "avx2", target_arch = "x86_64", target_feature = "avx2"))]
 #[path = "x86_256.rs"]
 mod platform;
 
-#[cfg(all(
-    not(feature = "avx2"),
-    target_arch = "x86_64"
-))]
+#[cfg(all(not(feature = "avx2"), target_arch = "x86_64"))]
 #[path = "x86_128.rs"]
 mod platform;
 

### 2023-11-25 src/gxhash/platform/x86_128.rs

@@ -23,9 +23,9 @@ pub unsafe fn load_unaligned(p: *const State) -> State {
 pub unsafe fn get_partial(p: *const State, len: usize) -> State {
     // Safety check
     if check_same_page(p) {
-        get_partial_unsafe(p, len as usize)
+        get_partial_unsafe(p, len)
     } else {
-        get_partial_safe(p, len as usize)
+        get_partial_safe(p, len)
     }
 }
 
@@ -57,13 +57,13 @@ pub unsafe fn compress(a: State, b: State) -> State {
     // 2+1 rounds of AES for compression
     let mut b = _mm_aesenc_si128(b, keys_1);
     b = _mm_aesenc_si128(b, keys_2);
-    return _mm_aesenclast_si128(a, b);
+    _mm_aesenclast_si128(a, b)
 }
 
 #[inline(always)]
 #[allow(overflowing_literals)]
 pub unsafe fn compress_fast(a: State, b: State) -> State {
-    return _mm_aesenc_si128(a, b);
+    _mm_aesenc_si128(a, b)
 }
 
 #[inline(always)]

### 2023-11-25 src/lib.rs

@@ -5,5 +5,5 @@
 mod gxhash;
 mod hasher;
 
-pub use gxhash::*;
-pub use hasher::*;
+pub use crate::gxhash::*;
+pub use crate::hasher::*;

### 2023-11-25 article/article.tex
Fix spelling and grammar mistakes (#19) (#26)
Co-authored-by: Ian Qvist <Genbox@users.noreply.github.com>

@@
 \caption{Quality benchmark results for the random dataset at 1,000,000 iterations}
-\label{tab:quality-data-random}
+\label{tab:scores-random}
 \end{table}
@@
 \caption{Quality benchmark results for the sequential dataset at 1,000,000 iterations}
-\label{tab:my_label}
+\label{tab:scores-sequential}
 \end{table}
@@
 
-TODO
-Regarding distribution, we can notice that GxHash outperforms HighwayHash\cite{highwayhash}, XxHash\cite{xxhash}, and T1ha0\cite{rust-t1ha}.
-Avalanche is slightly worse, however, possibly due to the tradeoff of doing fewer operations for greater performances.
-Overall, the numbers are all still very low and remain in the same ballpark, except for FNV-1a and CRC which still suffer from a relatively "high" avalanche.
+Overall, the distribution/avalanche scores are all very low and remain in the same ballpark for GxHash, HighwayHash, T1ha and XxHash.
+FNV-1a and CRC have relatively worse avalanche score due to their simplicity.
 
@@
 \caption{Quality benchmark results for words dataset at 1,000,000 iterations}
-\label{tab:my_label}
+\label{tab:scores-words}
 \end{table}
@@
 \caption{Distribution map for words dataset}
-\label{fig:quality-sequential}
+\label{fig:quality-words}
 \end{figure}

### 2024-05-15 src/lib.rs
Fix x86 hybrid build since rust update

@@ -1,5 +1,6 @@
 // Hybrid SIMD width usage currently requires unstable 'stdsimd'
 #![cfg_attr(hybrid, feature(stdsimd))]
+#![cfg_attr(hybrid, feature(stdarch_x86_avx512))]
 
 #[rustfmt::skip]
 mod gxhash;

### 2024-05-15 src/lib.rs
Try remove stdsimd

@@ -1,5 +1,4 @@
 // Hybrid SIMD width usage currently requires unstable 'stdsimd'
-#![cfg_attr(hybrid, feature(stdsimd))]
 #![cfg_attr(hybrid, feature(stdarch_x86_avx512))]
 
 #[rustfmt::skip]

### 2024-05-15 src/lib.rs
Fix x86 hybrid build since rust 1.79 (#68)
* Fix x86 hybrid build since rust update

* Try remove stdsimd

* Display version

* Try github macos runner

* Set version to 3.2.0

* Test rustc 1.72 with hybrid

* Add rust version compat check

* Try use patch in v

* Another test

* Disable fail fast

* Fix hybrid

* Fix missing cpu feature

* No hybrid

* Workflow dispatch

@@ -1,5 +1,5 @@
 // Hybrid SIMD width usage currently requires unstable 'stdsimd'
-#![cfg_attr(hybrid, feature(stdsimd))]
+#![cfg_attr(hybrid, feature(stdarch_x86_avx512))]
 
 #[rustfmt::skip]
 mod gxhash;

### 2024-05-15 article/article.tex
Fix typo in article

@@
 We still observe about 0.0116\% of collisions for all algorithms, explainable by the birthday paradox, as seen previously.
-This time however, XxHash\cite{xxhash}, Fnv1a, and Crc are not able to beep bijectivity as inputs use more bytes compared to the sequential case, making the bijectivity property impossible and thus leading to inevitable collision.
+This time however, XxHash\cite{xxhash}, Fnv1a, and Crc are not able to keep bijectivity as inputs use more bytes compared to the sequential case, making the bijectivity property impossible and thus leading to inevitable collision.
 The bits distribution is very close for all algorithms benchmarked, at about 0.001.
